### 2015-01-15 publish/plos_template.tex
really rough draft of intro

% Template for PLoS
% Version 2.0 July 2014
%
% To compile to pdf, run:
% latex plos.template
% bibtex plos.template
% latex plos.template
% latex plos.template
% dvipdf plos.template
%
% % % % % % % % % % % % % % % % % % % % % %
%
% -- IMPORTANT NOTE
%
% Be advised that this is merely a template 
% designed to facilitate accurate translation of manuscript content 
% into our production files. 
%
% This template contains extensive comments intended 
% to minimize problems and delays during our production 
% process. Please follow the template 
% whenever possible.
%
% % % % % % % % % % % % % % % % % % % % % % % 
%
% Once your paper is accepted for publication and enters production, 
% PLEASE REMOVE ALL TRACKED CHANGES in this file and leave only
% the final text of your manuscript.
%
% DO NOT ADD EXTRA PACKAGES TO THIS TEMPLATE unless absolutely necessary.
% Packages included in this template are intentionally
% limited and basic in order to reduce the possibility
% of issues during our production process.
%
% % % % % % % % % % % % % % % % % % % % % % %
%
% -- FIGURES AND TABLES
%
% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
% - Figures should be uploaded separately from your manuscript file. 
% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
% See http://www.plosone.org/static/figureGuidelines for PLOS figure guidelines.
%
% Tables should be cell-based and may not contain:
% - tabs/spacing/line breaks within cells to alter layout
% - vertically-merged cells (no tabular environments within tabular environments, do not use \multirow)
% - colors, shading, or graphic objects
% See http://www.plosone.org/static/figureGuidelines#tables for table guidelines.
%
% For sideways tables, use the {rotating} package and use \begin{sidewaystable} instead of \begin{table} in the appropriate section. PLOS guidelines do not accomodate sideways figures.
%
% % % % % % % % % % % % % % % % % % % % % % % %
%
% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
%
% IMPORTANT
% Below are a few tips to help format your equations and other special characters according to our specifications. For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://www.plosone.org/static/latexGuidelines
%
% Please be sure to include all portions of an equation in the math environment, and for any superscripts or subscripts also include the base number/text. For example, use $mathrm{mm}^2$ instead of mm$^2$ (do not use \textsuperscript command).
%
% DO NOT USE the \rm command to render mathmode characters in roman font, instead use $\mathrm{}$
% For bolding characters in mathmode, please use $\mathbf{}$ 
%
% Please add line breaks to long equations when possible in order to fit our 2-column layout. 
%
% For inline equations, please do not include punctuation within the math environment unless this is part of the equation.
%
% For spaces within the math environment please use the \; or \: commands, even within \text{} (do not use smaller spacing as this does not convert well).
%
%
% % % % % % % % % % % % % % % % % % % % % % % %

\documentclass[10pt]{article}

% amsmath package, useful for mathematical formulas
\usepackage{amsmath}
% amssymb package, useful for mathematical symbols
\usepackage{amssymb}

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

\usepackage{hyperref}

% line numbers
\usepackage{lineno}

% ligatures disabled
\usepackage{microtype}
\DisableLigatures[f]{encoding = *, family = * }

% rotating package for sideways tables
%\usepackage{rotating}

% If you wish to include algorithms, please use one of the packages below. Also, please see the algorithm section of our LaTeX guidelines (http://www.plosone.org/static/latexGuidelines) for important information about required formatting.
%\usepackage{algorithmic}
%\usepackage{algorithmicx}

% Use doublespacing - comment out for single spacing
%\usepackage{setspace} 
%\doublespacing

% Text layout
\topmargin 0.0cm
\oddsidemargin 0.5cm
\evensidemargin 0.5cm
\textwidth 16cm 
\textheight 21cm

% Bold the 'Figure #' in the caption and separate it with a period
% Captions will be left justified
\usepackage[labelfont=bf,labelsep=period,justification=raggedright]{caption}

% Use the PLoS provided BiBTeX style
\bibliographystyle{plos2009}

% Remove brackets from numbering in List of References
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

% Leave date blank
\date{}

\pagestyle{myheadings}

%% Include all macros below. Please limit the use of macros.

%% END MACROS SECTION

\begin{document}

% Title must be 150 characters or less
\begin{flushleft}
{\Large
\textbf{3D-Printable Micropipette}
}
% Insert Author names, affiliations and corresponding author email.
\\
Author1$^{1}$, 
Author2$^{2}$, 
Author3$^{3,\ast}$
\\
\bf{1} Author1 Dept/Program/Center, Institution Name, City, State, Country
\\
\bf{2} Author2 Dept/Program/Center, Institution Name, City, State, Country
\\
\bf{3} Author3 Dept/Program/Center, Institution Name, City, State, Country
\\
$\ast$ E-mail: Corresponding author@institute.edu
\end{flushleft}

% Please keep the abstract between 250 and 300 words
\section*{Abstract}

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
\section*{Author Summary}

\section*{Introduction}

Additive manufacturing methods have been under development and use for more than 30 years.
3D printing has experienced a sudden surge in popularity due to recent abalibily of consumer avalible desktop printers. 
3D printing as a form of additive manufacutring has existed for decades although t
The recent avalibility of inexpensive desktop printers have made it fesable for consumers to design and print prototypes and even functional parts, and consumer goods.

The open source software and has spawed the areas of open source hardware, including such as circuit boards computers (arduio, raspberrpi) as well as 3D printers themselves(reprap). 
Open source scientific instruments and laborotory equipment as also being activly developed.
A 3D-printable piece of lab equipment is espically attractive because of the simplicity of downloading and printing a functional object for only the price of the material. 
This may allow a researcher, an oppertunity to preform a measuremt, or activity with out typical finacial and time constraints and with the option of futher customizing the printed part.
Some of the more clever uses of the consumer avalible plastic extrusion printers(fused deposition modeling) is when a printed part is desiged to give a new function to a existig device where before there was none.
For example a drill bit attachment was designed and printed to hold micro centrifuge tubes allowing a drill to be used for centrifuging samples. 
Although this may make a rather crude crentrifuge it may be and adqquite method that only costs pennies compared to commerically avalible certirfuges.

Micropipette designs can be found on 3D-part shareing websites.
While exisiting designs require only pen springs, a gasket made from a ballon, and tape, none allow adjustment to know volumes.
We present a pipette constructed from 3D printed parts that allows a 1 mL syringe to be actuated to an adjustable volume.
The scale marks on the syringe can be used to adjust the dispenced volume accurately without calibarting with a scale.

This is a test of the citations \cite{oppegard2010}.

% You may title this section "Methods" or "Models". 
% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
% authors may use "Analysis" 
\section*{Materials and Methods}

% Results and Discussion can be combined.
\section*{Results}

% We only support three levels of headings, please do not create a heading level below \subsubsection.
\subsection*{Subsection 1}

\subsubsection*{SubSubsection 1.1}

\subsection*{Subsection 2}

\section*{Discussion}

% Do NOT remove this, even if you are not including acknowledgments.

\section*{Acknowledgments}

%\section*{References}

\bibliography{references}

% Either type in your references using
% \begin{thebibliography}{}
% \bibitem{}
% Text
% \end{thebibliography}
%
% OR
%
% Compile your BiBTeX database using our plos2009.bst
% style file and paste the contents of your .bbl file
% here.
%

\section*{Figure Legends}
% This section is for figure legends only, do not include
% graphics in your manuscript file.
%
%\begin{figure}
%\caption{
%{\bf Bold the first sentence.}  Rest of figure caption.  
%}
%\label{Figure_label}
%\end{figure}

\section*{Tables}
% 
% See introductory notes if you wish to include sideways tables.
%
% NOTE: Please look over our table guidelines at http://www.plosone.org/static/figureGuidelines#tables to make sure that your tables meet our requirements. Certain types of spacing, cell merging, and other formatting tricks may have unintended results and will be returned for revision.
%
%\begin{table}[!ht]
%\caption{
%\bf{Table title}}
%\begin{tabular}{|c|c|c|}
%table information
%\end{tabular}
%\begin{flushleft}Table caption
%\end{flushleft}
%\label{tab:label}
% \end{table}

\section*{Supporting Information Legends}
%
% Please enter your Supporting Information captions below in the following format:
%\item{\bf Figure SX. Enter mandatory title here.} Enter optional descriptive information here.
% 
%\begin{description}
%\item {\bf}
%\item {\bf}
%\end{description}

\end{document}

### 2015-01-16 publish/plos_template.tex
added graphicx package
added figures to .tex file

@@
 \documentclass[10pt]{article}
+
+% remove this package and figure for submission of manuscript
+\usepackage{graphicx}
 
@@
 %\begin{figure}
+%\includegraphics[scale=1]{file.png} % take image out for final manuscript
+%\caption{
+%{\bf Bold the first sentence.}  Rest of figure caption.  
+%}
+%\label{Figure_label}
+%\end{figure}
+
+\begin{figure}
+\includegraphics[scale=1]{figure-images/rendering-assembly4.jpg} % take image out for final manuscript
+\caption{
+{\bf CAD rendering of printable parts.}  Three parts are printed: the body, plunger shaft, and luer-lock adaptor for pipette tips.
+}
+\label{CAD-render-figure}
+\end{figure}
+
+\begin{figure}
+\includegraphics[scale=1]{figure-images/pipette-disassembled.JPG} % take image out for final manuscript
+\includegraphics[scale=1]{figure-images/pipette-assembled.JPG} % take image out for final manuscript
+\caption{
+{\bf Bold the first sentence.}  Rest of figure caption.  
+}
+\label{photo-parts-figure}
+\end{figure}
+
+%\begin{figure}
+%\includegraphics[scale=1]{file.png} % take image out for final manuscript
 %\caption{

### 2015-01-16 publish/plos_template.tex
updated rendering figure and scaled figures, added caption to photos

@@
 \section*{Figure Legends}
-% This section is for figure legends only, do not include
+% This section is for figure legends only, do not include3
 % graphics in your manuscript file.
@@
 \begin{figure}
-\includegraphics[scale=1]{figure-images/rendering-assembly4.jpg} % take image out for final manuscript
+\includegraphics[scale=0.4]{figure-images/rendering-assembly4.png} % take image out for final manuscript
 \caption{
@@
 \begin{figure}
-\includegraphics[scale=1]{figure-images/pipette-disassembled.JPG} % take image out for final manuscript
-\includegraphics[scale=1]{figure-images/pipette-assembled.JPG} % take image out for final manuscript
+\includegraphics[scale=0.04]{figure-images/pipette-disassembled.JPG} % take image out for final manuscript
+\includegraphics[scale=0.04]{figure-images/pipette-assembled.JPG} % take image out for final manuscript
 \caption{
-{\bf Bold the first sentence.}  Rest of figure caption.  
+{\bf Photos of pipette.}  The pipette is composed of three printed parts, a 1 mL syringe and some additional hardware.  
 }

### 2015-01-16 publish/plos_template.tex
added table of commercail comp
edited and spellchecked

@@
 
-Additive manufacturing methods have been under development and use for more than 30 years.
-3D printing has experienced a sudden surge in popularity due to recent abalibily of consumer avalible desktop printers. 
-3D printing as a form of additive manufacutring has existed for decades although t
-The recent avalibility of inexpensive desktop printers have made it fesable for consumers to design and print prototypes and even functional parts, and consumer goods.
+Although additive manufacturing methods have been under development and use for more than 30 years, 3D printing has experienced a sudden surge in popularity due to recent availability of consumer desktop printers.
+Inexpensive desktop printers have made it feasible for consumers to design and print prototypes and even functional parts, and consumer goods.
 
-The open source software and has spawed the areas of open source hardware, including such as circuit boards computers (arduio, raspberrpi) as well as 3D printers themselves(reprap). 
-Open source scientific instruments and laborotory equipment as also being activly developed.
-A 3D-printable piece of lab equipment is espically attractive because of the simplicity of downloading and printing a functional object for only the price of the material. 
-This may allow a researcher, an oppertunity to preform a measuremt, or activity with out typical finacial and time constraints and with the option of futher customizing the printed part.
-Some of the more clever uses of the consumer avalible plastic extrusion printers(fused deposition modeling) is when a printed part is desiged to give a new function to a existig device where before there was none.
+The open source software movement and has spawned the additional areas of open source hardware, such as circuit boards computers (Arduino, Raspberry Pi) as well as 3D printers themselves (RepRap).
+Open source scientific instruments and laboratory equipment as also being actively developed.
+A 3D-printable piece of lab equipment is and an attractive idea because of the simplicity of downloading and printing a functional object for only the price of the material. 
+This may allow a researcher, an opportunity to preform a measurement, or activity with out typical financial and time constraints and with the option of further customizing the printed object.
+Some of the more clever printable parts that have emerged  are ones that give a new function to a existing device where before there was none.
 For example a drill bit attachment was designed and printed to hold micro centrifuge tubes allowing a drill to be used for centrifuging samples. 
-Although this may make a rather crude crentrifuge it may be and adqquite method that only costs pennies compared to commerically avalible certirfuges.
+Although this may make a rather crude centrifuge it may be and adequate method that only costs pennies compared to commercially available centrifuges.
 
-Micropipette designs can be found on 3D-part shareing websites.
-While exisiting designs require only pen springs, a gasket made from a ballon, and tape, none allow adjustment to know volumes.
+Printable micropipette designs can be found on 3D-part sharing websites.
+While existing designs mayb require only pen springs, a gasket made from a balloon, and tape, none allow adjustment to know volumes.
 We present a pipette constructed from 3D printed parts that allows a 1 mL syringe to be actuated to an adjustable volume.
-The scale marks on the syringe can be used to adjust the dispenced volume accurately without calibarting with a scale.
+The scale marks on the syringe can be used to adjust the dispensed volume accurately without calibrating with a scale.
 
@@
 
+\begin{table}[!ht]
+\caption{
+\bf{Comparision of Accuracy and Precision}}
+\begin{tabular}{|c|c|c|c|}
+\hline
+    Target Volume & 20 $\mu$L & 50 $\mu$L & 200 $\mu$L  \\
+    \hline
+    Printed Pipette & 196.4 $\pm$ 2.2 & 53.5 $\pm$ 1.8 & 19.5 $\pm$ 0.6 \\
+    Commercial Pipette & 204.5 $\pm$ 2.9 & 49.9 $\pm$ 0.1 & 19.9 $\pm$ 0.2 \\
+    \hline
+\end{tabular}
+\begin{flushleft} Average measured volume by weight and standard deviation.
+\end{flushleft}
+\label{tab:comp}
+ \end{table}
+
 \section*{Supporting Information Legends}

### 2015-01-22 publishing/plos_template.tex
changed dir publish to publishing for branch of the same name

--- 2015-01-16 publish/plos_template.tex
@@
 
-% remove this package and figure for submission of manuscript
-\usepackage{graphicx}
-
 % amsmath package, useful for mathematical formulas
@@
 {\Large
-\textbf{3D-Printable Micropipette}
+\textbf{Title}
 }
@@
 \section*{Introduction}
-
-Additive manufacturing methods have been under development and use for more than 30 years.
-3D printing has experienced a sudden surge in popularity due to recent abalibily of consumer avalible desktop printers. 
-3D printing as a form of additive manufacutring has existed for decades although t
-The recent avalibility of inexpensive desktop printers have made it fesable for consumers to design and print prototypes and even functional parts, and consumer goods.
-
-The open source software and has spawed the areas of open source hardware, including such as circuit boards computers (arduio, raspberrpi) as well as 3D printers themselves(reprap). 
-Open source scientific instruments and laborotory equipment as also being activly developed.
-A 3D-printable piece of lab equipment is espically attractive because of the simplicity of downloading and printing a functional object for only the price of the material. 
-This may allow a researcher, an oppertunity to preform a measuremt, or activity with out typical finacial and time constraints and with the option of futher customizing the printed part.
-Some of the more clever uses of the consumer avalible plastic extrusion printers(fused deposition modeling) is when a printed part is desiged to give a new function to a existig device where before there was none.
-For example a drill bit attachment was designed and printed to hold micro centrifuge tubes allowing a drill to be used for centrifuging samples. 
-Although this may make a rather crude crentrifuge it may be and adqquite method that only costs pennies compared to commerically avalible certirfuges.
-
-Micropipette designs can be found on 3D-part shareing websites.
-While exisiting designs require only pen springs, a gasket made from a ballon, and tape, none allow adjustment to know volumes.
-We present a pipette constructed from 3D printed parts that allows a 1 mL syringe to be actuated to an adjustable volume.
-The scale marks on the syringe can be used to adjust the dispenced volume accurately without calibarting with a scale.
 
@@
 %\begin{figure}
-%\includegraphics[scale=1]{file.png} % take image out for final manuscript
-%\caption{
-%{\bf Bold the first sentence.}  Rest of figure caption.  
-%}
-%\label{Figure_label}
-%\end{figure}
-
-\begin{figure}
-\includegraphics[scale=1]{figure-images/rendering-assembly4.jpg} % take image out for final manuscript
-\caption{
-{\bf CAD rendering of printable parts.}  Three parts are printed: the body, plunger shaft, and luer-lock adaptor for pipette tips.
-}
-\label{CAD-render-figure}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=1]{figure-images/pipette-disassembled.JPG} % take image out for final manuscript
-\includegraphics[scale=1]{figure-images/pipette-assembled.JPG} % take image out for final manuscript
-\caption{
-{\bf Bold the first sentence.}  Rest of figure caption.  
-}
-\label{photo-parts-figure}
-\end{figure}
-
-%\begin{figure}
-%\includegraphics[scale=1]{file.png} % take image out for final manuscript
 %\caption{

### 2015-01-22 publishing/plos_template.tex

--- 2015-01-16 publish/plos_template.tex
@@
 Printable micropipette designs can be found on 3D-part sharing websites.
-While existing designs mayb require only pen springs, a gasket made from a balloon, and tape, none allow adjustment to know volumes.
+While existing designs may require only pen springs, a gasket made from a balloon, and tape, none allow adjustment to know volumes.
 We present a pipette constructed from 3D printed parts that allows a 1 mL syringe to be actuated to an adjustable volume.
@@
 \caption{
-{\bf CAD rendering of printable parts.}  Three parts are printed: the body, plunger shaft, and luer-lock adaptor for pipette tips.
+{\bf CAD rendering of printable parts.}  Three parts are printed: the body, plunger shaft, and luer-lock adapter for pipette tips.
 }

### 2015-01-22 publishing/plos_template.tex
dte's edits made

@@
 
-Although additive manufacturing methods have been under development and use for more than 30 years, 3D printing has experienced a sudden surge in popularity due to recent availability of consumer desktop printers.
-Inexpensive desktop printers have made it feasible for consumers to design and print prototypes and even functional parts, and consumer goods.
+3D printing as a form of additive manufacturing has existed for decades althought the recent avalibilty of inexpensive desktop printers have made it feasible for consumers to design and print prototypes and even functional parts, and consumer goods.
 
-The open source software movement and has spawned the additional areas of open source hardware, such as circuit boards computers (Arduino, Raspberry Pi) as well as 3D printers themselves (RepRap).
-Open source scientific instruments and laboratory equipment as also being actively developed.
-A 3D-printable piece of lab equipment is and an attractive idea because of the simplicity of downloading and printing a functional object for only the price of the material. 
-This may allow a researcher, an opportunity to preform a measurement, or activity with out typical financial and time constraints and with the option of further customizing the printed object.
-Some of the more clever printable parts that have emerged  are ones that give a new function to a existing device where before there was none.
+The open source software movement and has spawned the additional areas of open source hardware, such as microcontroller boards (Arduino) as well as 3D printers themselves (RepRap).
+Open source scientific instruments and laboratory equipment are being actively developed(openpcr.org, opensource lab book.)
+3D-printable lab equipment is and an attractive idea because of the simplicity of downloading and printing a functional object for only the price of the raw material. 
+In addition, end users can customize the equiment to their application. 
+Some of the more clever printable parts that have emerged are ones that give a new function to a ubiquitous existing device.
 For example a drill bit attachment was designed and printed to hold micro centrifuge tubes allowing a drill to be used for centrifuging samples. 
-Although this may make a rather crude centrifuge it may be and adequate method that only costs pennies compared to commercially available centrifuges.
+Although this may make a rather crude centrifuge it may be and adequate method that only costs pennies compared to commercially available centrifuges and could allow researchers in the developing world to better participate in science by reducing some finacial barriers of entry.
 
-Printable micropipette designs can be found on 3D-part sharing websites.
-While existing designs may require only pen springs, a gasket made from a balloon, and tape, none allow adjustment to know volumes.
+Printable micropipette designs can be found on 3D-part sharing websites (thiniverse).
+While existing designs may require only pen springs, a gasket made from a balloon, and tape, none allow adjustment to know volumes nor have any been rigorously validated.
 We present a pipette constructed from 3D printed parts that allows a 1 mL syringe to be actuated to an adjustable volume.

### 2015-01-22 publishing/figures.tex
seprated figures into second .tex updated .gitignore, updated figure1

--- 2015-01-22 publishing/plos_template.tex
@@
-% Template for PLoS
-% Version 2.0 July 2014
-%
-% To compile to pdf, run:
-% latex plos.template
-% bibtex plos.template
-% latex plos.template
-% latex plos.template
-% dvipdf plos.template
-%
-% % % % % % % % % % % % % % % % % % % % % %
-%
-% -- IMPORTANT NOTE
-%
-% Be advised that this is merely a template 
-% designed to facilitate accurate translation of manuscript content 
-% into our production files. 
-%
-% This template contains extensive comments intended 
-% to minimize problems and delays during our production 
-% process. Please follow the template 
-% whenever possible.
-%
-% % % % % % % % % % % % % % % % % % % % % % % 
-%
-% Once your paper is accepted for publication and enters production, 
-% PLEASE REMOVE ALL TRACKED CHANGES in this file and leave only
-% the final text of your manuscript.
-%
-% DO NOT ADD EXTRA PACKAGES TO THIS TEMPLATE unless absolutely necessary.
-% Packages included in this template are intentionally
-% limited and basic in order to reduce the possibility
-% of issues during our production process.
-%
-% % % % % % % % % % % % % % % % % % % % % % %
-%
-% -- FIGURES AND TABLES
-%
-% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
-% - Figures should be uploaded separately from your manuscript file. 
-% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
-% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
-% See http://www.plosone.org/static/figureGuidelines for PLOS figure guidelines.
-%
-% Tables should be cell-based and may not contain:
-% - tabs/spacing/line breaks within cells to alter layout
-% - vertically-merged cells (no tabular environments within tabular environments, do not use \multirow)
-% - colors, shading, or graphic objects
-% See http://www.plosone.org/static/figureGuidelines#tables for table guidelines.
-%
-% For sideways tables, use the {rotating} package and use \begin{sidewaystable} instead of \begin{table} in the appropriate section. PLOS guidelines do not accomodate sideways figures.
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
-%
-% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
-%
-% IMPORTANT
-% Below are a few tips to help format your equations and other special characters according to our specifications.
-For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://www.plosone.org/static/latexGuidelines
-%
-% Please be sure to include all portions of an equation in the math environment, and for any superscripts or subscripts also include the base number/text.
-For example, use $mathrm{mm}^2$ instead of mm$^2$ (do not use \textsuperscript command).
-%
-% DO NOT USE the \rm command to render mathmode characters in roman font, instead use $\mathrm{}$
-% For bolding characters in mathmode, please use $\mathbf{}$ 
-%
-% Please add line breaks to long equations when possible in order to fit our 2-column layout. 
-%
-% For inline equations, please do not include punctuation within the math environment unless this is part of the equation.
-%
-% For spaces within the math environment please use the \; or \: commands, even within \text{} (do not use smaller spacing as this does not convert well).
-%
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
+\documentclass[]{article}
 
-\documentclass[10pt]{article}
+\usepackage{graphicx}
 
-% amsmath package, useful for mathematical formulas
-\usepackage{amsmath}
-% amssymb package, useful for mathematical symbols
-\usepackage{amssymb}
-
-% cite package, to clean up citations in the main text. Do not remove.
-\usepackage{cite}
-
-\usepackage{hyperref}
-
-% line numbers
-\usepackage{lineno}
-
-% ligatures disabled
-\usepackage{microtype}
-\DisableLigatures[f]{encoding = *, family = * }
-
-% rotating package for sideways tables
-%\usepackage{rotating}
-
-% If you wish to include algorithms, please use one of the packages below.
-Also, please see the algorithm section of our LaTeX guidelines (http://www.plosone.org/static/latexGuidelines) for important information about required formatting.
-%\usepackage{algorithmic}
-%\usepackage{algorithmicx}
-
-% Use doublespacing - comment out for single spacing
-%\usepackage{setspace} 
-%\doublespacing
-
-% Text layout
-\topmargin 0.0cm
-\oddsidemargin 0.5cm
-\evensidemargin 0.5cm
-\textwidth 16cm 
-\textheight 21cm
-
-% Bold the 'Figure #' in the caption and separate it with a period
-% Captions will be left justified
-\usepackage[labelfont=bf,labelsep=period,justification=raggedright]{caption}
-
-% Use the PLoS provided BiBTeX style
-\bibliographystyle{plos2009}
-
-% Remove brackets from numbering in List of References
-\makeatletter
-\renewcommand{\@biblabel}[1]{\quad#1.}
-\makeatother
-
-% Leave date blank
-\date{}
-
-\pagestyle{myheadings}
-
-%% Include all macros below. Please limit the use of macros.
-
-%% END MACROS SECTION
+%opening
+\title{3D-printable micropipette}
+\author{}
 
@@
 
-% Title must be 150 characters or less
-\begin{flushleft}
-{\Large
-\textbf{Title}
+\maketitle
+
+\begin{figure}
+\includegraphics[scale=0.4]{fig1.PNG} % take image out for final manuscript
+\caption{
+{\bf CAD rendering of printable parts.}  Three parts are printed: the body, plunger shaft, and luer-lock adapter for pipette tips.
 }
-% Insert Author names, affiliations and corresponding author email.
-\\
-Author1$^{1}$, 
-Author2$^{2}$, 
-Author3$^{3,\ast}$
-\\
-\bf{1} Author1 Dept/Program/Center, Institution Name, City, State, Country
-\\
-\bf{2} Author2 Dept/Program/Center, Institution Name, City, State, Country
-\\
-\bf{3} Author3 Dept/Program/Center, Institution Name, City, State, Country
-\\
-$\ast$ E-mail: Corresponding author@institute.edu
-\end{flushleft}
+\label{figure1}
+\end{figure}
 
-% Please keep the abstract between 250 and 300 words
-\section*{Abstract}
+\begin{figure}
+\includegraphics[scale=0.04]{pipette-disassembled.JPG} % take image out for final manuscript
+\includegraphics[scale=0.04]{pipette-assembled.JPG} % take image out for final manuscript
+\caption{
+{\bf Photos of pipette.}  The pipette is composed of three printed parts, a 1 mL syringe and some additional hardware.  
+}
+\label{photo-parts-figure}
+\end{figure}
 
-% Please keep the Author Summary between 150 and 200 words
-% Use first person. PLOS ONE authors please skip this step. 
-% Author Summary not valid for PLOS ONE submissions.   
-\section*{Author Summary}
+%\begin{abstract}
 
-\section*{Introduction}
+%\end{abstract}
 
-This is a test of the citations \cite{oppegard2010}.
-
-% You may title this section "Methods" or "Models". 
-% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
-% authors may use "Analysis" 
-\section*{Materials and Methods}
-
-% Results and Discussion can be combined.
-\section*{Results}
-
-% We only support three levels of headings, please do not create a heading level below \subsubsection.
-\subsection*{Subsection 1}
-
-\subsubsection*{SubSubsection 1.1}
-
-\subsection*{Subsection 2}
-
-\section*{Discussion}
-
-% Do NOT remove this, even if you are not including acknowledgments.
-
-\section*{Acknowledgments}
-
-%\section*{References}
-
-\bibliography{references}
-
-% Either type in your references using
-% \begin{thebibliography}{}
-% \bibitem{}
-% Text
-% \end{thebibliography}
-%
-% OR
-%
-% Compile your BiBTeX database using our plos2009.bst
-% style file and paste the contents of your .bbl file
-% here.
-%
-
-\section*{Figure Legends}
-% This section is for figure legends only, do not include
-% graphics in your manuscript file.
-%
-%\begin{figure}
-%\caption{
-%{\bf Bold the first sentence.}  Rest of figure caption.  
-%}
-%\label{Figure_label}
-%\end{figure}
-
-\section*{Tables}
-% 
-% See introductory notes if you wish to include sideways tables.
-%
-% NOTE: Please look over our table guidelines at http://www.plosone.org/static/figureGuidelines#tables to make sure that your tables meet our requirements.
-Certain types of spacing, cell merging, and other formatting tricks may have unintended results and will be returned for revision.
-%
-%\begin{table}[!ht]
-%\caption{
-%\bf{Table title}}
-%\begin{tabular}{|c|c|c|}
-%table information
-%\end{tabular}
-%\begin{flushleft}Table caption
-%\end{flushleft}
-%\label{tab:label}
-% \end{table}
-
-\section*{Supporting Information Legends}
-%
-% Please enter your Supporting Information captions below in the following format:
-%\item{\bf Figure SX. Enter mandatory title here.} Enter optional descriptive information here.
-% 
-%\begin{description}
-%\item {\bf}
-%\item {\bf}
-%\end{description}
+%\section{}
 

### 2015-01-22 publishing/plos_template.tex
seprated figures into second .tex updated .gitignore, updated figure1

@@
 \documentclass[10pt]{article}
-
-% remove this package and figure for submission of manuscript
-\usepackage{graphicx}
 
@@
 \begin{figure}
-\includegraphics[scale=0.4]{figure-images/rendering-assembly4.png} % take image out for final manuscript
+%\includegraphics[scale=0.4]{figure-images/rendering-assembly4.png} % take image out for final manuscript
 \caption{
@@
 \begin{figure}
-\includegraphics[scale=0.04]{figure-images/pipette-disassembled.JPG} % take image out for final manuscript
-\includegraphics[scale=0.04]{figure-images/pipette-assembled.JPG} % take image out for final manuscript
+%\includegraphics[scale=0.04]{figure-images/pipette-disassembled.JPG} % take image out for final manuscript
+%\includegraphics[scale=0.04]{figure-images/pipette-assembled.JPG} % take image out for final manuscript
 \caption{

### 2015-01-26 publishing/plos_template.tex
added design and started validation in materials

@@
 \section*{Materials and Methods}
+\subsection*{Design}
+The device is designed to actuate a pipette to a set distance.
+The pipette is plunger is actuated to three points, two fixed and one adjustable.
+The fixed points are the dispensed point, when the plunger is all the way down, and the reset point, when the plunger is ready to withdraw fluid.
+The adjustable point is the set point, which determines the volume of fluid that will be drawn into the pipette and dependes on the position of the screw.
+The system is spring loaded towards the set point.
+A springed notch, in the plunger shaft part, and a groove, in the body part, hold the plunger at the reset position where it can be released by pressing in the notch.
+A 1 mL BD syringe twists to lock into the body part.
+An additional printed part adapts standard micropipette tips to the luer fitting of the pipette.
+
+Our printed pipette mimics commercial pipettes is design, function, and user operation, and is intuitive to use.
+
+3D parts were designed in Blender and SolidWorks and printed by Fineline Protoypeing via selective laser sintering. 
+Additional materials include a spring, a nut and bolt and two washers.
+
+\subsection*{Validation}
+
+The pipette was validated and compared to a commerical pipette. 
+The pipette was tested to see if the set point would drift between during use for example small, incremental movements of the screw or other parts causing the pipetted volume to drift.
+To test the pipette the same volume was pipetted 50 times without moveing or re-adjusting the set point. 
+The printed pipette's accuracy and precicion was charaterized and compared to a commericial pipette.
 

### 2015-01-26 publishing/plos_template.tex
methods draft finished

@@
 The printed pipette's accuracy and precicion was charaterized and compared to a commericial pipette.
+The printed pipette and a series of commericial pipettes were tested at volumes of 20 $\mu$L 50 $\mu$L and 200 $\mu$L.
+The printed pipette was adjusted to the the target volume by eye from the syring graduations, and the resulting volume was measured and repeated 5 times to account for varibility.
+Measurment were taken from the commericial pipette in a similar way.
+
+To test user friendliness and feasibilty for useing the pipette without verifing with a scale, data was also gathered from novice users.
+After a quick overview of the opperation of the pipette measurments were taken after the volunteers adjusted the pipette to 200, 50, 20 and 10 $\mu$L.
+After the first attempt was measured on the scale the volunteer was allow to adjust the set point and re-measure untill within 15\% of the target volume was reached.
 

### 2015-01-26 publishing/plos_template.tex
started discussion

@@
 % Results and Discussion can be combined.
-\section*{Results}
+\section*{Results and Discussion}
 
+Our printed pipette had a comparable accuracy to a commerical pipette (table 1).
+The commerical pipette has a digitial readout that allows the user to adjust precisly to set values where the printed pipette is adjusted by eye according to graduations.
+This is certianly the cause of the lower accuracy and wider deviation although it's preforamce is impressive.
+
+The novice user data demonstrates that the pipette set point is user friendly and is capable of accurate measurments without validating with a scale (Figure3).
 % We only support three levels of headings, please do not create a heading level below \subsubsection.

### 2015-01-26 publishing/plos_template.tex
spell checke

--- 2015-01-26 publishing/plos_template.tex
@@
 % Author Summary not valid for PLOS ONE submissions.   
-\section*{Author Summary}
+%\section*{Author Summary}
 
@@
 
-3D printing as a form of additive manufacturing has existed for decades althought the recent avalibilty of inexpensive desktop printers have made it feasible for consumers to design and print prototypes and even functional parts, and consumer goods.
+3D printing as a form of additive manufacturing has existed for decades although the recent availability of inexpensive desktop printers have made it feasible for consumers to design and print prototypes and even functional parts, and consumer goods.
 
-The open source software movement and has spawned the additional areas of open source hardware, such as microcontroller boards (Arduino) as well as 3D printers themselves (RepRap).
+The open source software movement and has spawned the additional areas of open source hardware, such as micro controller boards (Arduino) as well as 3D printers themselves (RepRap).
 Open source scientific instruments and laboratory equipment are being actively developed(openpcr.org, opensource lab book.)
 3D-printable lab equipment is and an attractive idea because of the simplicity of downloading and printing a functional object for only the price of the raw material. 
-In addition, end users can customize the equiment to their application. 
+In addition, end users can customize the equipment to their application. 
 Some of the more clever printable parts that have emerged are ones that give a new function to a ubiquitous existing device.
 For example a drill bit attachment was designed and printed to hold micro centrifuge tubes allowing a drill to be used for centrifuging samples. 
-Although this may make a rather crude centrifuge it may be and adequate method that only costs pennies compared to commercially available centrifuges and could allow researchers in the developing world to better participate in science by reducing some finacial barriers of entry.
+Although this may make a rather crude centrifuge it may be and adequate method that only costs pennies compared to commercially available centrifuges and could allow researchers in the developing world to better participate in science by reducing some financial barriers of entry.
 
-Printable micropipette designs can be found on 3D-part sharing websites (thiniverse).
+Printable micropipette designs can be found on 3D-part sharing websites (thingiverse).
 While existing designs may require only pen springs, a gasket made from a balloon, and tape, none allow adjustment to know volumes nor have any been rigorously validated.
-We present a pipette constructed from 3D printed parts that allows a 1 mL syringe to be actuated to an adjustable volume.
+We present a pipette constructed from 3D printed parts that allows a 1 ml syringe to be actuated to an adjustable volume.
 The scale marks on the syringe can be used to adjust the dispensed volume accurately without calibrating with a scale.
@@
 The fixed points are the dispensed point, when the plunger is all the way down, and the reset point, when the plunger is ready to withdraw fluid.
-The adjustable point is the set point, which determines the volume of fluid that will be drawn into the pipette and dependes on the position of the screw.
+The adjustable point is the set point, which determines the volume of fluid that will be drawn into the pipette and depends on the position of the screw.
 The system is spring loaded towards the set point.
-A springed notch, in the plunger shaft part, and a groove, in the body part, hold the plunger at the reset position where it can be released by pressing in the notch.
-A 1 mL BD syringe twists to lock into the body part.
+A spring notch, in the plunger shaft part, and a groove, in the body part, hold the plunger at the reset position where it can be released by pressing in the notch.
+A 1 ml BD syringe twists to lock into the body part.
 An additional printed part adapts standard micropipette tips to the luer fitting of the pipette.
@@
 
-3D parts were designed in Blender and SolidWorks and printed by Fineline Protoypeing via selective laser sintering. 
+3D parts were designed in Blender and SolidWorks and printed by Fineline Prototyping via selective laser sintering. 
 Additional materials include a spring, a nut and bolt and two washers.
@@
 
-The pipette was validated and compared to a commerical pipette. 
+The pipette was validated and compared to a commercial pipette. 
 The pipette was tested to see if the set point would drift between during use for example small, incremental movements of the screw or other parts causing the pipetted volume to drift.
-To test the pipette the same volume was pipetted 50 times without moveing or re-adjusting the set point. 
-The printed pipette's accuracy and precicion was charaterized and compared to a commericial pipette.
+To test the pipette the same volume was pipetted 50 times without moving or re-adjusting the set point. 
+The printed pipette's accuracy and precision was characterized and compared to a commercial pipette.
+The printed pipette and a series of commercial pipettes were tested at volumes of 20 $\mu$L 50 $\mu$L and 200 $\mu$L.
+The printed pipette was adjusted to the the target volume by eye from the syringe graduations, and the resulting volume was measured and repeated 5 times to account for variability
+Measurements were taken from the commercial pipette in a similar way.
+
+To test user friendliness and feasibility for using the pipette without verifying with a scale, data was also gathered from novice users.
+After a quick overview of the operation of the pipette measurements were taken after the volunteers adjusted the pipette to 200, 50, 20 and 10 $\mu$L.
+After the first attempt was measured on the scale the volunteer was allow to adjust the set point and re-measure until within 15\% of the target volume was reached.
 
 % Results and Discussion can be combined.
-\section*{Results}
+\section*{Results and Discussion}
 
+Our printed pipette had a comparable accuracy to a commercial pipette (table 1).
+The commercial pipette has a digital readout that allows the user to adjust precisely to set values where the printed pipette is adjusted by eye according to graduations.
+This is certainly the cause of the lower accuracy and wider deviation although it's performance is impressive.
+
+The novice user data demonstrates that the pipette set point is user friendly and is capable of accurate measurements without validating with a scale (Figure3).
 % We only support three levels of headings, please do not create a heading level below \subsubsection.
@@
 \caption{
-\bf{Comparision of Accuracy and Precision}}
+\bf{Comparison of Accuracy and Precision}}
 \begin{tabular}{|c|c|c|c|}

### 2015-03-12 publishing/figures.tex
added figure3
spell checke
added figure 3 and exported user data for plotting in R
updated figure 3 with R

@@
 %opening
-\title{3D-printable micropipette}
+\title{3D-printable micropipette (Figures and Tables)}
 \author{}
@@
 \begin{figure}
-\includegraphics[scale=0.4]{fig1.PNG} % take image out for final manuscript
+\includegraphics[scale=0.4]{fig1.PNG}
 \caption{
@@
 }
-\label{photo-parts-figure}
+\label{figure2}
+\end{figure}
+
+\begin{table}[!ht]
+\caption{
+\bf{Comparison of Accuracy and Precision}}
+\begin{tabular}{|c|c|c|c|}
+\hline
+    Target Volume & 20 $\mu$L & 50 $\mu$L & 200 $\mu$L  \\
+    \hline
+    Printed Pipette & 196.4 $\pm$ 2.2 & 53.5 $\pm$ 1.8 & 19.5 $\pm$ 0.6 \\
+    Commercial Pipette & 204.5 $\pm$ 2.9 & 49.9 $\pm$ 0.1 & 19.9 $\pm$ 0.2 \\
+    \hline
+\end{tabular}
+\begin{flushleft} Average measured volume by weight and standard deviation.
+\end{flushleft}
+\label{tab:comp}
+ \end{table}
+
+\begin{figure}
+\includegraphics[scale=0.7]{fig3.png}
+\caption{
+{\bf Novice user's first attempt.} Measurements of novice user's first attempt at adjusting the pipette to target volumes. The red cross it the mean value.
+}
+\label{figure3}
 \end{figure}

### 2015-03-12 data/user-data.R

@@ -1,0 +1,19 @@
+par(mfrow=c(1,4)) 
+title(main="Autos", col.main="red", font.main=4)
+plot(x200, novice_user_data$V1, ylim=c(150,280), axes=FALSE, ann=FALSE)
+points(200,mean(novice_user_data$V1), col="red", pch=3)
+axis(1, at=200, lab="200 uL")
+Axis(side=2)
+plot(x50, novice_user_data$V2, ylim=c(30,60), axes=FALSE, ann=FALSE)
+points(50,mean(novice_user_data$V2), col="red", pch=3)
+axis(1, at=50, lab="50 uL")
+Axis(side=2)
+plot(x20, novice_user_data$V3, ylim=c(10,30), axes=FALSE, ann=FALSE)
+points(20,mean(novice_user_data$V3), col="red", pch=3)
+axis(1, at=20, lab="20 uL")
+Axis(side=2)
+plot(x10, novice_user_data$V4, ylim=c(0,15), axes=FALSE, ann=FALSE)
+points(10,mean(novice_user_data$V4), col="red", pch=3)
+axis(1, at=10, lab="10 uL")
+Axis(side=2)
+title(main="Novice User's First Attempt", font.main=1, cex.main=1.5, line=-2, outer=TRUE)

### 2015-08-19 Plos-one-manuscript/latex/manuscript.tex
have the manuscript started

--- 2015-01-26 publishing/plos_template.tex
@@
 % Template for PLoS
-% Version 2.0 July 2014
+% Version 3.1 February 2015
 %
@@
 %
-% Be advised that this is merely a template 
-% designed to facilitate accurate translation of manuscript content 
-% into our production files. 
-%
-% This template contains extensive comments intended 
+% This template contains comments intended 
 % to minimize problems and delays during our production 
-% process. Please follow the template 
+% process. Please follow the template instructions
 % whenever possible.
@@
 %
-% Once your paper is accepted for publication and enters production, 
+% Once your paper is accepted for publication, 
 % PLEASE REMOVE ALL TRACKED CHANGES in this file and leave only
@@
 %
-% DO NOT ADD EXTRA PACKAGES TO THIS TEMPLATE unless absolutely necessary.
-% Packages included in this template are intentionally
-% limited and basic in order to reduce the possibility
-% of issues during our production process.
+% There are no restrictions on package use within the LaTeX files except that 
+% no packages listed in the template may be deleted.
+%
+% Please do not include colors or graphics in the text.
+%
+% Please do not create a heading level below \subsection. For 3rd level headings, use \paragraph{}.
 %
@@
 %
+% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
+%
 % DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
@@
 % - Figures containing multiple panels/subfigures must be combined into one image file before submission.
+% For figure citations, please use "Fig." instead of "Figure".
 % See http://www.plosone.org/static/figureGuidelines for PLOS figure guidelines.
@@
 % Tables should be cell-based and may not contain:
-% - tabs/spacing/line breaks within cells to alter layout
+% - tabs/spacing/line breaks within cells to alter layout or alignment
 % - vertically-merged cells (no tabular environments within tabular environments, do not use \multirow)
@@
 %
-% For sideways tables, use the {rotating} package and use \begin{sidewaystable} instead of \begin{table} in the appropriate section. PLOS guidelines do not accomodate sideways figures.
+% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
 %
@@
 %
-% Please be sure to include all portions of an equation in the math environment, and for any superscripts or subscripts also include the base number/text.
-For example, use $mathrm{mm}^2$ instead of mm$^2$ (do not use \textsuperscript command).
+% Please be sure to include all portions of an equation in the math environment.
 %
-% DO NOT USE the \rm command to render mathmode characters in roman font, instead use $\mathrm{}$
-% For bolding characters in mathmode, please use $\mathbf{}$ 
+% Do not include text that is not math in the math environment. For example, CO2 will be CO\textsubscript{2}.
 %
-% Please add line breaks to long equations when possible in order to fit our 2-column layout. 
+% Please add line breaks to long display equations when possible in order to fit size of the column. 
 %
-% For inline equations, please do not include punctuation within the math environment unless this is part of the equation.
+% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
 %
-% For spaces within the math environment please use the \; or \: commands, even within \text{} (do not use smaller spacing as this does not convert well).
+% % % % % % % % % % % % % % % % % % % % % % % % 
 %
+% Please contact latex@plos.org with any questions.
 %
@@
 
-\documentclass[10pt]{article}
+\documentclass[10pt,letterpaper]{article}
+\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
 
-% amsmath package, useful for mathematical formulas
-\usepackage{amsmath}
-% amssymb package, useful for mathematical symbols
-\usepackage{amssymb}
+% Use adjustwidth environment to exceed column width (see example table in text)
+\usepackage{changepage}
+
+% Use Unicode characters when possible
+\usepackage[utf8]{inputenc}
+
+% textcomp package and marvosym package for additional characters
+\usepackage{textcomp,marvosym}
+
+% fixltx2e package for \textsubscript
+\usepackage{fixltx2e}
+
+% amsmath and amssymb packages, useful for mathematical formulas and symbols
+\usepackage{amsmath,amssymb}
 
@@
 
-\usepackage{hyperref}
+% Use nameref to cite supporting information files (see Supporting Information section for more info)
+\usepackage{nameref,hyperref}
 
 % line numbers
-\usepackage{lineno}
+\usepackage[right]{lineno}
 
@@
 % rotating package for sideways tables
-%\usepackage{rotating}
+\usepackage{rotating}
 
-% If you wish to include algorithms, please use one of the packages below.
-Also, please see the algorithm section of our LaTeX guidelines (http://www.plosone.org/static/latexGuidelines) for important information about required formatting.
-%\usepackage{algorithmic}
-%\usepackage{algorithmicx}
-
-% Use doublespacing - comment out for single spacing
+% Remove comment for double spacing
 %\usepackage{setspace} 
@@
 % Text layout
-\topmargin 0.0cm
-\oddsidemargin 0.5cm
-\evensidemargin 0.5cm
-\textwidth 16cm 
-\textheight 21cm
+\raggedright
+\setlength{\parindent}{0.5cm}
+\textwidth 5.25in 
+\textheight 8.75in
 
-% Bold the 'Figure #' in the caption and separate it with a period
+% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
 % Captions will be left justified
-\usepackage[labelfont=bf,labelsep=period,justification=raggedright]{caption}
+\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
 
 % Use the PLoS provided BiBTeX style
-\bibliographystyle{plos2009}
+\bibliographystyle{plos2015}
 
@@
 
+% Header and Footer with logo
+\usepackage{lastpage,fancyhdr,graphicx}
+\usepackage{epstopdf}
 \pagestyle{myheadings}
+\pagestyle{fancy}
+\fancyhf{}
+\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
+\rfoot{\thepage/\pageref{LastPage}}
+\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
+\fancyheadoffset[L]{2.25in}
+\fancyfootoffset[L]{2.25in}
+\lfoot{\sf PLOS}
 
-%% Include all macros below. Please limit the use of macros.
+%% Include all macros below
+
+\newcommand{\lorem}{{\bf LOREM}}
+\newcommand{\ipsum}{{\bf IPSUM}}
 
@@
 \begin{document}
+\vspace*{0.35in}
 
-% Title must be 150 characters or less
+% Title must be 250 characters or less.
+% Please capitalize all terms in the title except conjunctions, prepositions, and articles.
 \begin{flushleft}
 {\Large
-\textbf{3D-Printable Micropipette}
+\textbf\newline{3D-Printable Micropipette}
 }
-% Insert Author names, affiliations and corresponding author email.
+\newline
+% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
 \\
-Author1$^{1}$, 
-Author2$^{2}$, 
-Author3$^{3,\ast}$
+Martin D. Brennan\textsuperscript{1},
+Fahad F. Bokhari\textsuperscript{1},
+David T. Eddington\textsuperscript{1,*},
+%Name4 Surname\textsuperscript{2,\ddag},
+%Name5 Surname\textsuperscript{2,\ddag},
+%Name6 Surname\textsuperscript{2},
+%Name7 Surname\textsuperscript{3,*},
+%with the Lorem Ipsum Consortium\textsuperscript{\textpilcrow}
 \\
-\bf{1} Author1 Dept/Program/Center, Institution Name, City, State, Country
-\\
-\bf{2} Author2 Dept/Program/Center, Institution Name, City, State, Country
-\\
-\bf{3} Author3 Dept/Program/Center, Institution Name, City, State, Country
-\\
-$\ast$ E-mail: Corresponding author@institute.edu
+\bigskip
+\bf{1} Department of Bioengineering, University of Illinois at Chicago, Chicago, Illinois, USA
+%\\
+%\bf{2} Affiliation Dept/Program/Center, Institution Name, City, State, Country
+%\\
+%\bf{3} Affiliation Dept/Program/Center, Institution Name, City, State, Country
+%\\
+\bigskip
+
+% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
+% 
+% Remove or comment out the author notes below if they aren't used.
+%
+% Primary Equal Contribution Note
+%\Yinyang These authors contributed equally to this work.
+
+% Additional Equal Contribution Note
+% Also use this double-dagger symbol for special authorship notes, such as senior authorship.
+%\ddag These authors also contributed equally to this work.
+
+% Current address notes
+%\textcurrency a Insert current address of first author with an address update
+% \textcurrency b Insert current address of second author with an address update
+% \textcurrency c Insert current address of third author with an address update
+
+% Deceased author note
+%\dag Deceased
+
+% Group/Consortium Author Note
+%\textpilcrow Membership list can be found in the Acknowledgments section.
+
+% Use the asterisk to denote corresponding authorship and provide email address in note below.
+* dte@uic.edu
+
 \end{flushleft}
+% Please keep the abstract below 300 words
+\section*{Abstract}
+This is the abstract.
 
-% Please keep the abstract between 250 and 300 words
-\section*{Abstract}
-
-% Please keep the Author Summary between 150 and 200 words
-% Use first person. PLOS ONE authors please skip this step. 
-% Author Summary not valid for PLOS ONE submissions.   
-%\section*{Author Summary}
+\linenumbers
 
 \section*{Introduction}
-
-3D printing as a form of additive manufacturing has existed for decades although the recent availability of inexpensive desktop printers have made it feasible for consumers to design and print prototypes and even functional parts, and consumer goods.
-
+3D printing as a form of additive manufacturing has existed for decades although the recent availability of inexpensive desktop printers have made it feasible for consumers to design and print prototypes and even functional parts, and consumer goods\cite{Fullerton2014}.
 The open source software movement and has spawned the additional areas of open source hardware, such as micro controller boards (Arduino) as well as 3D printers themselves (RepRap). 
 Open source scientific instruments and laboratory equipment are being actively developed(openpcr.org, opensource lab book.) 
-3D-printable lab equipment is and an attractive idea because of the simplicity of downloading and printing a functional object for only the price of the raw material. 
+3D-printable lab equipment is and an attractive idea because of the simplicity of downloading and printing a functional object for only the price of the raw material\cite{Waldbaur2011,Zhang2013}. 
 In addition, end users can customize the equipment to their application. 
@@
 Although this may make a rather crude centrifuge it may be and adequate method that only costs pennies compared to commercially available centrifuges and could allow researchers in the developing world to better participate in science by reducing some financial barriers of entry.
-
 Printable micropipette designs can be found on 3D-part sharing websites (thingiverse). 
@@
 
-This is a test of the citations \cite{oppegard2010}.
+%\begin{equation}\label{eq:schemeP} 
+%D_{coll} = \frac{D_f+\frac{[S]^2}{K_D S_T} D_S} {1+\frac{[S]^2}{K_D S_T}}, 
+%D_{sm} = \frac{D_f+ \frac{[S]}{K_D} D_S}{1+\frac{[S]}{K_D}},
+%\end{equation}
 
@@
 \subsection*{Design}
-The device is designed to actuate a pipette to a set distance.
-The pipette is plunger is actuated to three points, two fixed and one adjustable.
+
+The device is designed to actuate a pipette to a set distance. The pipette is plunger is actuated to three points, two fixed and one adjustable. 
 The fixed points are the dispensed point, when the plunger is all the way down, and the reset point, when the plunger is ready to withdraw fluid. 
@@
 An additional printed part adapts standard micropipette tips to the luer fitting of the pipette.
-
 Our printed pipette mimics commercial pipettes is design, function, and user operation, and is intuitive to use.
-
 3D parts were designed in Blender and SolidWorks and printed by Fineline Prototyping via selective laser sintering. 
@@
 
+\begin{figure}
+\caption{
+{\bf CAD rendering of printable parts.}  Three parts are printed: the body, plunger shaft, and luer-lock adapter for pipette tips.
+}
+\label{fig1}
+\end{figure}
+
+\begin{figure}
+\caption{
+{\bf Photos of pipette.}  The pipette is composed of three printed parts, a 1 mL syringe and some additional hardware.  
+}
+\label{fig2}
+\end{figure}
+
 \subsection*{Validation}
-
 The pipette was validated and compared to a commercial pipette. 
 The pipette was tested to see if the set point would drift between during use for example small, incremental movements of the screw or other parts causing the pipetted volume to drift. 
-To test the pipette the same volume was pipetted 50 times without moving or re-adjusting the set point. 
-The printed pipette's accuracy and precision was characterized and compared to a commercial pipette.
+To test the pipette the same volume was pipetted times without moving or re-adjusting the set point. 
+The printed pipette’s accuracy and precision was characterized and compared to a commercial pipette. 
 The printed pipette and a series of commercial pipettes were tested at volumes of 20 $\mu$L 50 $\mu$L and 200 $\mu$L. 
-The printed pipette was adjusted to the the target volume by eye from the syringe graduations, and the resulting volume was measured and repeated 5 times to account for variability
+The printed pipette was adjusted to the the target volume by eye from the syringe graduations, and the resulting volume was measured and repeated 5 times to account for variability.
 Measurements were taken from the commercial pipette in a similar way.
-
 To test user friendliness and feasibility for using the pipette without verifying with a scale, data was also gathered from novice users. 
 After a quick overview of the operation of the pipette measurements were taken after the volunteers adjusted the pipette to 200, 50, 20 and 10 $\mu$L. 
-After the first attempt was measured on the scale the volunteer was allow to adjust the set point and re-measure until within 15\% of the target volume was reached.
+After the first attempt was measured on the scale the volunteer was allowed to adjust the set point and re-measure until within 15\% of the target volume was 58 reached.
+
+% For figure citations, please use "Fig." instead of "Figure".
+%Nulla mi mi, Fig.~\ref{fig1} venenatis sed ipsum varius, volutpat euismod diam.
+Proin rutrum vel massa non gravida.
+Quisque tempor sem et dignissim rutrum.
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Morbi at justo vitae nulla elementum commodo eu id massa.
+In vitae diam ac augue semper tincidunt eu ut eros.
+Fusce fringilla erat porttitor lectus cursus, \nameref{S1_Video} vel sagittis arcu lobortis.
+Aliquam in enim semper, aliquam massa id, cursus neque.
+Praesent faucibus semper libero.
+
+\begin{figure}[h]
+\caption{{\bf Novice User efficacy.}
+Novice users were asked to pipette volumes of 200, 50, 20 and 10 $\mu$L without the use of a scale.}
+\label{fig3}
+\end{figure}
+
+%\begin{enumerate}
+%\item{react}
+%\item{diffuse free particles}
+%\item{increment time by dt and go to 1}
+%\end{enumerate}
 
@@
 
-Our printed pipette had a comparable accuracy to a commercial pipette (table 1).
+Our printed pipette had a comparable accuracy to a commercial pipette (Table~\ref{table1}).
 The commercial pipette has a digital readout that allows the user to adjust precisely to set values where the printed pipette is adjusted by eye according to graduations.
 This is certainly the cause of the lower accuracy and wider deviation although it's performance is impressive.
-
-The novice user data demonstrates that the pipette set point is user friendly and is capable of accurate measurements without validating with a scale (Figure3).
-% We only support three levels of headings, please do not create a heading level below \subsubsection.
-\subsection*{Subsection 1}
-
-\subsubsection*{SubSubsection 1.1}
-
-\subsection*{Subsection 2}
-
-\section*{Discussion}
-
-% Do NOT remove this, even if you are not including acknowledgments.
-
-\section*{Acknowledgments}
-
-%\section*{References}
-
-\bibliography{references}
-
-% Either type in your references using
-% \begin{thebibliography}{}
-% \bibitem{}
-% Text
-% \end{thebibliography}
-%
-% OR
-%
-% Compile your BiBTeX database using our plos2009.bst
-% style file and paste the contents of your .bbl file
-% here.
-%
-
-\section*{Figure Legends}
-% This section is for figure legends only, do not include3
-% graphics in your manuscript file.
-%
-%\begin{figure}
-%\includegraphics[scale=1]{file.png} % take image out for final manuscript
-%\caption{
-%{\bf Bold the first sentence.}  Rest of figure caption.  
-%}
-%\label{Figure_label}
-%\end{figure}
-
-\begin{figure}
-%\includegraphics[scale=0.4]{figure-images/rendering-assembly4.png} % take image out for final manuscript
-\caption{
-{\bf CAD rendering of printable parts.}  Three parts are printed: the body, plunger shaft, and luer-lock adapter for pipette tips.
-}
-\label{CAD-render-figure}
-\end{figure}
-
-\begin{figure}
-%\includegraphics[scale=0.04]{figure-images/pipette-disassembled.JPG} % take image out for final manuscript
-%\includegraphics[scale=0.04]{figure-images/pipette-assembled.JPG} % take image out for final manuscript
-\caption{
-{\bf Photos of pipette.}  The pipette is composed of three printed parts, a 1 mL syringe and some additional hardware.  
-}
-\label{photo-parts-figure}
-\end{figure}
-
-%\begin{figure}
-%\includegraphics[scale=1]{file.png} % take image out for final manuscript
-%\caption{
-%{\bf Bold the first sentence.}  Rest of figure caption.  
-%}
-%\label{Figure_label}
-%\end{figure}
-
-\section*{Tables}
-% 
-% See introductory notes if you wish to include sideways tables.
-%
-% NOTE: Please look over our table guidelines at http://www.plosone.org/static/figureGuidelines#tables to make sure that your tables meet our requirements.
-Certain types of spacing, cell merging, and other formatting tricks may have unintended results and will be returned for revision.
-%
-%\begin{table}[!ht]
-%\caption{
-%\bf{Table title}}
-%\begin{tabular}{|c|c|c|}
-%table information
-%\end{tabular}
-%\begin{flushleft}Table caption
-%\end{flushleft}
-%\label{tab:label}
-% \end{table}
 
@@
 \end{flushleft}
-\label{tab:comp}
+\label{table1}
  \end{table}
 
-\section*{Supporting Information Legends}
+The novice user data demonstrates that the pipette set point is user friendly and is capable of accurate measurements without validating with a scale (Figure~\ref{fig3}).
+
+%\begin{table}[!ht]
+%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+%\caption{
+%{\bf Table caption Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.}}
+%\begin{tabular}{|l|l|l|l|l|l|l|l|}
+%\hline
+%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \hline
+%$cell1 row1$ & cell2 row 1 & cell3 row 1 & cell4 row 1 & cell5 row 1 & cell6 row 1 & cell7 row 1 & cell8 row 1\\ \hline
+%$cell1 row2$ & cell2 row 2 & cell3 row 2 & cell4 row 2 & cell5 row 2 & cell6 row 2 & cell7 row 2 & cell8 row 2\\ \hline
+%$cell1 row3$ & cell2 row 3 & cell3 row 3 & cell4 row 3 & cell5 row 3 & cell6 row 3 & cell7 row 3 & cell8 row 3\\ \hline
+%\end{tabular}
+%\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl.
+Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
+%\end{flushleft}
+%\label{table1}
+%\end{adjustwidth}
+%\end{table}
+
+% Please do not create a heading level below \subsection. For 3rd level headings, use \paragraph{}.
+
+For more information, see \nameref{S1_Text}.
+
+\section*{Supporting Information}
+
+% Include only the SI item label in the subsection heading. Use the \nameref{label} command to cite SI items in the text.
+%\subsection*{S1 Video}
+%\label{S1_Video}
+%{\bf Bold the first sentence.}  Maecenas convallis mauris sit amet sem ultrices gravida.
+Etiam eget sapien nibh.
+Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
+Curabitur fringilla pulvinar lectus consectetur pellentesque.
+
+%\subsection*{S1 Text}
+%\label{S1_Text}
+%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
+Etiam eget sapien nibh.
+Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
+Curabitur fringilla pulvinar lectus consectetur pellentesque.
+
+%\subsection*{S1 Fig}
+%\label{S1_Fig}
+%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
+Etiam eget sapien nibh.
+Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
+Curabitur fringilla pulvinar lectus consectetur pellentesque.
+
+%\subsection*{S2 Fig}
+%\label{S2_Fig}
+%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
+Etiam eget sapien nibh.
+Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
+Curabitur fringilla pulvinar lectus consectetur pellentesque.
+
+%\subsection*{S1 Table}
+%\label{S1_Table}
+%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
+Etiam eget sapien nibh.
+Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
+Curabitur fringilla pulvinar lectus consectetur pellentesque.
+
+%\section*{Acknowledgments}
+%Cras egestas velit mauris, eu mollis turpis pellentesque sit amet.
+Interdum et malesuada fames ac ante ipsum primis in faucibus.
+Nam id pretium nisi.
+Sed ac quam id nisi malesuada congue.
+Sed interdum aliquet augue, at pellentesque quam rhoncus vitae.
+
+\nolinenumbers
+
+%\section*{References}
+% Either type in your references using
+% \begin{thebibliography}{}
+% \bibitem{}
+% Text
+% \end{thebibliography}
 %
-% Please enter your Supporting Information captions below in the following format:
-%\item{\bf Figure SX. Enter mandatory title here.} Enter optional descriptive information here.
+% OR
 %
-%\begin{description}
-%\item {\bf}
-%\item {\bf}
-%\end{description}
+% Compile your BiBTeX database using our plos2015.bst
+% style file and paste the contents of your .bbl file
+% here.
+% 
+\bibliographystyle{plos2015.bst}
+\bibliography{references}
 

### 2016-02-03 Plos-one-manuscript/latex/manuscript.tex
update

@@
 
+\usepackage{multirow}
+
 % Remove comment for double spacing
@@
 \section*{Abstract}
-This is the abstract.
+Open source development of lab equipment is being facilitated, in part, by growing availability of 3D printing which allows the production of simple lab tools.
+We developed 3D-printable parts that, along with a disposable syringe, form a micropipette.
+Once assembled the pipette requires no calibration or validation with a scale.
+Our printed micropipette is assessed in comparison to a commercial pipette demonstrating comparable performance in accuracy and precision and approaches ISO standard.
 
@@
 \section*{Introduction}
-3D printing as a form of additive manufacturing has existed for decades although the recent availability of inexpensive desktop printers have made it feasible for consumers to design and print prototypes and even functional parts, and consumer goods\cite{Fullerton2014}.
-The open source software movement and has spawned the additional areas of open source hardware, such as micro controller boards (Arduino) as well as 3D printers themselves (RepRap). 
-Open source scientific instruments and laboratory equipment are being actively developed(openpcr.org, opensource lab book.) 
-3D-printable lab equipment is and an attractive idea because of the simplicity of downloading and printing a functional object for only the price of the raw material\cite{Waldbaur2011,Zhang2013}. 
-In addition, end users can customize the equipment to their application. 
-Some of the more clever printable parts that have emerged are ones that give a new function to a ubiquitous existing device. 
-For example a drill bit attachment was designed and printed to hold micro centrifuge tubes allowing a drill to be used for centrifuging samples. 
-Although this may make a rather crude centrifuge it may be and adequate method that only costs pennies compared to commercially available centrifuges and could allow researchers in the developing world to better participate in science by reducing some financial barriers of entry.
-Printable micropipette designs can be found on 3D-part sharing websites (thingiverse). 
-While existing designs may require only pen springs, a gasket made from a balloon, and tape, none allow adjustment to know volumes nor have any been rigorously validated. 
-We present a pipette constructed from 3D printed parts that allows a 1 ml syringe to be actuated to an adjustable volume. 
+The open source development model, initially applied to software, is thriving in the development of open source scientific equipment due in part to increasing access of 3D printing \cite{Baden2015,Pearce2014}.
+Open design 3D-printable lab equipment is and attractive idea because, like open source software, it allows free access to technology that is otherwise inaccessible due to proprietary and/or financial barriers.
+Open design tools create opportunity for scientists and educational programs in remote or resource limited areas to participate with inexpensive and easy to make tools\cite{Baden2015}. 
+Open source development also enables the development of custom solutions to meet unique applications not met by commercial products that are shared freely and are user modifiable\cite{Fullerton2014,Pearce2012}.
+Some advanced, noteworthy open-source scientific equipment include a PCR device\cite{ChaiBiotechnologiesInc2015}, and a two-photon microscope\cite{Rosenegger2014} although even simple tools are impactful especially if the fabrication is simplified by 3D printing.
+%The user is required to assemble the tools requiring them the learn how it functions.
+%The user is then equipped to diagnose problems and enact their own fixes and changes which is limited when dealing with commercial products.
+
+3D printing as a form of additive manufacturing has existed for decades although the recent availability of inexpensive desktop printers\cite{MakerbotIndustries2016,Reprap2015} have made it feasible for consumers to design and print prototypes and even functional parts, and consumer goods\cite{Fullerton2014}.
+Proliferation of free CAD software[OpenSCAD, Blender, SketchUp] and design sharing sites\cite{MakerbotIndustries2016,NationalInstitutesofHealth2015,grabCAD,GitHubInc.2016} have also supported the growth and popularity of open designed parts and projects.
+Some simple and clever printable parts that have emerged are ones that give a new function to a ubiquitous existing device such as drill bit attachment designed to hold centrifuge tubes, turning the drill into a centrifuge\cite{Garvey2009}.
+Although this may make a rather crude centrifuge it may be and adequate method that only costs pennies compared to commercially available centrifuges.
+Other examples of open-design research tools that utilize 3D printed parts include optics equipment\cite{Zhang2013}, microscopes\cite{Baden2014a,Walus2014}, syringe pumps\cite{Wijnen2014}, and reactionware\cite{Symes2012} to name a few.
+
+There are a few open design printable micropipettes including a popular one which uses parts scavenged from a retractable pen in addition to the printed parts\cite{Baden2014}.
+An air displacement pipette uses a piston operating principal to draw liquid into the pipette.
+In a typical commercial pipette the piston is made gas-tight with a gasketed plunger inside a smooth barrel.
+Consumer grade fused deposition modeling (FDM) printers are unable to form a smooth surface do to the formation of ridges that occur as each layer that is deposited.
+The ridges formed by FDM make it impractical to form a gas-tight seal between moving parts, even with a gasket.
+Printable open-design micropipettes get around this limitation by stretching a membrane over one end of a printed tube, which when pressed causes the displacement.
+The displacement membrane can be made from any elastic material such as a latex glove.
+After assembly this design requires the user to validate the volumes dispensed with a high precision scale.
+%uncertianty  
+Without verification with a scale the volumes dispensed can only be estimated based on theoretical displacement intended by the design.
+There is no built-in feature such as a digital readout for the user to set the displacement to a desired volume.
+The pipette can be calibrated to a specific volume with a set screw but if a new volume is desired it has to be re-adjusted and validated with a scale.
+%In addition no open-design pipettes have be rigorously validated.
+
+We present a new open design 3D-printable micropipette that works by actuating a 1 mL syringe to a user adjustable set-point.
+This allows the user to set the pipette to a volume a priori by reading the graduations of the syringe barrel.
 The scale marks on the syringe can be used to adjust the dispensed volume accurately without calibrating with a scale.
+Our pipette also offers a simplified assembly requiring no glue, tape or permanent connections.
+
+%range of 226 ul, one tip size per pipette
 
@@
 
-The device is designed to actuate a pipette to a set distance. The pipette is plunger is actuated to three points, two fixed and one adjustable. 
-The fixed points are the dispensed point, when the plunger is all the way down, and the reset point, when the plunger is ready to withdraw fluid. 
-The adjustable point is the set point, which determines the volume of fluid that will be drawn into the pipette and depends on the position of the screw. 
-The system is spring loaded towards the set point. 
-A spring notch, in the plunger shaft part, and a groove, in the body part, hold the plunger at the reset position where it can be released by pressing in the notch. 
-A 1 ml BD syringe twists to lock into the body part. 
+Our printed pipette is designed to actuate a 1 mL syringe to a user set displacement.
+The core of the design is two printed parts, the body and the plunger.
+A 1 mL BD syringe twists to lock in the body part and is held into place by the syringe flanges.
+The plunger part slides freely in the body part and actuates the syringe by pushing the thumb press. 
+The pipette is spring loaded towards a set point which is adjustable by a set-screw. 
+When the plunger is depressed the system locks when it reaches the ready point, where it is ready to draw in fluid.
+The plunger is held in place with a notch and groove design which is then released with a lever drawing in fluid. 
+The displacement is directly readable with the syringe graduations and is equal to the distance between the set and the ready point.
+The pipette can also be pressed past the ready point to purge the transfered fluid completely from the pipette tip.   
 An additional printed part adapts standard micropipette tips to the luer fitting of the pipette.
-Our printed pipette mimics commercial pipettes is design, function, and user operation, and is intuitive to use.
-3D parts were designed in Blender and SolidWorks and printed by Fineline Prototyping via selective laser sintering. 
-Additional materials include a spring, a nut and bolt and two washers.
+Additional materials required for assembly include a spring, a nut and bolt and washers.
+
+Our printed pipette mimics commercial pipettes's design, function, and user operation, making it intuitive to use.
+It also can reach to the bottom of a 15 mL conical tube.
+
+%3D parts were designed in Blender and SolidWorks and printed by Fineline Prototyping via selective laser sintering.
 
@@
 \label{fig1}
+% Ideally: cad rendering showing the design and function of the pipette. 
+% a) Un-assembled whole parts next to their cross-sections.  
+% b) Assembly next to crossection
+% c) close up of how the locking groove/mechanism works
+% d) cross-section showing the two positions of the plunger, locked at the goove and stopped at the screw 
 \end{figure}
@@
 \label{fig2}
+% Ideally: Photo showing assembled pipette as well as parts
 \end{figure}
@@
 The pipette was tested to see if the set point would drift between during use for example small, incremental movements of the screw or other parts causing the pipetted volume to drift. 
-To test the pipette the same volume was pipetted times without moving or re-adjusting the set point. 
+To test the pipette the same volume was pipetted 50 times without moving or re-adjusting the set point. 
 The printed pipette’s accuracy and precision was characterized and compared to a commercial pipette. 
@@
 Measurements were taken from the commercial pipette in a similar way.
+
 To test user friendliness and feasibility for using the pipette without verifying with a scale, data was also gathered from novice users. 
+This group included researchers experienced with pipettes as well as undergraduates with little to no experience pipetting at all.
 After a quick overview of the operation of the pipette measurements were taken after the volunteers adjusted the pipette to 200, 50, 20 and 10 $\mu$L.
-After the first attempt was measured on the scale the volunteer was allowed to adjust the set point and re-measure until within 15\% of the target volume was 58 reached.
+
+For the printed pipette the 1000 $\mu$L tips were used for the 200 $\mu$L measurement. 100 $\mu$L tips were used for the 50, 20 and 10 $\mu$L measurements.
+
+compare the force required to press the button.
+
+compare the weight of the pipettes
+
+%After the first attempt was measured on the scale the volunteer was allowed to adjust the set point and re-measure until within 15\% of the target volume was reached.
 
@@
 The commercial pipette has a digital readout that allows the user to adjust precisely to set values where the printed pipette is adjusted by eye according to graduations.
+Due to being unable to re-set the printed pipette back to the exact mechanical location it may be hard to compare directly with the commercial pipettes.
 This is certainly the cause of the lower accuracy and wider deviation although it's performance is impressive.
+Despite this additional variability the printed pipette's accuracy and precision approaches the ISO 8655 standard.
 
-\begin{table}[!ht]
+The Novice user data demonstrates that even someone inexperienced with pipetting and unfamiliar with our design is able to use out pipette accurately with out the use of a scale. 
+The systematic error trended towards over estimating the displacement. 
+This is likely due the function of adjusting the volume where it is easier to start at a lower displacement and increase it by unscrewing, or releasing compression of the spring.
+This explains the negative systematic error as the user avoids 'going over'.
+
+This pipette improves on existing open design pipettes in several ways. 
+It requires only two printed parts, a syringe, and some hardware.
+It is able to reach into a 15 mL conical tube which is a routine requirement for cell culture.
+No permanent connections using tape or glue are required for assembly allowing worn out or broken part to be replaced easily.
+Assembly does not require a membrane that may wear or stretch and require tedious replacement.
+No validation or calibration is required.
+The pipette can be assembled and used to accurately pipette micro volumes without first validating with a scale.
+
+The only major limitation of this design compared to the briopipette is the option for a pipette tip ejector, although incorporation of a similar design in our pipette would not leave room for it to reach into a 15 mL conical tube.
+Our pipette requires a syringe and some additional hardware where briopipette's additional parts can be obtained virtually anywhere.
+The briopipette also allows step-wise shifts in displacement allowing the user to quickly change to a relative volume
+
+% Please add the following required packages to your document preamble:
+% \usepackage{multirow}
+\begin{table}[]
+\centering
 \caption{
-\bf{Comparison of Accuracy and Precision}}
-\begin{tabular}{|c|c|c|c|}
+\bf{Comparison of error between the printed and commercially produced pipette}}
+\begin{tabular}{llllll}
+                  Volume &   & Systematic error &  & Random error & \\
                   \hline
-    Target Volume & 20 $\mu$L & 50 $\mu$L & 200 $\mu$L  \\
+\multirow{2}{*}{10 $\mu$L} & printed & 2.17 \% & $\pm$0.217$\mu$L  & 1.96\% & $\pm$0.196$\mu$L   \\
+                  & commercial & 3\% & $\pm$0.3$\mu$L  & 1\% & $\pm$0.1$\mu$L  \\
                   \hline
-    Printed Pipette & 196.4 $\pm$ 2.2 & 53.5 $\pm$ 1.8 & 19.5 $\pm$ 0.6 \\
-    Commercial Pipette & 204.5 $\pm$ 2.9 & 49.9 $\pm$ 0.1 & 19.9 $\pm$ 0.2 \\
+\multirow{2}{*}{20 $\mu$L} & printed  & 0.33\% & $\pm$0.066$\mu$L & 1.18 \% & $\pm$0.236$\mu$L \\
+                  & commercial & 2.50\% & $\pm$0.5$\mu$L & 0.70\% & $\pm$0.14$\mu$L \\
                   \hline
+\multirow{2}{*}{50 $\mu$L} & printed & 1.17\% & $\pm$0.585$\mu$L & 0.50\% & $\pm$0.25$\mu$L \\
+                  & commercial & 1\% & $\pm$0.5$\mu$L & 0.30\% & $\pm$0.15$\mu$L \\
+                  \hline
+\multirow{2}{*}{200 $\mu$L} & printed & 2.52\% & $\pm$5.04$\mu$L & 0.69\% & $\pm$1.38$\mu$L  \\
+                  & commercial & 0.6\% & $\pm$1.2$\mu$L & 0.20\% & $\pm$0.4$\mu$L
 \end{tabular}
-\begin{flushleft} Average measured volume by weight and standard deviation.
+\begin{flushleft} Error assessed for average measured volume by weight of water compared with published specifications of commercial pipette.
+[Alos compare to data taken with commercial pipettes in our lab]
 \end{flushleft}
@@
 The novice user data demonstrates that the pipette set point is user friendly and is capable of accurate measurements without validating with a scale (Figure~\ref{fig3}).
+
+\begin{table}[]
+\centering9
+\caption{
+\bf{Novice Users' first attempt}}
+\begin{tabular}{llll}
+Target volume & Average $\pm$ SD & Systematic error  & Random error\\
+\hline
+10 $\mu$L         & 7.6 $\pm$ 3.3     & -23.80\% & 9.95\% \\
+\hline
+20 $\mu$L         & 18.1 $\pm$ 4.4   & -9.60\%   & 6.66\% \\
+\hline
+50 $\mu$L         & 45.3 $\pm$ 4.6   & -9.48\%   & 2.75\% \\
+\hline
+200 $\mu$L       & 185.2 $\pm$ 5.6 & -7.43\%   & 0.84\%
+\end{tabular}
+\begin{flushleft} Error assessed for average measured volume by weight of water compared with published specifications of commercial pipette.
+\end{flushleft}
+\label{table2}
+\end{table}
 

### 2016-02-03 data/user-data.R
cleaned up data folder

@@ -1,23 +1,0 @@
-par(mfrow=c(1,4)) 
-novice_user_data <- read.csv(file='novice_user_data.csv', sep=',', header=FALSE)
-x200 <- c(200, 200, 200, 200, 200, 200)
-plot(x200, novice_user_data$V1, ylim=c(150,280), axes=FALSE, ann=FALSE, cex=2)
-points(200,mean(novice_user_data$V1), col="red", pch=3, cex=3)
-axis(1, at=200, lab="200 uL", cex.axis=1.4)
-Axis(side=2, cex.axis=1.3)
-x50 <- c(50, 50, 50, 50, 50, 50)
-plot(x50, novice_user_data$V2, ylim=c(30,60), axes=FALSE, ann=FALSE, cex=2)
-points(50,mean(novice_user_data$V2), col="red", pch=3, cex=3)
-axis(1, at=50, lab="50 uL", cex.axis=1.4)
-Axis(side=2, cex.axis=1.3)
-x20 <- c(20, 20, 20, 20, 20, 20)
-plot(x20, novice_user_data$V3, ylim=c(10,30), axes=FALSE, ann=FALSE, cex=2)
-points(20,mean(novice_user_data$V3), col="red", pch=3, cex=3)
-axis(1, at=20, lab="20 uL", cex.axis=1.4)
-Axis(side=2, cex.axis=1.3)
-x10 <- c(10, 10, 10, 10, 10, 10)
-plot(x10, novice_user_data$V4, ylim=c(0,15), axes=FALSE, ann=FALSE, cex=2)
-points(10,mean(novice_user_data$V4), col="red", pch=3, cex=3)
-axis(1, at=10, lab="10 uL", cex.axis=1.4)
-Axis(side=2, cex.axis=1.3)
-title(main="Novice Users' First Attempt", font.main=1, cex.main=2.7, line=-2, outer=TRUE)

### 2016-02-03 data/novice-user-data/user-data.R
clean up data folder

@@ -1,0 +1,23 @@
+par(mfrow=c(1,4)) 
+novice_user_data <- read.csv(file='novice_user_data.csv', sep=',', header=FALSE)
+x200 <- c(200, 200, 200, 200, 200, 200)
+plot(x200, novice_user_data$V1, ylim=c(150,280), axes=FALSE, ann=FALSE, cex=2)
+points(200,mean(novice_user_data$V1), col="red", pch=3, cex=3)
+axis(1, at=200, lab="200 uL", cex.axis=1.4)
+Axis(side=2, cex.axis=1.3)
+x50 <- c(50, 50, 50, 50, 50, 50)
+plot(x50, novice_user_data$V2, ylim=c(30,60), axes=FALSE, ann=FALSE, cex=2)
+points(50,mean(novice_user_data$V2), col="red", pch=3, cex=3)
+axis(1, at=50, lab="50 uL", cex.axis=1.4)
+Axis(side=2, cex.axis=1.3)
+x20 <- c(20, 20, 20, 20, 20, 20)
+plot(x20, novice_user_data$V3, ylim=c(10,30), axes=FALSE, ann=FALSE, cex=2)
+points(20,mean(novice_user_data$V3), col="red", pch=3, cex=3)
+axis(1, at=20, lab="20 uL", cex.axis=1.4)
+Axis(side=2, cex.axis=1.3)
+x10 <- c(10, 10, 10, 10, 10, 10)
+plot(x10, novice_user_data$V4, ylim=c(0,15), axes=FALSE, ann=FALSE, cex=2)
+points(10,mean(novice_user_data$V4), col="red", pch=3, cex=3)
+axis(1, at=10, lab="10 uL", cex.axis=1.4)
+Axis(side=2, cex.axis=1.3)
+title(main="Novice Users' First Attempt", font.main=1, cex.main=2.7, line=-2, outer=TRUE)

### 2016-02-10 Plos-one-manuscript/latex/manuscript.tex
working on manuscript

@@
 \end{flushleft}
+\label{table0}
+\end{table}
+
+\begin{table}[]
+\centering
+\caption{\bfseries{Commercial and Printed pipettes compared to ISO standard 8655.}}
+\label{my-label}
+\begin{tabular}{lllllll}
+Volume & Pipette & Mean   & SE    & \% SE & RE & \% RE \\
+       & ISO, 20-200 $\mu$L & 200 $\mu$L       & $\pm$1.60         & $\pm$0.08          & 0.60 & 0.30 \\
+200 $\mu$L & Commercial & 198.23       & -1.77        & -0.88         & 1.14 & 0.58 \\
+       & Printed  & 193.40       & -6.60        & -3.30         & 2.86 & 1.48 \\
+       &                     &              &              &               &      &      \\
+       & ISO, 20-200 $\mu$L & 50 $\mu$L        & $\pm$1.60         &$\pm$3.20          & 0.60 & 1.20 \\
+50 $\mu$L  & Commercial   & 48.89        & -1.11        & -2.23         & 0.71 & 1.46 \\
+       & Printed      & 49.62        & -0.38        & -0.76         & 1.26 & 2.53 \\
+       &                     &              &              &               &      &      \\
+       & ISO, 20-200 $\mu$L & 20 $\mu$L        & $\pm$1.60         & $\pm$8.00          & 0.60 & 3.00 \\
+20 $\mu$L  & Commercial   & 20.16        & 0.16         & 0.81          & 0.16 & 0.81 \\
+       & Printed     & 18.70        & -1.30        & -6.48         & 0.38 & 2.01 \\
+       &                     &              &              &               &      &      \\
+       & ISO, 10-100 $\mu$L & 10 $\mu$L        & $\pm$0.80         & $\pm$8.00          & 0.30 & 3.00 \\
+10 $\mu$L  & Commercial   & 9.88         & -0.12        & -1.23         & 0.34 & 3.39 \\
+       & Printed      & 11.95        & 1.95         & 19.52         & 0.73 & 6.08 \\
+       &                     &              &              &               &      &      \\
+       & ISO, 20-200 $\mu$L & 10 $\mu$L        & $\pm$1.60         & $\pm$16.00         & 0.60 & 6.00 \\
+10 $\mu$L* & Commercial   & 9.88         & -0.12        & -1.23         & 0.34 & 3.39 \\
+       & Printed      & 11.95        & 1.95         & 19.52         & 0.73 & 6.08
+\end{tabular}
+\begin{flushleft} Commercial and Printed pipettes compared to ISO standard 8655.
+\end{flushleft}
 \label{table1}

### 2016-02-12 data/commerical-Vs-printed-comparison/analysis/analysis.R
added data for 3mL

@@ -49,22 +49,59 @@ se.p.com.10 = 100*(se.vol.com.10/10)
 analyzed.com.10 = c(m.com.10, se.vol.com.10, se.p.com.10, re.vol.com.10, re.p.com.10)
 
 #printed pipette data
+printed_1000uL <- read.csv(file='1000uL_printed.csv', sep=',')
+printed_500uL <- read.csv(file='500uL_printed.csv', sep=',')
+printed_200uL_3mL <- read.csv(file='200uL_printed_3mL.csv', sep=',')
+
 printed_200uL <- read.csv(file='200uL_printed.csv', sep=',')
 printed_50uL <- read.csv(file='50uL_printed.csv', sep=',')
 printed_20uL <- read.csv(file='20uL_printed.csv', sep=',')
 printed_10uL <- read.csv(file='10uL_printed.csv', sep=',')
 
 # Conversion to volume from mass
+vol.prt.1000 = printed_1000uL*1.0038
+vol.prt.500 = printed_500uL*1.0038
+vol.prt.200_3mL = printed_200uL_3mL*1.0038
+
 vol.prt.200 = printed_200uL*1.0038
 vol.prt.50 = printed_50uL*1.0038
 vol.prt.20 = printed_20uL*1.0038
 vol.prt.10 = printed_10uL*1.0038
 
 #take mean of 5 transfers for each tip
+m.tips.prt.1000 = colMeans(vol.prt.1000)
+m.tips.prt.500 = colMeans(vol.prt.500)
+m.tips.prt.200_3mL = colMeans(vol.prt.200_3mL)
+
 m.tips.prt.200 = colMeans(vol.prt.200)
 m.tips.prt.50 = colMeans(vol.prt.50)
 m.tips.prt.20 = colMeans(vol.prt.20)
 m.tips.prt.10 = colMeans(vol.prt.10)
+
+#1000 uL
+m.prt.1000 = mean(m.tips.prt.1000)
+re.vol.prt.1000 = sd(m.tips.prt.1000)
+re.p.prt.1000 = 100*(re.vol.prt.1000/m.prt.1000)
+se.vol.prt.1000 = mean(m.tips.prt.1000) - 1000
+se.p.prt.1000 = 100*(se.vol.prt.1000/1000)
+analyzed.prt.1000 = c(m.prt.1000, se.vol.prt.1000, se.p.prt.1000, re.vol.prt.1000, re.p.prt.1000)
+
[…]

### 2016-08-12 Plos-one-manuscript/latex/manuscript.tex
update
added new figure updated tables

--- 2016-02-03 Plos-one-manuscript/latex/manuscript.tex
@@
 \caption{
+{\bf CAD rendering of printable parts.}  Three parts are printed: the body, plunger shaft, and luer-lock adapter for pipette tips.
+}
+\label{fig2}
+% Ideally: cad rendering showing the design and function of the pipette. 
+% a) Un-assembled whole parts next to their cross-sections.  
+% b) Assembly next to crossection
+% c) close up of how the locking groove/mechanism works
+% d) cross-section showing the two positions of the plunger, locked at the goove and stopped at the screw 
+\end{figure}
+
+\begin{figure}
+\caption{
 {\bf Photos of pipette.}  The pipette is composed of three printed parts, a 1 mL syringe and some additional hardware.  
 }
-\label{fig2}
+\label{fig3}
 % Ideally: Photo showing assembled pipette as well as parts
@@
 % \usepackage{multirow}
-\begin{table}[]
+\begin{table}[!ht]
+\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
 \centering
-\caption{
-\bf{Comparison of error between the printed and commercially produced pipette}}
-\begin{tabular}{llllll}
-                  Volume &   & Systematic error &  & Random error & \\
-                  \hline
-\multirow{2}{*}{10 $\mu$L} & printed & 2.17 \% & $\pm$0.217$\mu$L  & 1.96\% & $\pm$0.196$\mu$L   \\
-                  & commercial & 3\% & $\pm$0.3$\mu$L  & 1\% & $\pm$0.1$\mu$L  \\
-                  \hline
-\multirow{2}{*}{20 $\mu$L} & printed  & 0.33\% & $\pm$0.066$\mu$L & 1.18 \% & $\pm$0.236$\mu$L \\
-                  & commercial & 2.50\% & $\pm$0.5$\mu$L & 0.70\% & $\pm$0.14$\mu$L \\
-                  \hline
-\multirow{2}{*}{50 $\mu$L} & printed & 1.17\% & $\pm$0.585$\mu$L & 0.50\% & $\pm$0.25$\mu$L \\
-                  & commercial & 1\% & $\pm$0.5$\mu$L & 0.30\% & $\pm$0.15$\mu$L \\
-                  \hline
-\multirow{2}{*}{200 $\mu$L} & printed & 2.52\% & $\pm$5.04$\mu$L & 0.69\% & $\pm$1.38$\mu$L  \\
-                  & commercial & 0.6\% & $\pm$1.2$\mu$L & 0.20\% & $\pm$0.4$\mu$L
+\caption{ISO 8655 for 100-1000 uL comparing a commercial pipette with our printed pipette used with existing 3 mL syringe scale and an adjusted scale}
+\label{table1}
+\begin{tabular}{lllllll}
+        &                       & Mean   & Systematic Error & \% Sys. err. & Random Error & \% Rand. err. \\
+1000 uL & ISO 8655, 100-1000 uL & 1000    & 8.00             & 0.80         & 3.00         & 0.30          \\
+        & Commercial Pipette    & 1002.98 & 2.98             & 0.30         & 1.72         & 0.17          \\
+        & Printed Pipette       & 949.29  & -50.71           & -5.07        & 0.60         & 0.06          \\
+        & Printed Pipette Scale & 1003.57 & 3.57             & 0.36         & 0.89         & 0.09          \\
+        &                       &         &                  &              &              &               \\
+500 uL  & ISO 8655, 100-1000 uL & 500     & 8.00             & 1.60         & 3.00         & 0.60          \\
+        & Commercial Pipette    & 503.67  & 3.67             & 0.73         & 0.49         & 0.10          \\
+        & Printed Pipette       & 475.99  & -24.01           & -4.80        & 4.75         & 1.00          \\
+        & Printed Pipette Scale & 503.62  & 3.62             & 0.72         & 1.64         & 0.33          \\
+        &                       &         &                  &              &              &               \\
+200 uL  & ISO 8655, 100-1000 uL & 200     & 8.00             & 4.00         & 3.00         & 1.50          \\
+        & Commercial Pipette    & 204.61  & 4.61             & 2.30         & 0.15         & 0.07          \\
+        & Printed Pipette       & 186.55  & -13.45           & -6.72        & 1.31         & 0.70          \\
+        & Printed Pipette Scale & 201.87  & 1.87             & 0.94         & 1.47         & 0.73          \\
+        &                       &         &                  &              &              &               \\
+100 uL  & ISO 8655, 100-1000 uL & 100     & 8.00             & 8.00         & 3.00         & 3.00          \\
+        & Commercial Pipette    & 104.29  & 4.29             & 4.29         & 1.65         & 1.58          \\
+        & Printed Pipette       & 94.02   & -5.98            & -5.98        & 4.81         & 5.12          \\
+        & Printed Pipette Scale & 101.00  & 1.00             & 1.00         & 1.05         & 1.04         
 \end{tabular}
-\begin{flushleft} Error assessed for average measured volume by weight of water compared with published specifications of commercial pipette.
-[Alos compare to data taken with commercial pipettes in our lab]
-\end{flushleft}
-\label{table1}
+%\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl.
+Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
+%\end{flushleft}
+\end{adjustwidth}
 \end{table}
 
-The novice user data demonstrates that the pipette set point is user friendly and is capable of accurate measurements without validating with a scale (Figure~\ref{fig3}).
-
-\begin{table}[]
-\centering9
-\caption{
-\bf{Novice Users' first attempt}}
-\begin{tabular}{llll}
-Target volume & Average $\pm$ SD & Systematic error  & Random error\\
-\hline
-10 $\mu$L         & 7.6 $\pm$ 3.3     & -23.80\% & 9.95\% \\
-\hline
-20 $\mu$L         & 18.1 $\pm$ 4.4   & -9.60\%   & 6.66\% \\
-\hline
-50 $\mu$L         & 45.3 $\pm$ 4.6   & -9.48\%   & 2.75\% \\
-\hline
-200 $\mu$L       & 185.2 $\pm$ 5.6 & -7.43\%   & 0.84\%
+\begin{table}[!ht]
+\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\centering
+\caption{ISO 8655 for 30-300 uL comparing a commercial pipette with our printed pipette used with existing 3 mL syringe scale and an adjusted scale}
+\label{table2}
+\begin{tabular}{lllllll}
+       &                       & Mean   & Systematic Error & \% Sys. err. & Random Error & \% Rand. err. \\
+300 uL & ISO 8655, 30-300 uL   & 300    & 4.00             & 1.33         & 1.50         & 0.50          \\
+       & Commercial Pipette    & 301.19 & 1.19             & 0.40         & 0.53         & 0.18          \\
+       & Printed Pipette       & 286.91 & -13.09           & -4.36        & 0.42         & 0.15          \\
+       & Printed Pipette Scale & 299.11 & -0.89            & -0.30        & 0.48         & 0.16          \\
+       &                       &        &                  &              &              &               \\
+200 uL & ISO 8655, 30-300 uL   & 200    & 4                & 2            & 1.5          & 0.75          \\
+       & Commercial Pipette    & 200.06 & 0.06             & 0.03         & 0.46         & 0.23          \\
+       & Printed Pipette       & 193.40 & -6.60            & -3.30        & 2.86         & 1.48          \\
+       & Printed Pipette Scale & 200.57 & 0.57             & 0.28         & 0.86         & 0.43          \\
+       &                       &        &                  &              &              &               \\
+50 uL  & ISO 8655, 30-300 uL   & 50     & 4                & 8            & 1.5          & 3             \\
+       & Commercial Pipette    & 49.02  & -0.98            & -1.96        & 0.10         & 0.20          \\
+       & Printed Pipette       & 49.62  & -0.38            & -0.76        & 1.26         & 2.53          \\
+       & Printed Pipette Scale & 48.73  & -1.27            & -2.54        & 1.11         & 2.27          \\
+       &                       &        &                  &              &              &               \\
+30 uL  & ISO 8655, 30-300 uL   & 30     & 4                & 13.3         & 1.5          & 5             \\
+       & Commercial Pipette    & 29.08  & -0.92            & -3.06        & 0.09         & 0.31          \\
+       & Printed Pipette       & 29.22  & -0.78            & -2.59        & 0.31         & 1.07          \\
+       & Printed Pipette Scale & 27.78  & -2.22            & -7.41        & 1.37         & 4.93          \\
+       &                       &        &                  &              &              &               \\
+20 uL* & ISO 8655, 30-300 uL   & 20     & 4                & 20           & 1.5          & 7.5           \\
+       & Commercial Pipette    & NA     & NA               & NA           & NA           & NA            \\
+       & Printed Pipette       & 18.70  & -1.30            & -6.48        & 0.38         & 2.01          \\
+       & Printed Pipette Scale & 17.94  & -2.06            & -10.29       & 1.87         & 10.42         \\
+       &                       &        &                  &              &              &               \\
+10 uL* & ISO 8655, 30-300 uL   & 10     & 4                & 40           & 1.5          & 15            \\
+       & Commercial Pipette    & NA     & NA               & NA           & NA           & NA            \\
+       & Printed Pipette       & 11.95  & 1.95             & 19.52        & 0.73         & 6.08          \\
+       & Printed Pipette Scale & 7.64   & -2.36            & -23.64       & 0.38         & 4.92         
 \end{tabular}
-\begin{flushleft} Error assessed for average measured volume by weight of water compared with published specifications of commercial pipette.
+\begin{flushleft} * The 20 uL and 10 uL volumes are out of the range in this case but we wanted to demonstrate that the pipette is capable of even smaller volumes.
 \end{flushleft}
-\label{table2}
+\end{adjustwidth}
 \end{table}

### 2016-08-19 Plos-one-manuscript/latex/manuscript.tex
clean up and working on figures
working on manuscript

@@
 
-Our printed pipette is designed to actuate a 1 mL syringe to a user set displacement.
-The core of the design is two printed parts, the body and the plunger.
+Our printed pipette is designed to actuate a 1 mL or 3 mL syringe to a user set displacement.
+The core of the design is two printed parts, the body and the plunger which are able to be printed on a consumer grade FDM printer.
 A 1 mL BD syringe twists to lock in the body part and is held into place by the syringe flanges.
@@
 The pipette is spring loaded towards a set point which is adjustable by a set-screw. 
-When the plunger is depressed the system locks when it reaches the ready point, where it is ready to draw in fluid.
-The plunger is held in place with a notch and groove design which is then released with a lever drawing in fluid.
-The displacement is directly readable with the syringe graduations and is equal to the distance between the set and the ready point.
-The pipette can also be pressed past the ready point to purge the transfered fluid completely from the pipette tip.   
-An additional printed part adapts standard micropipette tips to the luer fitting of the pipette.
+When the plunger is depressed the system locks when it reaches the latched position, where it is ready to draw in fluid.
+The plunger is held in place with a latching button design which is released with a lever drawing in fluid.
+The displacement is equal to the distance between the set position and the latched position.
+The pipette can also be pressed past the latched position to 'blow-out' the transfered fluid completely from the pipette tip.   
 Additional materials required for assembly include a spring, a nut and bolt and washers.
+Attempts to make a printable luer lock adapter for tips was abandoned as the surface of printed parts is too rough to make an air tight seal with the luer or pipette tip.
+Instead a combination of a barbed luer adapter and elastic tubing was used to attach the pipette tips.
 
 Our printed pipette mimics commercial pipettes's design, function, and user operation, making it intuitive to use.
-It also can reach to the bottom of a 15 mL conical tube.
+The button is pressed with the thumb until the latched position is reached.
+The the tip immersed in fluid and drawn in by actuating the lever with the palm or fingers.
+Conveniently this design can also reach to the bottom of a 15 mL conical tube allowing tasks such as aspirating supernatant fluid from a cell pellet where existing printed designs cannot.
+
+Our pipette uses the air-displacement design, where a pocket of air is used to draw liquid into the pipette.
+As air is an expansible fluid, this pocket of air expands due to the weight of the liquid pulling on it.
+Due to this effect the graduations on the syringe are not accurate, as they are designed for measuring liquid within the syringe.
+At larger volumes this is more pronounced where the volume of are measured is greater then the amount of liquid pulled into the syringe.
+
+when the liquid volume is pulling due to the force of gravity.
+This effect increases as the larger volumes are transfered.
+Due to the expandability of air the graduations on the syringe are not accurate.
+This effect is the greatest at larger volumes corresponding to a greater mass pulling on the air pocket.
+The pocket of air that is drawing in the water is stretched causing the inaccurate readings.
+We remedied this by creating a new scale to account for the expansion.
+The scale which is printed on a transparency sheet is pasted on the syringe as a guide for the set point.
+%Testing taken with the original scale along with the adjusted scale is shown in table 1 and 2.
 
@@
 \caption{
-{\bf CAD rendering of printable parts.}  Three parts are printed: the body, plunger shaft, and luer-lock adapter for pipette tips.
+{\bf CAD renderings of printable parts.} Two parts are printed: The plunger part (A) slides inside the body part (B).
 }
-\label{fig2}
+\label{fig1}
 % Ideally: cad rendering showing the design and function of the pipette. 
@@
 \subsection*{Validation}
-The pipette was validated and compared to a commercial pipette. 
+The printed pipette was validated and compared to a commercial pipette. 
 The pipette was tested to see if the set point would drift between during use for example small, incremental movements of the screw or other parts causing the pipetted volume to drift. 
 To test the pipette the same volume was pipetted 50 times without moving or re-adjusting the set point.
+A small amount of paraffin wax was applied to the screw to prevent it from slipping during each actuation. 
 The printed pipette’s accuracy and precision was characterized and compared to a commercial pipette.
-The printed pipette and a series of commercial pipettes were tested at volumes of 20 $\mu$L 50 $\mu$L and 200 $\mu$L. 
+The printed pipette and a series of commercial pipettes were tested at volumes of 10 $\mu$L, 20 $\mu$L, 30 $\mu$L, 50 $\mu$L, 200 $\mu$L, 300 $\mu$L, 500 $\mu$L and 1000 $\mu$L. 
 The printed pipette was adjusted to the the target volume by eye from the syringe graduations, and the resulting volume was measured and repeated 5 times to account for variability.
 Measurements were taken from the commercial pipette in a similar way.
-
-To test user friendliness and feasibility for using the pipette without verifying with a scale, data was also gathered from novice users. 
-This group included researchers experienced with pipettes as well as undergraduates with little to no experience pipetting at all.
-After a quick overview of the operation of the pipette measurements were taken after the volunteers adjusted the pipette to 200, 50, 20 and 10 $\mu$L.
-
-For the printed pipette the 1000 $\mu$L tips were used for the 200 $\mu$L measurement. 100 $\mu$L tips were used for the 50, 20 and 10 $\mu$L measurements.
-
-compare the force required to press the button.
-
-compare the weight of the pipettes
-
-%After the first attempt was measured on the scale the volunteer was allowed to adjust the set point and re-measure until within 15\% of the target volume was reached.
 
@@
 Praesent faucibus semper libero.
-
-\begin{figure}[h]
-\caption{{\bf Novice User efficacy.}
-Novice users were asked to pipette volumes of 200, 50, 20 and 10 $\mu$L without the use of a scale.}
-\label{fig3}
-\end{figure}
 

### 2016-09-02 Plos-one-manuscript/latex/manuscript.tex
update

@@
 The open source development model, initially applied to software, is thriving in the development of open source scientific equipment due in part to increasing access of 3D printing \cite{Baden2015,Pearce2014}.
+Additive manufacturing methods have existed for decades although the recent availability of inexpensive desktop printers\cite{MakerbotIndustries2016,Reprap2015} have made it feasible for consumers to design and print prototypes and even functional parts, and consumer goods\cite{Fullerton2014}.
+Proliferation of free CAD software[OpenSCAD, Blender, SketchUp] and design sharing sites\cite{MakerbotIndustries2016,NationalInstitutesofHealth2015,grabCAD,GitHubInc.2016} have also supported the growth and popularity of open designed parts and projects.
 Open design 3D-printable lab equipment is and attractive idea because, like open source software, it allows free access to technology that is otherwise inaccessible due to proprietary and/or financial barriers.
@@
 Open source development also enables the development of custom solutions to meet unique applications not met by commercial products that are shared freely and are user modifiable\cite{Fullerton2014,Pearce2012}.
-Some advanced, noteworthy open-source scientific equipment include a PCR device\cite{ChaiBiotechnologiesInc2015}, and a two-photon microscope\cite{Rosenegger2014} although even simple tools are impactful especially if the fabrication is simplified by 3D printing.
-%The user is required to assemble the tools requiring them the learn how it functions.
-%The user is then equipped to diagnose problems and enact their own fixes and changes which is limited when dealing with commercial products.
-
-3D printing as a form of additive manufacturing has existed for decades although the recent availability of inexpensive desktop printers\cite{MakerbotIndustries2016,Reprap2015} have made it feasible for consumers to design and print prototypes and even functional parts, and consumer goods\cite{Fullerton2014}.
-Proliferation of free CAD software[OpenSCAD, Blender, SketchUp] and design sharing sites\cite{MakerbotIndustries2016,NationalInstitutesofHealth2015,grabCAD,GitHubInc.2016} have also supported the growth and popularity of open designed parts and projects.
-Some simple and clever printable parts that have emerged are ones that give a new function to a ubiquitous existing device such as drill bit attachment designed to hold centrifuge tubes, turning the drill into a centrifuge\cite{Garvey2009}.
-Although this may make a rather crude centrifuge it may be and adequate method that only costs pennies compared to commercially available centrifuges.
+Some advanced, noteworthy, open-source scientific equipment include a PCR device\cite{ChaiBiotechnologiesInc2015}, and a two-photon microscope\cite{Rosenegger2014} although simple tools are often more impactful as they can serve a wider community.
+Some simple and clever printable parts that have emerged are ones that give a new function to a ubiquitous existing device, such as drill bit attachment designed to hold centrifuge tubes, allowing a drill to be used as a centrifuge\cite{Garvey2009}.
+Although this may make a rather crude centrifuge it may be an adequate method which only costs pennies compared to commercially available centrifuges.
 Other examples of open-design research tools that utilize 3D printed parts include optics equipment\cite{Zhang2013}, microscopes\cite{Baden2014a,Walus2014}, syringe pumps\cite{Wijnen2014}, and reactionware\cite{Symes2012} to name a few.
 
-There are a few open design printable micropipettes including a popular one which uses parts scavenged from a retractable pen in addition to the printed parts\cite{Baden2014}.
-An air displacement pipette uses a piston operating principal to draw liquid into the pipette.
-In a typical commercial pipette the piston is made gas-tight with a gasketed plunger inside a smooth barrel.
+One example of a everyday scientific tool that provides opportunity for an open design solution is the micropipette.
+Micropipettes are and indispensable tool used routinely in lab tasks and can easily cost \$1000 USD for a set.
+Often a lab will require several sets each for a dedicated task.
+Some pipettes are even re-calibrated for use with liquids of different properties.
+A open design pipette that can be made for cheap can cut costs for labs as well as allow a option for educational settings.
+
+Air displacement pipettes use a piston operating principal to draw liquid into the pipette\cite{ISO2002}.
+In a typical commercial pipette the piston is made to be gas-tight with a gasketed plunger inside a smooth barrel.
 Consumer grade fused deposition modeling (FDM) printers are unable to form a smooth surface do to the formation of ridges that occur as each layer that is deposited.
@@
 The displacement membrane can be made from any elastic material such as a latex glove.
-After assembly this design requires the user to validate the volumes dispensed with a high precision scale.
-%uncertianty  
-Without verification with a scale the volumes dispensed can only be estimated based on theoretical displacement intended by the design.
-There is no built-in feature such as a digital readout for the user to set the displacement to a desired volume.
-The pipette can be calibrated to a specific volume with a set screw but if a new volume is desired it has to be re-adjusted and validated with a scale.
-%In addition no open-design pipettes have be rigorously validated.
+There are a few open design printable micropipettes including a popular one which uses parts scavenged from a retractable pen in addition to the printed parts\cite{Baden2014}.
+This design requires the user to validate the volumes dispensed with a high precision scale.
+There is no built-in feature such as a readout for the user to set the displacement to a desired volume.
+Without verification with a scale the volumes dispensed can only be estimated based on calculations of the deflection of the membrane.
+We submit a new design whose major strength is the ability to adjust to any volume according to built in scale.
 
-We present a new open design 3D-printable micropipette that works by actuating a 1 mL syringe to a user adjustable set-point.
-This allows the user to set the pipette to a volume a priori by reading the graduations of the syringe barrel.
+Our open design 3D-printable micropipette works by actuating a disposable syringe to a user adjustable set-point.
+This allows the user to set the pipette to a volume by reading the graduations on the syringe barrel.
 The scale marks on the syringe can be used to adjust the dispensed volume accurately without calibrating with a scale.
 Our pipette also offers a simplified assembly requiring no glue, tape or permanent connections.
+%In addition no open-design pipettes have be rigorously validated.
 
@@
 Our printed pipette is designed to actuate a 1 mL or 3 mL syringe to a user set displacement.
+A syringe is used because the current state of FDM leaves ridges on the surface of printed parts making a airtight connection impossible. 
+Micropipette designs use a piston operating principle to draw fluid into the device.
+Previous 3D printed designs have gotten around this limitation by using a flexable membrane to make an airtight tube.
+Then when the membrane is depressed the air is displaced allowing liquid to be drawn in.
+This allows a functional pipette to be created with very few easily sourced parts.
+
+These pipettes do now allow the 
 The core of the design is two printed parts, the body and the plunger which are able to be printed on a consumer grade FDM printer.
@@
 \caption{
-{\bf Photos of pipette.}  The pipette is composed of three printed parts, a 1 mL syringe and some additional hardware.  
+{\bf Photos of pipette.}  The pipette is composed of two printed parts, a 1 mL syringe and some additional hardware.  
 }
@@
 \subsection*{Validation}
-The printed pipette was validated and compared to a commercial pipette. 
+The printed pipette was validated and compared ISO 8655 and to a commercial pipette. 
 The pipette was tested to see if the set point would drift between during use for example small, incremental movements of the screw or other parts causing the pipetted volume to drift.
@@
 
-Our printed pipette had a comparable accuracy to a commercial pipette (Table~\ref{table1}).
-The commercial pipette has a digital readout that allows the user to adjust precisely to set values where the printed pipette is adjusted by eye according to graduations.
-Due to being unable to re-set the printed pipette back to the exact mechanical location it may be hard to compare directly with the commercial pipettes.
-This is certainly the cause of the lower accuracy and wider deviation although it's performance is impressive.
-Despite this additional variability the printed pipette's accuracy and precision approaches the ISO 8655 standard.
-
-The Novice user data demonstrates that even someone inexperienced with pipetting and unfamiliar with our design is able to use out pipette accurately with out the use of a scale. 
-The systematic error trended towards over estimating the displacement. 
-This is likely due the function of adjusting the volume where it is easier to start at a lower displacement and increase it by unscrewing, or releasing compression of the spring.
-This explains the negative systematic error as the user avoids 'going over'.
+Initially validation was preformed with the original graduations printed on the syringes.
+Due to the expansion of air the built in graduations are were not accurate, especially at larger volumes.
+Using our redesigned scale volumes were accurate.
+Our printed pipette meets ISO standards for accuracy and precision. (Table~\ref{table1 ,table2}).
 
@@
 No validation or calibration is required.
-The pipette can be assembled and used to accurately pipette micro volumes without first validating with a scale.
+The pipette can be assembled and used to accurately pipette without first validating with a scale.
 

### 2016-11-09 Plos-one-manuscript/latex/manuscript.tex
update

@@
 In a typical commercial pipette the piston is made to be gas-tight with a gasketed plunger inside a smooth barrel.
-Consumer grade fused deposition modeling (FDM) printers are unable to form a smooth surface do to the formation of ridges that occur as each layer that is deposited.
+Consumer grade fused deposition modeling (FDM) printers are unable to build a smooth surface do to the formation of ridges that occur as each layer is deposited.
 The ridges formed by FDM make it impractical to form a gas-tight seal between moving parts, even with a gasket.
-Printable open-design micropipettes get around this limitation by stretching a membrane over one end of a printed tube, which when pressed causes the displacement.
+Existing printable open-design micropipettes get around this limitation by stretching a membrane over one end of a printed tube, which when pressed causes the displacement.
 The displacement membrane can be made from any elastic material such as a latex glove.
-There are a few open design printable micropipettes including a popular one which uses parts scavenged from a retractable pen in addition to the printed parts\cite{Baden2014}.
-This design requires the user to validate the volumes dispensed with a high precision scale.
-There is no built-in feature such as a readout for the user to set the displacement to a desired volume.
+There are a few open design printable micropipettes including a popular one which, in addition to the printed parts, uses parts scavenged from a retractable pen \cite{Baden2014}.
+Because there is no built-in feature such as a readout for the user to set the displacement to a desired volume, this design requires the user to validate the volumes dispensed with a high precision scale.
 Without verification with a scale the volumes dispensed can only be estimated based on calculations of the deflection of the membrane.
+
 We submit a new design whose major strength is the ability to adjust to any volume according to built in scale.
-
 Our open design 3D-printable micropipette works by actuating a disposable syringe to a user adjustable set-point.
@@
 % authors may use "Analysis" 
-\section*{Materials and Methods}
-\subsection*{Design}
+\section*{Design}
 
@@
 Micropipette designs use a piston operating principle to draw fluid into the device.
-Previous 3D printed designs have gotten around this limitation by using a flexable membrane to make an airtight tube.
+Previous 3D printed designs have gotten around this limitation by using a flexible membrane to make an airtight tube.
 Then when the membrane is depressed the air is displaced allowing liquid to be drawn in.
@@
 
-These pipettes do now allow the 
 The core of the design is two printed parts, the body and the plunger which are able to be printed on a consumer grade FDM printer.
@@
 The button is pressed with the thumb until the latched position is reached.
-The the tip immersed in fluid and drawn in by actuating the lever with the palm or fingers.
-Conveniently this design can also reach to the bottom of a 15 mL conical tube allowing tasks such as aspirating supernatant fluid from a cell pellet where existing printed designs cannot.
+Then the tip immersed in fluid and drawn in by actuating the lever with the palm or fingers.
+Conveniently this design can also reach to the bottom of a 15 mL conical tube allowing tasks such as aspirating supernatant fluid from a cell pellet.
 
+\subsection*{Adjusted Syringe Graduations}
 Our pipette uses the air-displacement design, where a pocket of air is used to draw liquid into the pipette.
@@
 Due to this effect the graduations on the syringe are not accurate, as they are designed for measuring liquid within the syringe.
-At larger volumes this is more pronounced where the volume of are measured is greater then the amount of liquid pulled into the syringe.
+At larger volumes this effect is more pronounced resulting in the volume measured being greater then the amount of liquid pulled into the syringe.
+We remedied this by creating a new scale to account for the expansion.
+The scale is printed on a transparency sheet and is pasted on the syringe for accurate measurements.
 
-when the liquid volume is pulling due to the force of gravity.
-This effect increases as the larger volumes are transfered.
-Due to the expandability of air the graduations on the syringe are not accurate.
-This effect is the greatest at larger volumes corresponding to a greater mass pulling on the air pocket.
-The pocket of air that is drawing in the water is stretched causing the inaccurate readings.
-We remedied this by creating a new scale to account for the expansion.
-The scale which is printed on a transparency sheet is pasted on the syringe as a guide for the set point.
+\subsection*{Materials and Assembly}
+
+\begin{table}[]
+\centering
+\caption{My caption}
+\label{table1}
+\begin{tabular}{|l|l|l|l|}
+\hline
+             & Unit price & Source         & Part number \\ \hline
+Filiment     & \$1.63     & Makerbot       & NA          \\ \hline
+1 mL Syringe & \$0.15     & BD Biosciences & 309628      \\ \hline
+3 mL Syringe & \$0.73     & BD Biosciences & 309657      \\ \hline
+Bolt         & \$0.12     & McMaster-Carr  & 91287A026   \\ \hline
+Nut          & \$0.01     & McMaster-Carr  & 90591A121   \\ \hline
+Spring       & \$4.14     & McMaster-Carr  & 94125K542   \\ \hline
+Washers      & ??         & McMaster-Carr  & ??          \\ \hline
+Total        & \$6.78     &                &             \\ \hline
+\end{tabular}
+\end{table}
+
+% cost for each part filiment,syringe hardware
+% tips used
+% syringes used
+% printer used and settings
+
 %Testing taken with the original scale along with the adjusted scale is shown in table 1 and 2.
@@
 \caption{
-{\bf CAD rendering of printable parts.}  Three parts are printed: the body, plunger shaft, and luer-lock adapter for pipette tips.
+{\bf CAD renderings of printable parts.} Two parts are printed: The plunger part (A) slides inside the body part (B).
 }
 \label{fig1}
-% Ideally: cad rendering showing the design and function of the pipette. 
-% a) Un-assembled whole parts next to their cross-sections.  
-% b) Assembly next to crossection
-% c) close up of how the locking groove/mechanism works
-% d) cross-section showing the two positions of the plunger, locked at the goove and stopped at the screw 
 \end{figure}
@@
 \caption{
-{\bf CAD renderings of printable parts.} Two parts are printed: The plunger part (A) slides inside the body part (B).
+{\bf CAD renderings of assembled pipette and function.} The pipetted actuates the syringe to three positions.
+{\bf(i) The set position.} The position of the screw determines the total displacement.
+The pipette is spring loaded to return to this position {\bf (ii) The latched position.} When the plunger is pressed the pipette locks at this position.
+The tip is then placed in a liquid and the button pressed to release the pipette back to the set position, drawing in liquid.
+{\bf (iii) The blow-out position.} The fluid is transfered by pressing the plunger past the latched position to blow-out all the liquid.
 }
 \label{fig1}
-% Ideally: cad rendering showing the design and function of the pipette. 
-% a) Un-assembled whole parts next to their cross-sections.  
-% b) Assembly next to crossection
-% c) close up of how the locking groove/mechanism works
-% d) cross-section showing the two positions of the plunger, locked at the goove and stopped at the screw 
 \end{figure}
@@
 \caption{ISO 8655 for 100-1000 uL comparing a commercial pipette with our printed pipette used with existing 3 mL syringe scale and an adjusted scale}
-\label{table1}
+\label{table2}
 \begin{tabular}{lllllll}
@@
 \caption{ISO 8655 for 30-300 uL comparing a commercial pipette with our printed pipette used with existing 3 mL syringe scale and an adjusted scale}
-\label{table2}
+\label{table3}
 \begin{tabular}{lllllll}

### 2016-12-15 data/commerical-Vs-printed-comparison/analysis/analysis.R
updated 'merged with develop'

@@ -1,0 +1,192 @@
+# read in raw data
+
+
+eppendorf1000 <- read.csv(file='eppendorf_1000iso_1000', sep=',')
+eppendorf500 <- read.csv(file='eppendorf_1000iso_500', sep=',')
+eppendorf200 <- read.csv(file='eppendorf_1000iso_200', sep=',')
+eppendorf100 <- read.csv(file='eppendorf_1000iso_100', sep=',')
+
+commercial_200uL <- read.csv(file='200uL_commercial.csv', sep=',')
+commercial_50uL <- read.csv(file='50uL_commercial.csv', sep=',')
+commercial_20uL <- read.csv(file='20uL_commercial.csv', sep=',')
+commercial_10uL <- read.csv(file='10uL_commercial.csv', sep=',')
+
+# conversion of mass to volume according to temp and air pressure
+vol.epp.1000 = eppendorf1000*1.0038
+vol.epp.500 = eppendorf500*1.0038
+vol.epp.200 = eppendorf200*1.0038
+vol.epp.100 = eppendorf100*1.0038
+vol.com.200 = commercial_200uL*1.0038
+vol.com.50 = commercial_50uL*1.0038
+vol.com.20 = commercial_20uL*1.0038
+vol.com.10 = commercial_10uL*1.0038
+
+#take mean of 5 transfers for each tip
+m.tips.epp.1000 = colMeans(vol.epp.1000)
+m.tips.epp.500 = colMeans(vol.epp.500)
+m.tips.epp.200 = colMeans(vol.epp.200)
+m.tips.epp.100 = colMeans(vol.epp.100)
+m.tips.com.200 = colMeans(vol.com.200)
+m.tips.com.50 = colMeans(vol.com.50)
+m.tips.com.20 = colMeans(vol.com.20)
+m.tips.com.10 = colMeans(vol.com.10)
+
+#200 uL
+m.epp.1000 = mean(m.tips.epp.1000)
+re.vol.com.200 = sd(m.tips.com.200)
+re.p.com.200 = 100*(re.vol.com.200/m.com.200)
+se.vol.com.200 = mean(m.tips.com.200) - 200
+se.p.com.200 = 100*(se.vol.com.200/200)
[…]

### 2016-12-15 data/commerical-Vs-printed-comparison/analysis/plotting.R

@@ -1,0 +1,72 @@
+# ISO 1000-100
+ISO_1000uL <- read.csv(file='1000uL_ISO.csv', sep=',')
+eppendorf_1000 <- read.csv(file='eppendorf-1000-analyzed.csv', sep=',')
+printed_analyzed <- read.csv(file='printed_analyzed.csv', sep=',')
+ISO_plot_1000 = c(printed_analyzed[1:4,"Mean"])
+ISO_plot_1000 = as.data.frame(ISO_plot_1000)
+colnames(ISO_plot_1000) <- c("Printed")
+ISO_plot_1000$ plus = ISO_1000uL[1:4,"plus"]
+ISO_plot_1000$ minus = ISO_1000uL[1:4,"minus"]
+ISO_plot_1000$ commercial = eppendorf_1000[1:4,"Mean"]
+ISO_plot_1000$ nominal <- c("1000uL", "500uL", "200uL", "100uL")
+#ISO_plot_1000$nominal <- as.character(ISO_plot_1000$nominal)
+ISO_plot_1000$nominal <- factor(ISO_plot_1000$nominal, levels=unique(ISO_plot_1000$nominal))
+
+
+library(ggplot2)
+ggplot(ISO_plot_1000[3:4,], aes(x=nominal, ymin = `minus`, 
+                                ymax = `plus`, lower = `minus`, 
+                                upper = `plus`, middle = `commercial`)) + 
+  geom_boxplot(stat = 'identity') +
+  xlab('Nominal Volume') + 
+  ylab('Volume') +
+  geom_crossbar(aes(y = `commercial`), linetype = 1)+
+  geom_crossbar(aes(y = `Printed`), linetype = 2)
+
+
+#ISO 300
+ISO_300uL <- read.csv(file='300uL_ISO.csv', sep=',')
+commercial_analyzed <- read.csv(file='commercial_analyzed.csv', sep=',')
+ISO_plot_300 = commercial_analyzed["Mean"]
+#ISO_plot_300 = as.data.frame(ISO_mean)
+ISO_plot_300$ nominal <- c("200uL", "50uL", "20uL", "10uL")
+ISO_plot_300$ nominal <- factor(ISO_plot_300$ nominal, levels=unique(ISO_plot_300$nominal))
+ISO_plot_300$ printed = printed_analyzed[6:9,"Mean"]
+ISO_plot_300$ plus = ISO_300uL[1:4,"plus"]
[…]

### 2016-12-15 data/printed-Vs-commercial/analysis.m

@@ -1,38 +1,0 @@
-clear
-
-load 20uL-printed-pipette.csv
-load 50uL-printed-pipette.csv
-load 200uL-printed-pipette.csv
-load commercial-pipette.csv
-
-mean20 = mean(mean(X20uL_printed_pipette,1),2);
-mean50 = mean(mean(X50uL_printed_pipette,1),2);
-mean200 = mean(mean(X200uL_printed_pipette,1),2);
-
-std20 = std(mean(X20uL_printed_pipette,1));
-std50 = std(mean(X50uL_printed_pipette,1));
-std200 = std(mean(X200uL_printed_pipette,1));
-
-commercial_mean_20=mean(commercial_pipette(:,3));
-commercial_mean_50=mean(commercial_pipette(:,2));
-commercial_mean_200=mean(commercial_pipette(:,1));
-
-commercial_std_20=std(commercial_pipette(:,3));
-commercial_std_50=std(commercial_pipette(:,2));
-commercial_std_200=std(commercial_pipette(:,1));
-
-means = [mean20 mean50 mean200; commercial_mean_20 commercial_mean_50 commercial_mean_200]*1000;
-
-stds = [std20 std50 std200; commercial_std_20 commercial_std_50 commercial_std_200]*1000;
-
-dlmwrite('analyzed_means.csv',means,'precision',4)
-dlmwrite('analyzed_stds.csv',stds,'precision',3)
-
-%save -ascii analyzed_means.csv means
-%save -ascii analyzed_stds.csv stds
-
-%string_means = mat2str(means,4)
-%string_stds = mat2str(stds,3)
-
-%save -ascii string_means.csv string_means
-%save -ascii string_means.csv string_means

### 2016-12-15 data/user-data.R

@@ -1,19 +1,0 @@
-par(mfrow=c(1,4)) 
-title(main="Autos", col.main="red", font.main=4)
-plot(x200, novice_user_data$V1, ylim=c(150,280), axes=FALSE, ann=FALSE)
-points(200,mean(novice_user_data$V1), col="red", pch=3)
-axis(1, at=200, lab="200 uL")
-Axis(side=2)
-plot(x50, novice_user_data$V2, ylim=c(30,60), axes=FALSE, ann=FALSE)
-points(50,mean(novice_user_data$V2), col="red", pch=3)
-axis(1, at=50, lab="50 uL")
-Axis(side=2)
-plot(x20, novice_user_data$V3, ylim=c(10,30), axes=FALSE, ann=FALSE)
-points(20,mean(novice_user_data$V3), col="red", pch=3)
-axis(1, at=20, lab="20 uL")
-Axis(side=2)
-plot(x10, novice_user_data$V4, ylim=c(0,15), axes=FALSE, ann=FALSE)
-points(10,mean(novice_user_data$V4), col="red", pch=3)
-axis(1, at=10, lab="10 uL")
-Axis(side=2)
-title(main="Novice User's First Attempt", font.main=1, cex.main=1.5, line=-2, outer=TRUE)

### 2016-12-16 Plos-one-manuscript/latex/manuscript.tex
working on figures
working

@@
 % authors may use "Analysis" 
-\section*{Design}
+\section*{Materials and Methods}
 
 Our printed pipette is designed to actuate a 1 mL or 3 mL syringe to a user set displacement.
-A syringe is used because the current state of FDM leaves ridges on the surface of printed parts making a airtight connection impossible. 
-Micropipette designs use a piston operating principle to draw fluid into the device.
-Previous 3D printed designs have gotten around this limitation by using a flexible membrane to make an airtight tube.
-Then when the membrane is depressed the air is displaced allowing liquid to be drawn in.
-This allows a functional pipette to be created with very few easily sourced parts.
-
 The core of the design is two printed parts, the body and the plunger which are able to be printed on a consumer grade FDM printer.
-A 1 mL BD syringe twists to lock in the body part and is held into place by the syringe flanges.
+A 1 mL or 3 mL BD syringe twists to lock in the body part and is held into place by the syringe flanges.
+The 30-300 uL configuration uses a 1 mL pipette and the 100-1000 uL configuration uses a 3 mL pipette.
 The plunger part slides freely in the body part and actuates the syringe by pushing the thumb press. 
@@
 Attempts to make a printable luer lock adapter for tips was abandoned as the surface of printed parts is too rough to make an air tight seal with the luer or pipette tip.
-Instead a combination of a barbed luer adapter and elastic tubing was used to attach the pipette tips.
-
+Instead a combination of a barbed luer adapter and elastic tubing is used to attach the pipette tips.
 Our printed pipette mimics commercial pipettes's design, function, and user operation, making it intuitive to use.
-The button is pressed with the thumb until the latched position is reached.
-Then the tip immersed in fluid and drawn in by actuating the lever with the palm or fingers.
 Conveniently this design can also reach to the bottom of a 15 mL conical tube allowing tasks such as aspirating supernatant fluid from a cell pellet.
 
-\subsection*{Adjusted Syringe Graduations}
 Our pipette uses the air-displacement design, where a pocket of air is used to draw liquid into the pipette.
@@
 
-\subsection*{Materials and Assembly}
+\subsection*{Assembly}
 
-\begin{table}[]
+A small amount of parrifin wax is applyed to the screw to prevent slop from causing the set point to drift after each acuation.
+This was effective in preventing drift.
+The nut is sunk in to the hex inset in the body part.
+The bolt is threaded in from the top of the body into the nut.
+Springs and washers are threaded onto the plunger of the 1 mL syringe for the 30-300 uL configuration.
+Springs are placed inside the 3 mL syringe for the 100-1000 mL configuration.
+The plunger part is inserted in the body and the syringe assembly is pushed in and locked from the syringe flanges to the body part to complete assembly.
+
+\begin{table}[!ht]
 \centering
-\caption{My caption}
+\caption{Parts and cost for the 30-300 uL pipette.}
 \label{table1}
@@
 	\hline
-             & Unit price & Source         & Part number \\ \hline
-Filiment     & \$1.63     & Makerbot       & NA          \\ \hline
+	Part         & Unit Price & Source         & Part number \\ \hline
+	Filament     & \$1.63     & Makerbot       & NA          \\ \hline
 	1 mL Syringe & \$0.15     & BD Biosciences & 309628      \\ \hline
+	Bolt         & \$0.12     & McMaster-Carr  & 91287A026   \\ \hline
+	Nut          & \$0.01     & McMaster-Carr  & 90591A121   \\ \hline
+	Spring (2)   & \$4.14     & McMaster-Carr  & 94125K542   \\ \hline
+	Washers (2)  & \$0.16     & McMaster-Carr  & 90107A012   \\ \hline
+	total        & \$6.21     &                &             \\ \hline
+\end{tabular}
+\end{table}
+
+\begin{table}[!ht]
+\centering
+\caption{Parts and cost for the 100-1000 uL pipette.}
+\label{table2}
+\begin{tabular}{|l|l|l|l|}
+	\hline
+	Part         & Unit Price & Source         & Part number \\ \hline
+	Filament     & \$1.63     & Makerbot       & NA          \\ \hline
 	3 mL Syringe & \$0.73     & BD Biosciences & 309657      \\ \hline
@@
 	Nut          & \$0.01     & McMaster-Carr  & 90591A121   \\ \hline
-Spring       & \$4.14     & McMaster-Carr  & 94125K542   \\ \hline
-Washers      & ??         & McMaster-Carr  & ??          \\ \hline
-Total        & \$6.78     &                &             \\ \hline
+	Spring (2)   & \$4.14     & McMaster-Carr  & 94125K542   \\ \hline
+	total        & \$6.63     &                &             \\ \hline
 \end{tabular}
 \end{table}
-
-% cost for each part filiment,syringe hardware
-% tips used
-% syringes used
-% printer used and settings
-
-%Testing taken with the original scale along with the adjusted scale is shown in table 1 and 2.
-
-%3D parts were designed in Blender and SolidWorks and printed by Fineline Prototyping via selective laser sintering.
 
@@
 \subsection*{Validation}
-The printed pipette was validated and compared ISO 8655 and to a commercial pipette. 
-The pipette was tested to see if the set point would drift between during use for example small, incremental movements of the screw or other parts causing the pipetted volume to drift.
-To test the pipette the same volume was pipetted 50 times without moving or re-adjusting the set point.
-A small amount of paraffin wax was applied to the screw to prevent it from slipping during each actuation. 
-The printed pipette’s accuracy and precision was characterized and compared to a commercial pipette.
-The printed pipette and a series of commercial pipettes were tested at volumes of 10 $\mu$L, 20 $\mu$L, 30 $\mu$L, 50 $\mu$L, 200 $\mu$L, 300 $\mu$L, 500 $\mu$L and 1000 $\mu$L. 
-The printed pipette was adjusted to the the target volume by eye from the syringe graduations, and the resulting volume was measured and repeated 5 times to account for variability.
-Measurements were taken from the commercial pipette in a similar way.
+The printed pipette’s accuracy and precision was characterized and compared to a commercial pipette as well as ISO 8655.
+The printed pipette was adjusted to the the target volume by eye from the syringe graduations, and the resulting volume was measured and repeated 5 times to account for transfer variability.
+Data was taken for printed pipettes with existing graduations as well as with the adjusted scale.
+The commerical pipette was adjusted to the desired volume and 5 transfers were taken.
 
@@
 \caption{ISO 8655 for 100-1000 uL comparing a commercial pipette with our printed pipette used with existing 3 mL syringe scale and an adjusted scale}
-\label{table2}
+\label{table3}
 \begin{tabular}{lllllll}
@@
 \caption{ISO 8655 for 30-300 uL comparing a commercial pipette with our printed pipette used with existing 3 mL syringe scale and an adjusted scale}
-\label{table3}
+\label{table4}
 \begin{tabular}{lllllll}

### 2016-12-21 Plos-one-manuscript/latex/manuscript.tex
working

@@
 Our pipette uses the air-displacement design, where a pocket of air is used to draw liquid into the pipette.
-As air is an expansible fluid, this pocket of air expands due to the weight of the liquid pulling on it.
+As air is an compressible fluid, this pocket of air grows due to the weight of the liquid pulling on it.
 Due to this effect the graduations on the syringe are not accurate, as they are designed for measuring liquid within the syringe.
@@
 
-A small amount of parrifin wax is applyed to the screw to prevent slop from causing the set point to drift after each acuation.
-This was effective in preventing drift.
+A small amount of parrifin wax is applyed to the screw to prevent slop from causeing the set point to drift after each acuation.
 The nut is sunk in to the hex inset in the body part.

### 2016-12-21 Plos-one-manuscript/latex/manuscript.tex
working

@@
 
-A small amount of parrifin wax is applyed to the screw to prevent slop from causeing the set point to drift after each acuation.
+A small amount of parrifin wax is applyed to the screw to prevent slop from causeting the set point to drift after each acuation.
 The nut is sunk in to the hex inset in the body part.
@@
 The commerical pipette was adjusted to the desired volume and 5 transfers were taken.
+The systematic error and random error was calculated according to ISO 8655 (Table~\ref{table3,table4}).
 
@@
 This pipette improves on existing open design pipettes in several ways. 
-It requires only two printed parts, a syringe, and some hardware.
-It is able to reach into a 15 mL conical tube which is a routine requirement for cell culture.
-No permanent connections using tape or glue are required for assembly allowing worn out or broken part to be replaced easily.
-Assembly does not require a membrane that may wear or stretch and require tedious replacement.
-No validation or calibration is required.
-The pipette can be assembled and used to accurately pipette without first validating with a scale.
+Most significatly the user is able to adjust the syringe accuratly without verifying the volume with a scale.
+In additon the assembly requires no permanent connections using tape or glue which allows for re-configurationorn and easy replacment of parts.
+Our pipette is able to transfer from the bottom of a 15 mL conical tube which is a requirement for many routine lab procedures such as aspirating supernatant from a centrifuged cell pellet.
+This design does not use a membrane that may wear out and require tedious replacement.
 

### 2016-12-22 Plos-one-manuscript/latex/manuscript.tex
spell check

@@
 
-%range of 226 ul, one tip size per pipette
+%range of 226 uL, one tip size per pipette
 
@@
 The core of the design is two printed parts, the body and the plunger which are able to be printed on a consumer grade FDM printer.
-A 1 mL or 3 mL BD syringe twists to lock in the body part and is held into place by the syringe flanges.
+A 1 mL or 3 mL syringe twists to lock in the body part and is held into place by the syringe flanges.
 The 30-300 uL configuration uses a 1 mL pipette and the 100-1000 uL configuration uses a 3 mL pipette.
@@
 The displacement is equal to the distance between the set position and the latched position.
-The pipette can also be pressed past the latched position to 'blow-out' the transfered fluid completely from the pipette tip.   
+The pipette can also be pressed past the latched position to 'blow-out' the transferred fluid completely from the pipette tip.   
 Additional materials required for assembly include a spring, a nut and bolt and washers.
@@
 Instead a combination of a barbed luer adapter and elastic tubing is used to attach the pipette tips.
-Our printed pipette mimics commercial pipettes's design, function, and user operation, making it intuitive to use.
+Our printed pipette mimics commercial pipettes design, function, and user operation, making it intuitive to use.
 Conveniently this design can also reach to the bottom of a 15 mL conical tube allowing tasks such as aspirating supernatant fluid from a cell pellet.
@@
 
-A small amount of parrifin wax is applyed to the screw to prevent slop from causeting the set point to drift after each acuation.
+A small amount of paraffin wax is applied to the screw to prevent slop from causing the set point to drift after each actuation.
 The nut is sunk in to the hex inset in the body part.
@@
 The tip is then placed in a liquid and the button pressed to release the pipette back to the set position, drawing in liquid.
-{\bf (iii) The blow-out position.} The fluid is transfered by pressing the plunger past the latched position to blow-out all the liquid.
+{\bf (iii) The blow-out position.} The fluid is transferred by pressing the plunger past the latched position to blow-out all the liquid.
 }
@@
 The printed pipette’s accuracy and precision was characterized and compared to a commercial pipette as well as ISO 8655.
-The printed pipette was adjusted to the the target volume by eye from the syringe graduations, and the resulting volume was measured and repeated 5 times to account for transfer variability.
+The printed pipette was adjusted to the target volume by eye from the syringe graduations, and the resulting volume was measured and repeated 5 times to account for transfer variability.
 Data was taken for printed pipettes with existing graduations as well as with the adjusted scale.
-The commerical pipette was adjusted to the desired volume and 5 transfers were taken.
+The commercial pipette was adjusted to the desired volume and 5 transfers were taken.
 The systematic error and random error was calculated according to ISO 8655 (Table~\ref{table3,table4}).
@@
 This pipette improves on existing open design pipettes in several ways. 
-Most significatly the user is able to adjust the syringe accuratly without verifying the volume with a scale.
-In additon the assembly requires no permanent connections using tape or glue which allows for re-configurationorn and easy replacment of parts.
+Most significantly the user is able to adjust the syringe accurately without verifying the volume with a scale.
+In addition the assembly requires no permanent connections using tape or glue which allows for re-configuration and easy replacement of parts.
 Our pipette is able to transfer from the bottom of a 15 mL conical tube which is a requirement for many routine lab procedures such as aspirating supernatant from a centrifuged cell pellet.
@@
 
-The only major limitation of this design compared to the briopipette is the option for a pipette tip ejector, although incorporation of a similar design in our pipette would not leave room for it to reach into a 15 mL conical tube.
-Our pipette requires a syringe and some additional hardware where briopipette's additional parts can be obtained virtually anywhere.
-The briopipette also allows step-wise shifts in displacement allowing the user to quickly change to a relative volume
+The only major limitation of this design compared to the biropipette is the option for a pipette tip ejector, although incorporation of a similar design in our pipette would not leave room for it to reach into a 15 mL conical tube.
+Our pipette requires a syringe and some additional hardware where biropipette's additional parts can be obtained virtually anywhere.
+The biropipette also allows step-wise shifts in displacement allowing the user to quickly change to a relative volume
 

### 2016-12-29 Plos-one-manuscript/latex/manuscript.tex
working

@@
 One example of a everyday scientific tool that provides opportunity for an open design solution is the micropipette.
-Micropipettes are and indispensable tool used routinely in lab tasks and can easily cost \$1000 USD for a set.
+Micropipettes are an indispensable tool used routinely in lab tasks and can easily cost \$1000 USD for a set.
 Often a lab will require several sets each for a dedicated task.
@@
 Our pipette also offers a simplified assembly requiring no glue, tape or permanent connections.
-%In addition no open-design pipettes have be rigorously validated.
 
-%range of 226 uL, one tip size per pipette
-
-%\begin{equation}\label{eq:schemeP} 
-%D_{coll} = \frac{D_f+\frac{[S]^2}{K_D S_T} D_S} {1+\frac{[S]^2}{K_D S_T}}, 
-%D_{sm} = \frac{D_f+ \frac{[S]}{K_D} D_S}{1+\frac{[S]}{K_D}},
-%\end{equation}
-
-% You may title this section "Methods" or "Models". 
-% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
-% authors may use "Analysis" 
-\section*{Materials and Methods}
-
+\section*{Methods}
 Our printed pipette is designed to actuate a 1 mL or 3 mL syringe to a user set displacement.
@@
 \subsection*{Assembly}
-
 A small amount of paraffin wax is applied to the screw to prevent slop from causing the set point to drift after each actuation.
@@
 The plunger part is inserted in the body and the syringe assembly is pushed in and locked from the syringe flanges to the body part to complete assembly.
+Parts and cost are listed in tables~\ref{table1,table2}
 
@@
 }
-\label{fig1}
+\label{fig2}
 \end{figure}
@@
 \label{fig3}
-% Ideally: Photo showing assembled pipette as well as parts
 \end{figure}
@@
 The printed pipette was adjusted to the target volume by eye from the syringe graduations, and the resulting volume was measured and repeated 5 times to account for transfer variability.
-Data was taken for printed pipettes with existing graduations as well as with the adjusted scale.
-The commercial pipette was adjusted to the desired volume and 5 transfers were taken.
-The systematic error and random error was calculated according to ISO 8655 (Table~\ref{table3,table4}).
+Data was taken for printed pipettes with existing syringe graduations as well as with the our adjusted scale.
+Data was taken with commercial pipettes of 30-300 and 100-1000 to compare to the printed pipette. 
+The systematic error and random error was calculated according to ISO 8655~\ref{ISO2013} (Table~\ref{table3,table4}).
 
-% For figure citations, please use "Fig." instead of "Figure".
-%Nulla mi mi, Fig.~\ref{fig1} venenatis sed ipsum varius, volutpat euismod diam.
-Proin rutrum vel massa non gravida.
-Quisque tempor sem et dignissim rutrum.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Morbi at justo vitae nulla elementum commodo eu id massa.
-In vitae diam ac augue semper tincidunt eu ut eros.
-Fusce fringilla erat porttitor lectus cursus, \nameref{S1_Video} vel sagittis arcu lobortis.
-Aliquam in enim semper, aliquam massa id, cursus neque.
-Praesent faucibus semper libero.
+\section*{Results and Discussion}
+Validation testing preformed with the existing graduations printed on the syringes did not meet the ISO standards.
+Due to the expansion of air the built in graduations were not accurate, especially at larger volumes.
+Replacing the scale with our scale that accounts for the expansion corrected this effect. 
+Our printed pipette with the adjusted scale meets ISO standards for accuracy and precision. (Table~\ref{table1 ,table2}).
 
-%\begin{enumerate}
-%\item{react}
-%\item{diffuse free particles}
-%\item{increment time by dt and go to 1}
-%\end{enumerate}
-
-% Results and Discussion can be combined.
-\section*{Results and Discussion}
-
-Initially validation was preformed with the original graduations printed on the syringes.
-Due to the expansion of air the built in graduations are were not accurate, especially at larger volumes.
-Using our redesigned scale volumes were accurate.
-Our printed pipette meets ISO standards for accuracy and precision. (Table~\ref{table1 ,table2}).
-
-This pipette improves on existing open design pipettes in several ways. 
+Our printed pipette improves on existing open design pipettes in several ways. 
 Most significantly the user is able to adjust the syringe accurately without verifying the volume with a scale.
@@
 
-The only major limitation of this design compared to the biropipette is the option for a pipette tip ejector, although incorporation of a similar design in our pipette would not leave room for it to reach into a 15 mL conical tube.
-Our pipette requires a syringe and some additional hardware where biropipette's additional parts can be obtained virtually anywhere.
-The biropipette also allows step-wise shifts in displacement allowing the user to quickly change to a relative volume
+The only major limitation of this design compared to the biropipette is the option for a pipette tip ejector.
+The biropipette also uses easier to source parts relative to what is required from our design.
 

### 2016-12-31 Plos-one-manuscript/latex/manuscript.tex
working on manuscript

@@
 Proliferation of free CAD software[OpenSCAD, Blender, SketchUp] and design sharing sites\cite{MakerbotIndustries2016,NationalInstitutesofHealth2015,grabCAD,GitHubInc.2016} have also supported the growth and popularity of open designed parts and projects.
-Open design 3D-printable lab equipment is and attractive idea because, like open source software, it allows free access to technology that is otherwise inaccessible due to proprietary and/or financial barriers.
+Open design 3D-printable lab equipment is an attractive idea because, like open source software, it allows free access to technology that is otherwise inaccessible due to proprietary and/or financial barriers.
 Open design tools create opportunity for scientists and educational programs in remote or resource limited areas to participate with inexpensive and easy to make tools\cite{Baden2015}. 
@@
 One example of a everyday scientific tool that provides opportunity for an open design solution is the micropipette.
+A open design pipette that can be made for cheap can cut costs and allow for more options for labs and educational settings.
 Micropipettes are an indispensable tool used routinely in lab tasks and can easily cost \$1000 USD for a set.
@@
 Some pipettes are even re-calibrated for use with liquids of different properties.
-A open design pipette that can be made for cheap can cut costs for labs as well as allow a option for educational settings.
 
@@
 The displacement membrane can be made from any elastic material such as a latex glove.
-There are a few open design printable micropipettes including a popular one which, in addition to the printed parts, uses parts scavenged from a retractable pen \cite{Baden2014}.
+A few open design micropipettes exist including a popular one which, in addition to the printed parts, uses parts scavenged from a retractable pen\cite{Baden2014}.
 Because there is no built-in feature such as a readout for the user to set the displacement to a desired volume, this design requires the user to validate the volumes dispensed with a high precision scale.
@@
 
-We submit a new design whose major strength is the ability to adjust to any volume according to built in scale.
+We submit a new design who's major strength is the ability to adjust to any volume according to a built in scale.
 Our open design 3D-printable micropipette works by actuating a disposable syringe to a user adjustable set-point.
@@
 The scale marks on the syringe can be used to adjust the dispensed volume accurately without calibrating with a scale.
-Our pipette also offers a simplified assembly requiring no glue, tape or permanent connections.
+Our pipette also offers a simplified assembly requiring no glue, tape, or permanent connections.
 
@@
 Attempts to make a printable luer lock adapter for tips was abandoned as the surface of printed parts is too rough to make an air tight seal with the luer or pipette tip.
-Instead a combination of a barbed luer adapter and elastic tubing is used to attach the pipette tips.
+Instead, a combination of a barbed luer adapter and elastic tubing is used to attach the pipette tips.
 Our printed pipette mimics commercial pipettes design, function, and user operation, making it intuitive to use.
-Conveniently this design can also reach to the bottom of a 15 mL conical tube allowing tasks such as aspirating supernatant fluid from a cell pellet.
 
@@
 We remedied this by creating a new scale to account for the expansion.
-The scale is printed on a transparency sheet and is pasted on the syringe for accurate measurements.
+The scale is printed on a transparency sheet and is taped onto the syringe for accurate measurements.
 
@@
 The printed pipette’s accuracy and precision was characterized and compared to a commercial pipette as well as ISO 8655.
-The printed pipette was adjusted to the target volume by eye from the syringe graduations, and the resulting volume was measured and repeated 5 times to account for transfer variability.
+The printed pipette was adjusted to the target volume by eye from the syringe graduations.
+Dionized water was transfered and measured with a scale,
+Five transferes were recorded and averaged to account for random variability.
 Data was taken for printed pipettes with existing syringe graduations as well as with the our adjusted scale.
@@
 Validation testing preformed with the existing graduations printed on the syringes did not meet the ISO standards.
-Due to the expansion of air the built in graduations were not accurate, especially at larger volumes.
+According to ISO 8655 for a pipette with the maximum nominal volume of 1000 uL the systematic error cannot excede 8 uL and the random error cannot excede 3 uL and the the maximum nominal volume of 300 uL the systemic error cannot excede 4 uL and the random error cannot excede 1.5 uL.
+The commerical pipettes met these standards handidly, but in our initial tests with our printed pipette we noticied large negaive systematic error suggesting that we were missing a biasing factor. 
+This error was exagurated while transfering larger volumes.
+After further investigation we realized that the graduations are intended to measure incompressible fluids within the syringe while we were using them to measure air while under vacuum.
+Becasue the syringe graduations were used measure the air under vacuum it could not be expected to serve as a 1:1 volume ratio of water that was pulled into the tip because under vacuum the air had expanded.
+This explains the negative systematic error we were experiencing.
+The water in the tip pulls on the air due to gravity whcih causes it to expand slighty but enough to make measuing with the graduation in this way inaccurate.
+Our solution was to replace the built-in scale with a scale that acounted for the expansion.
+Using the data from our inital testing we calulated a factor for the expansion and used that to make the new scale.
+With the new scale taped on the syringe our validation testing met the ISO 8655 standard.
 Replacing the scale with our scale that accounts for the expansion corrected this effect. 
@@
 Most significantly the user is able to adjust the syringe accurately without verifying the volume with a scale.
+The pipette can be adjuseted to any discrete volume within range.
 In addition the assembly requires no permanent connections using tape or glue which allows for re-configuration and easy replacement of parts.
-Our pipette is able to transfer from the bottom of a 15 mL conical tube which is a requirement for many routine lab procedures such as aspirating supernatant from a centrifuged cell pellet.
-This design does not use a membrane that may wear out and require tedious replacement.
+Conveniently our design can also reach to the bottom of a 15 mL conical tube allowing tasks such as aspirating supernatant fluid from a cell pellet.
+Unlike existing designs our desing does not use a membrane that may wear out and require tedious replacement.
+The only major limitation of this design compared to the biropipette is the option for a pipette tip ejector.
+The biropipette also uses arguably easier to source parts (a pen VS a syringe) relative to what is required from our design.
 
-The only major limitation of this design compared to the biropipette is the option for a pipette tip ejector.
-The biropipette also uses easier to source parts relative to what is required from our design.
-
+The open design nature of this project encourages anyone to use and submit changes to improve and add features to this design.
+All of the working files and documentation are kept in a public repository\ref{micropipetterepo}.
 % Please add the following required packages to your document preamble:

### 2016-12-31 Plos-one-manuscript/latex/manuscript.tex
working on manuscript

@@
 The biropipette also uses arguably easier to source parts (a pen VS a syringe) relative to what is required from our design.
+The biropipette also was developed in OpenSCAD which is free and open source CAD software where our design was created in Solidworks a propriatiery software.
 
@@
 \end{table}
+
+\section*{Conclusion}
+We have presented an open design micropipette that uses 3D-printable parts in addition to a disposable syringe and a few eaisly sourced pieces of hardware.
+Our open design pipette is novel in that it allows the user to set the pipette to the desired volume with out the need to calibrate or verify with a weighing scale. 
+We validated the accuracy and presiion of our pipette and developed a new graduation scale to correct for the use of the syringe for air-displacemet measurements.
+o meet the ISO standard for adjustable pipettes.
+Our design is free to use and modifiy to encourage further collabrateive developlement.
 

### 2017-01-02 Plos-one-manuscript/latex/manuscript.tex
spell check

@@
 One example of a everyday scientific tool that provides opportunity for an open design solution is the micropipette.
-A open design pipette that can be made for cheap can cut costs and allow for more options for labs and educational settings.
+A open design micropipette that can be made for cheap can cut costs and allow for more options for labs and educational settings.
 Micropipettes are an indispensable tool used routinely in lab tasks and can easily cost \$1000 USD for a set.
@@
 
-\subsection*{Assembly}
+\subsection*{Fabrication & Assembly}
+Two parts are printed (body.stl and plunger.stl) at normal resolution with rafts on a Makerbot Replicator.
 A small amount of paraffin wax is applied to the screw to prevent slop from causing the set point to drift after each actuation.
-The nut is sunk in to the hex inset in the body part.
+The nut is sunk in to the hex inset in the printed body part.
 The bolt is threaded in from the top of the body into the nut.
-Springs and washers are threaded onto the plunger of the 1 mL syringe for the 30-300 uL configuration.
-Springs are placed inside the 3 mL syringe for the 100-1000 mL configuration.
+Springs and washers are threaded onto the plunger of a 1 mL syringe for the 30-300 uL configuration.
+Springs are placed inside a 3 mL syringe for the 100-1000 mL configuration.
 The plunger part is inserted in the body and the syringe assembly is pushed in and locked from the syringe flanges to the body part to complete assembly.
@@
 The printed pipette was adjusted to the target volume by eye from the syringe graduations.
-Dionized water was transfered and measured with a scale,
-Five transferes were recorded and averaged to account for random variability.
+Deionized water was transferred and measured with a scale,
+Five transfers were recorded and averaged to account for random variability.
 Data was taken for printed pipettes with existing syringe graduations as well as with the our adjusted scale.
@@
 Validation testing preformed with the existing graduations printed on the syringes did not meet the ISO standards.
-According to ISO 8655 for a pipette with the maximum nominal volume of 1000 uL the systematic error cannot excede 8 uL and the random error cannot excede 3 uL and the the maximum nominal volume of 300 uL the systemic error cannot excede 4 uL and the random error cannot excede 1.5 uL.
-The commerical pipettes met these standards handidly, but in our initial tests with our printed pipette we noticied large negaive systematic error suggesting that we were missing a biasing factor. 
-This error was exagurated while transfering larger volumes.
+According to ISO 8655 for a pipette with the maximum nominal volume of 1000 uL the systematic error cannot exceed 8 uL and the random error cannot exceed 3 uL
+For the maximum nominal volume of 300 uL the systemic error cannot exceed 4 uL and the random error cannot exceed 1.5 uL.
+The commercial pipettes met these standards handily, but in our initial tests with our printed pipette we noticed large negative systematic error suggesting that we were missing a biasing factor. 
+This error was exaggerated while transferring larger volumes.
 After further investigation we realized that the graduations are intended to measure incompressible fluids within the syringe while we were using them to measure air while under vacuum.
-Becasue the syringe graduations were used measure the air under vacuum it could not be expected to serve as a 1:1 volume ratio of water that was pulled into the tip because under vacuum the air had expanded.
+Because the syringe graduations were used measure the air under vacuum it could not be expected to serve as a 1:1 volume ratio of water that was pulled into the tip because under vacuum the air had expanded.
 This explains the negative systematic error we were experiencing.
-The water in the tip pulls on the air due to gravity whcih causes it to expand slighty but enough to make measuing with the graduation in this way inaccurate.
-Our solution was to replace the built-in scale with a scale that acounted for the expansion.
-Using the data from our inital testing we calulated a factor for the expansion and used that to make the new scale.
+The water in the tip pulls on the air due to gravity which causes it to expand slightly but enough to make measuring with the graduation in this way inaccurate.
+Our solution was to replace the built-in scale with a scale that accounted for the expansion.
+Using the data from our initial testing we calculated a factor for the expansion and used that to make the new scale.
 With the new scale taped on the syringe our validation testing met the ISO 8655 standard.
@@
 Most significantly the user is able to adjust the syringe accurately without verifying the volume with a scale.
-The pipette can be adjuseted to any discrete volume within range.
+The pipette can be adjusted to any discrete volume within range.
 In addition the assembly requires no permanent connections using tape or glue which allows for re-configuration and easy replacement of parts.
 Conveniently our design can also reach to the bottom of a 15 mL conical tube allowing tasks such as aspirating supernatant fluid from a cell pellet.
-Unlike existing designs our desing does not use a membrane that may wear out and require tedious replacement.
+Unlike existing designs our design does not use a membrane that may wear out and require tedious replacement.
 The only major limitation of this design compared to the biropipette is the option for a pipette tip ejector.
 The biropipette also uses arguably easier to source parts (a pen VS a syringe) relative to what is required from our design.
-The biropipette also was developed in OpenSCAD which is free and open source CAD software where our design was created in Solidworks a propriatiery software.
+The biropipette also was developed in OpenSCAD which is free and open source CAD software where our design was created in Solidworks a proprietary software.
 

### 2017-01-02 Plos-one-manuscript/latex/manuscript.tex
fixed citations

@@
 Open source development of lab equipment is being facilitated, in part, by growing availability of 3D printing which allows the production of simple lab tools.
-We developed 3D-printable parts that, along with a disposable syringe, form a micropipette.
-Once assembled the pipette requires no calibration or validation with a scale.
-Our printed micropipette is assessed in comparison to a commercial pipette demonstrating comparable performance in accuracy and precision and approaches ISO standard.
+We developed 3D-printable parts that, along with a disposable syringe, form a micropipette that requires no calibration or validation with a scale.
+Our printed micropipette is assessed in comparison to a commercial pipette and meets ISO 8655 standards.
 
@@
 \section*{Introduction}
-The open source development model, initially applied to software, is thriving in the development of open source scientific equipment due in part to increasing access of 3D printing \cite{Baden2015,Pearce2014}.
-Additive manufacturing methods have existed for decades although the recent availability of inexpensive desktop printers\cite{MakerbotIndustries2016,Reprap2015} have made it feasible for consumers to design and print prototypes and even functional parts, and consumer goods\cite{Fullerton2014}.
-Proliferation of free CAD software[OpenSCAD, Blender, SketchUp] and design sharing sites\cite{MakerbotIndustries2016,NationalInstitutesofHealth2015,grabCAD,GitHubInc.2016} have also supported the growth and popularity of open designed parts and projects.
+The open source development model, initially applied to software, is thriving in the development of open source scientific equipment due in part to increasing access of 3D printing\cite{Baden2015,Pearce2013}.
+Additive manufacturing methods have existed for decades although the recent availability of inexpensive desktop printers\cite{MakerbotIndustries,RepRap} have made it feasible for consumers to design and print prototypes and even functional parts, and consumer goods\cite{Fullerton2014}.
+Proliferation of free CAD software\cite{OpenScad,Blender,SketchUp,123D} and design sharing sites\cite{Thingiverse,NationalInstitutesofHealth,GrabCAD,GitHubInc} have also supported the growth and popularity of open designed parts and projects.
 Open design 3D-printable lab equipment is an attractive idea because, like open source software, it allows free access to technology that is otherwise inaccessible due to proprietary and/or financial barriers.
@@
 Some simple and clever printable parts that have emerged are ones that give a new function to a ubiquitous existing device, such as drill bit attachment designed to hold centrifuge tubes, allowing a drill to be used as a centrifuge\cite{Garvey2009}.
-Although this may make a rather crude centrifuge it may be an adequate method which only costs pennies compared to commercially available centrifuges.
+Although this may make a rather crude centrifuge it may be adequate which only costs pennies compared to commercially available centrifuges.
 Other examples of open-design research tools that utilize 3D printed parts include optics equipment\cite{Zhang2013}, microscopes\cite{Baden2014a,Walus2014}, syringe pumps\cite{Wijnen2014}, and reactionware\cite{Symes2012} to name a few.
@@
 
-Air displacement pipettes use a piston operating principal to draw liquid into the pipette\cite{ISO2002}.
+Air displacement pipettes use a piston operating principal to draw liquid into the pipette\cite{ISO8655}.
 In a typical commercial pipette the piston is made to be gas-tight with a gasketed plunger inside a smooth barrel.
@@
 
-\subsection*{Fabrication & Assembly}
+\subsection*{Fabrication \& Assembly}
 Two parts are printed (body.stl and plunger.stl) at normal resolution with rafts on a Makerbot Replicator.
@@
 The plunger part is inserted in the body and the syringe assembly is pushed in and locked from the syringe flanges to the body part to complete assembly.
-Parts and cost are listed in tables~\ref{table1,table2}
+Parts and cost are listed in Table~\ref{table1} and \ref{table2}.
 
@@
 Data was taken with commercial pipettes of 30-300 and 100-1000 to compare to the printed pipette. 
-The systematic error and random error was calculated according to ISO 8655~\ref{ISO2013} (Table~\ref{table3,table4}).
+The systematic error and random error was calculated according to ISO 8655~\cite{ISO8655} (Table~\ref{table3} and \ref{table4}).
 
@@
 Validation testing preformed with the existing graduations printed on the syringes did not meet the ISO standards.
-According to ISO 8655 for a pipette with the maximum nominal volume of 1000 uL the systematic error cannot exceed 8 uL and the random error cannot exceed 3 uL
+According to ISO 8655 for a pipette with the maximum nominal volume of 1000 uL the systematic error cannot exceed 8 uL and the random error cannot exceed 3 uL.
 For the maximum nominal volume of 300 uL the systemic error cannot exceed 4 uL and the random error cannot exceed 1.5 uL.
@@
 Replacing the scale with our scale that accounts for the expansion corrected this effect. 
-Our printed pipette with the adjusted scale meets ISO standards for accuracy and precision. (Table~\ref{table1 ,table2}).
+Our printed pipette with the adjusted scale meets ISO standards for accuracy and precision. (Table \ref{table3} and \ref{table4}).
 
@@
 \section*{Conclusion}
-We have presented an open design micropipette that uses 3D-printable parts in addition to a disposable syringe and a few eaisly sourced pieces of hardware.
+We have presented an open design micropipette that uses 3D-printable parts in addition to a disposable syringe and a few easily sourced pieces of hardware.
 Our open design pipette is novel in that it allows the user to set the pipette to the desired volume with out the need to calibrate or verify with a weighing scale. 
-We validated the accuracy and presiion of our pipette and developed a new graduation scale to correct for the use of the syringe for air-displacemet measurements.
+We validated the accuracy and precision of our pipette and developed a new graduation scale to correct for the use of the syringe for air-displacement measurements.
 o meet the ISO standard for adjustable pipettes.
-Our design is free to use and modifiy to encourage further collabrateive developlement.
+Our design is free to use and modify to encourage further collaborative development.
 
-%\begin{table}[!ht]
-%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
-%\caption{
-%{\bf Table caption Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.}}
-%\begin{tabular}{|l|l|l|l|l|l|l|l|}
-%\hline
-%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \hline
-%$cell1 row1$ & cell2 row 1 & cell3 row 1 & cell4 row 1 & cell5 row 1 & cell6 row 1 & cell7 row 1 & cell8 row 1\\ \hline
-%$cell1 row2$ & cell2 row 2 & cell3 row 2 & cell4 row 2 & cell5 row 2 & cell6 row 2 & cell7 row 2 & cell8 row 2\\ \hline
-%$cell1 row3$ & cell2 row 3 & cell3 row 3 & cell4 row 3 & cell5 row 3 & cell6 row 3 & cell7 row 3 & cell8 row 3\\ \hline
-%\end{tabular}
-%\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl.
-Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
-%\end{flushleft}
-%\label{table1}
-%\end{adjustwidth}
-%\end{table}
+%For more information, see \nameref{S1_Text}.
 
-% Please do not create a heading level below \subsection. For 3rd level headings, use \paragraph{}.
-
-For more information, see \nameref{S1_Text}.
-
-\section*{Supporting Information}
-
-% Include only the SI item label in the subsection heading. Use the \nameref{label} command to cite SI items in the text.
-%\subsection*{S1 Video}
-%\label{S1_Video}
-%{\bf Bold the first sentence.}  Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-
-%\subsection*{S1 Text}
-%\label{S1_Text}
-%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-
-%\subsection*{S1 Fig}
-%\label{S1_Fig}
-%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-
-%\subsection*{S2 Fig}
-%\label{S2_Fig}
-%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-
-%\subsection*{S1 Table}
-%\label{S1_Table}
-%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-
-%\section*{Acknowledgments}
-%Cras egestas velit mauris, eu mollis turpis pellentesque sit amet.
-Interdum et malesuada fames ac ante ipsum primis in faucibus.
-Nam id pretium nisi.
-Sed ac quam id nisi malesuada congue.
-Sed interdum aliquet augue, at pellentesque quam rhoncus vitae.
+%\section*{Supporting Information}
 
@@
 
-%\section*{References}
-% Either type in your references using
-% \begin{thebibliography}{}
-% \bibitem{}
-% Text
-% \end{thebibliography}
-%
-% OR
-%
-% Compile your BiBTeX database using our plos2015.bst
-% style file and paste the contents of your .bbl file
-% here.
-% 
 \bibliographystyle{plos2015.bst}

### 2017-01-02 Plos-one-manuscript/latex/manuscript.tex
a word
working on figures

@@
 Often a lab will require several sets each for a dedicated task.
-Some pipettes are even re-calibrated for use with liquids of different properties.
+Some pipettes may even re-calibrated for use with liquids of different properties.
 
@@
 Our printed pipette is designed to actuate a 1 mL or 3 mL syringe to a user set displacement.
-The core of the design is two printed parts, the body and the plunger which are able to be printed on a consumer grade FDM printer.
+The core of the design is two printed parts, the body and the plunger which are able to be printed on a consumer grade FDM printer (fig.~\ref{fig1}).
 A 1 mL or 3 mL syringe twists to lock in the body part and is held into place by the syringe flanges.
 The 30-300 uL configuration uses a 1 mL pipette and the 100-1000 uL configuration uses a 3 mL pipette.
-The plunger part slides freely in the body part and actuates the syringe by pushing the thumb press. 
+The plunger part slides freely in the body part and actuates the syringe by pushing the thumb button (fig.~\ref{fig2}). 
 The pipette is spring loaded towards a set point which is adjustable by a set-screw.
-When the plunger is depressed the system locks when it reaches the latched position, where it is ready to draw in fluid.
-The plunger is held in place with a latching button design which is released with a lever drawing in fluid.
+When the when the thumb button is pressed the system locks when it reaches the latched position, where it is ready to draw in fluid.
+The plunger is held in place with a latching button design which is released with the unlatching button drawing in fluid.
 The displacement is equal to the distance between the set position and the latched position.
@@
 
+\begin{figure}
+	\caption{
+		{\bf CAD renderings of printable parts and cross-sections.} (A) The printed plunger part is a shaft pushes on the syringe plunger and slides in the printed body part.
+The printed plunger has a latching tongue and button which interfaces with the printed body part.
+(B) The printed body part holds the syringe and interfaces with the printed plunger part.
+The body part features the un-latching button and slots to hold the syringe in place by its flanges.
+The body part also has two cutouts in the top for the plunger button and for the hex nut and bolt.
+	}
+	\label{fig1}
+\end{figure}
+
+\begin{figure}
+	\caption{
+		{\bf CAD renderings of assembled pipette and function.} The pipetted actuates the syringe to three positions.
+{\bf(i) The set position.} The position of the screw determines the total displacement.
+The pipette is spring loaded to return to this position.
+{\bf (ii) The latched position.} When the plunger is pressed the pipette locks at this position.
+The tip is then placed in a liquid and the unlatching button is pressed to release the pipette back to the set position, drawing in liquid.
+{\bf (iii) The blow-out position.} The fluid is transferred by pressing the plunger past the latched position to blow-out all the liquid.
+	}
+	\label{fig2}
+\end{figure}
+
 Our pipette uses the air-displacement design, where a pocket of air is used to draw liquid into the pipette.
@@
 The scale is printed on a transparency sheet and is taped onto the syringe for accurate measurements. 
-
 \subsection*{Fabrication \& Assembly}
@@
 Springs are placed inside a 3 mL syringe for the 100-1000 mL configuration.
-The plunger part is inserted in the body and the syringe assembly is pushed in and locked from the syringe flanges to the body part to complete assembly.
+The plunger part is inserted in the body and the syringe assembly is pushed in and locked from the syringe flanges to the body part to complete assembly(fig.~\ref{fig3}).
 Parts and cost are listed in Table~\ref{table1} and \ref{table2}.
@@
 \end{table}
-
-\begin{figure}
-\caption{
-{\bf CAD renderings of printable parts.} Two parts are printed: The plunger part (A) slides inside the body part (B).
-}
-\label{fig1}
-\end{figure}
-
-\begin{figure}
-\caption{
-{\bf CAD renderings of assembled pipette and function.} The pipetted actuates the syringe to three positions.
-{\bf(i) The set position.} The position of the screw determines the total displacement.
-The pipette is spring loaded to return to this position {\bf (ii) The latched position.} When the plunger is pressed the pipette locks at this position.
-The tip is then placed in a liquid and the button pressed to release the pipette back to the set position, drawing in liquid.
-{\bf (iii) The blow-out position.} The fluid is transferred by pressing the plunger past the latched position to blow-out all the liquid.
-}
-\label{fig2}
-\end{figure}
 
@@
 
-%\section*{Supporting Information}
+\section*{Supporting Information}
+
+\subsection*{S1 Fig}
+\label{S1_Fig}
+{\bf Adjusted Scale Graduations for 30-300 uL Pipette.} New scale graduations that can be printed on a transparency sheet and taped onto a 1 mL syringe.
+Using these graduations will correct for expansion of air and allow ISO standards to be met.
+PDF format for ease of printing to scale.
+1 inch and 1 cm marks to check scale as well as reproduction of standard graduation marks.
+
+\subsection*{S2 Fig}
+\label{S2_Fig}
+{\bf Adjusted Scale Graduations for 100-1000 uL Pipette.} New scale graduations that can be printed on a transparency sheet and taped onto a 3 mL syringe.
+Using these graduations will correct for expansion of air and allow ISO standards to be met.
+PDF format for ease of printing to scale.
+1 inch and 1 cm marks to check scale as well as reproduction of standard graduation marks.
 

### 2017-01-02 Plos-one-manuscript/latex/manuscript.tex
added SI and updated figures

@@
 We remedied this by creating a new scale to account for the expansion.
-The scale is printed on a transparency sheet and is taped onto the syringe for accurate measurements. 
+The scale is printed on a transparency sheet and is taped onto the syringe for accurate measurements (See~\nameref{S1_Fig} and \nameref{S2_Fig}).
+
 \subsection*{Fabrication \& Assembly}
@@
 Parts and cost are listed in Table~\ref{table1} and \ref{table2}.
+
+\begin{figure}
+	\caption{
+		{\bf Photos of assembled pipettes.}  (A) Two assemblies of the pipette: the 100-1000 uL configuration (above) and the 30-300 uL configuration (below).
+(B) Close-up photo of the taped on scale for each of the syringes.
+	}
+	\label{fig3}
+\end{figure}
 
@@
 \end{table}
-
-\begin{figure}
-\caption{
-{\bf Photos of pipette.}  The pipette is composed of two printed parts, a 1 mL syringe and some additional hardware.  
-}
-\label{fig3}
-\end{figure}
 

### 2017-01-03 Plos-one-manuscript/latex/manuscript.tex
updated citations

@@
 We developed 3D-printable parts that, along with a disposable syringe, form a micropipette that requires no calibration or validation with a scale.
-Our printed micropipette is assessed in comparison to a commercial pipette and meets ISO 8655 standards.
+Our open design printed micropipette is assessed in comparison to a commercial pipette and meets ISO 8655 standards.
 
@@
 The open source development model, initially applied to software, is thriving in the development of open source scientific equipment due in part to increasing access of 3D printing\cite{Baden2015,Pearce2013}.
-Additive manufacturing methods have existed for decades although the recent availability of inexpensive desktop printers\cite{MakerbotIndustries,RepRap} have made it feasible for consumers to design and print prototypes and even functional parts, and consumer goods\cite{Fullerton2014}.
+Additive manufacturing methods have existed for decades although the recent availability of inexpensive desktop printers\cite{MakerbotIndustries,RepRap} have made it feasible for consumers to design and print prototypes and even functional parts, and consumer goods\cite{Fullerton2014,Wittbrodt2013}.
 Proliferation of free CAD software\cite{OpenScad,Blender,SketchUp,123D} and design sharing sites\cite{Thingiverse,NationalInstitutesofHealth,GrabCAD,GitHubInc} have also supported the growth and popularity of open designed parts and projects.
 Open design 3D-printable lab equipment is an attractive idea because, like open source software, it allows free access to technology that is otherwise inaccessible due to proprietary and/or financial barriers.
-Open design tools create opportunity for scientists and educational programs in remote or resource limited areas to participate with inexpensive and easy to make tools\cite{Baden2015}. 
-Open source development also enables the development of custom solutions to meet unique applications not met by commercial products that are shared freely and are user modifiable\cite{Fullerton2014,Pearce2012}.
+Open design tools create opportunity for scientists and educational programs in remote or resource limited areas to participate with inexpensive and easy to make tools\cite{Baden2015,Marzullo2012,Lang2011,Baker2014,Cybulski2014}.
+Open source development also enables the development of custom solutions to meet unique applications not met by commercial products that are shared freely and are user modifiable\cite{Fullerton2014,Pearce2012,Rankin2014,Sulkin2013}.
 Some advanced, noteworthy, open-source scientific equipment include a PCR device\cite{ChaiBiotechnologiesInc2015}, and a two-photon microscope\cite{Rosenegger2014} although simple tools are often more impactful as they can serve a wider community.
+
 Some simple and clever printable parts that have emerged are ones that give a new function to a ubiquitous existing device, such as drill bit attachment designed to hold centrifuge tubes, allowing a drill to be used as a centrifuge\cite{Garvey2009}.
@@
 The open design nature of this project encourages anyone to use and submit changes to improve and add features to this design.
-All of the working files and documentation are kept in a public repository\ref{micropipetterepo}.
+All of the working files and documentation are kept in a public repository~\cite{BMLmicropipette}.
 % Please add the following required packages to your document preamble:

### 2017-01-03 Plos-one-manuscript/latex/manuscript.tex
updated figures
minor corrections

@@
 Some simple and clever printable parts that have emerged are ones that give a new function to a ubiquitous existing device, such as drill bit attachment designed to hold centrifuge tubes, allowing a drill to be used as a centrifuge\cite{Garvey2009}.
-Although this may make a rather crude centrifuge it may be adequate which only costs pennies compared to commercially available centrifuges.
+Although this may make a rather crude centrifuge it may be an adequate solution which only costs pennies compared to commercially available centrifuges.
 Other examples of open-design research tools that utilize 3D printed parts include optics equipment\cite{Zhang2013}, microscopes\cite{Baden2014a,Walus2014}, syringe pumps\cite{Wijnen2014}, and reactionware\cite{Symes2012} to name a few.
@@
 A few open design micropipettes exist including a popular one which, in addition to the printed parts, uses parts scavenged from a retractable pen\cite{Baden2014}.
-Because there is no built-in feature such as a readout for the user to set the displacement to a desired volume, this design requires the user to validate the volumes dispensed with a high precision scale.
+Because there is no built in feature such as a readout for the user to set the displacement to a desired volume, this design requires the user to validate the volumes dispensed with a high precision scale.
 Without verification with a scale the volumes dispensed can only be estimated based on calculations of the deflection of the membrane.
 
-We submit a new design who's major strength is the ability to adjust to any volume according to a built in scale.
+We submit a new design whose major strength is the ability to adjust to any volume according to a built in scale.
 Our open design 3D-printable micropipette works by actuating a disposable syringe to a user adjustable set-point.
@@
 A 1 mL or 3 mL syringe twists to lock in the body part and is held into place by the syringe flanges.
-The 30-300 uL configuration uses a 1 mL pipette and the 100-1000 uL configuration uses a 3 mL pipette.
+The 30-300 $\mu$L configuration uses a 1 mL pipette and the 100-1000 $\mu$L configuration uses a 3 mL pipette.
 The plunger part slides freely in the body part and actuates the syringe by pushing the thumb button (fig.~\ref{fig2}). 
 The pipette is spring loaded towards a set point which is adjustable by a set-screw.
-When the when the thumb button is pressed the system locks when it reaches the latched position, where it is ready to draw in fluid.
+When the thumb button is pressed the system locks when it reaches the latched position, where it is ready to draw in fluid.
 The plunger is held in place with a latching button design which is released with the unlatching button drawing in fluid.
 The displacement is equal to the distance between the set position and the latched position.
-The pipette can also be pressed past the latched position to 'blow-out' the transferred fluid completely from the pipette tip.   
-Additional materials required for assembly include a spring, a nut and bolt and washers.
+The pipette can also be pressed past the latched position to `blow-out' the transferred fluid completely from the pipette tip.   
+Additional materials required for assembly include two springs, a nut, a bolt and two washers.
 Attempts to make a printable luer lock adapter for tips was abandoned as the surface of printed parts is too rough to make an air tight seal with the luer or pipette tip.
@@
 (B) The printed body part holds the syringe and interfaces with the printed plunger part.
-The body part features the un-latching button and slots to hold the syringe in place by its flanges.
+The body part features the unlatching button and slots to hold the syringe in place by its flanges.
 The body part also has two cutouts in the top for the plunger button and for the hex nut and bolt.
@@
 Due to this effect the graduations on the syringe are not accurate, as they are designed for measuring liquid within the syringe.
-At larger volumes this effect is more pronounced resulting in the volume measured being greater then the amount of liquid pulled into the syringe.
+At larger volumes this effect is more pronounced resulting in the volume measured being greater than the amount of liquid pulled into the syringe.
 We remedied this by creating a new scale to account for the expansion.
@@
 A small amount of paraffin wax is applied to the screw to prevent slop from causing the set point to drift after each actuation.
-The nut is sunk in to the hex inset in the printed body part.
+The nut is sunk into the hex inset in the printed body part.
 The bolt is threaded in from the top of the body into the nut.
-Springs and washers are threaded onto the plunger of a 1 mL syringe for the 30-300 uL configuration.
-Springs are placed inside a 3 mL syringe for the 100-1000 mL configuration.
+Springs and washers are threaded onto the plunger of a 1 mL syringe for the 30-300 $\mu$L configuration.
+Springs are placed inside a 3 mL syringe for the 100-1000 $\mu$L configuration.
 The plunger part is inserted in the body and the syringe assembly is pushed in and locked from the syringe flanges to the body part to complete assembly(fig.~\ref{fig3}).
@@
 	\caption{
-		{\bf Photos of assembled pipettes.}  (A) Two assemblies of the pipette: the 100-1000 uL configuration (above) and the 30-300 uL configuration (below).
+		{\bf Photos of assembled pipettes.}  (A) Two assemblies of the pipette: the 100-1000 $\mu$L configuration (above) and the 30-300 $\mu$L configuration (below).
 (B) Close-up photo of the taped on scale for each of the syringes.
@@
 \centering
-\caption{Parts and cost for the 30-300 uL pipette.}
+\caption{Parts and cost for the 30-300 $\mu$L pipette.}
 \label{table1}
@@
 \centering
-\caption{Parts and cost for the 100-1000 uL pipette.}
+\caption{Parts and cost for the 100-1000 $\mu$L pipette.}
 \label{table2}
@@
 The printed pipette was adjusted to the target volume by eye from the syringe graduations.
-Deionized water was transferred and measured with a scale,
+Deionized water was transferred and measured with a scale.
 Five transfers were recorded and averaged to account for random variability.
 Data was taken for printed pipettes with existing syringe graduations as well as with the our adjusted scale.
-Data was taken with commercial pipettes of 30-300 and 100-1000 to compare to the printed pipette. 
+Data was taken with commercial pipettes of 30-300 $\mu$L and 100-1000 $\mu$L to compare to the printed pipette.
 The systematic error and random error was calculated according to ISO 8655~\cite{ISO8655} (Table~\ref{table3} and \ref{table4}).
@@
 Validation testing preformed with the existing graduations printed on the syringes did not meet the ISO standards.
-According to ISO 8655 for a pipette with the maximum nominal volume of 1000 uL the systematic error cannot exceed 8 uL and the random error cannot exceed 3 uL.
-For the maximum nominal volume of 300 uL the systemic error cannot exceed 4 uL and the random error cannot exceed 1.5 uL.
+According to ISO 8655 for a pipette with the maximum nominal volume of 1000 $\mu$L the systematic error cannot exceed 8 $\mu$L and the random error cannot exceed 3 $\mu$L.
+For the maximum nominal volume of 300 $\mu$L the systemic error cannot exceed 4 $\mu$L and the random error cannot exceed 1.5 $\mu$L.
 The commercial pipettes met these standards handily, but in our initial tests with our printed pipette we noticed large negative systematic error suggesting that we were missing a biasing factor. 
@@
 After further investigation we realized that the graduations are intended to measure incompressible fluids within the syringe while we were using them to measure air while under vacuum.
-Because the syringe graduations were used measure the air under vacuum it could not be expected to serve as a 1:1 volume ratio of water that was pulled into the tip because under vacuum the air had expanded.
+Because the syringe graduations were used to measure the air under vacuum it could not be expected to serve as a 1:1 volume ratio of water that was pulled into the tip because under vacuum the air had expanded.
 This explains the negative systematic error we were experiencing.
@@
 The pipette can be adjusted to any discrete volume within range.
-In addition the assembly requires no permanent connections using tape or glue which allows for re-configuration and easy replacement of parts.
-Conveniently our design can also reach to the bottom of a 15 mL conical tube allowing tasks such as aspirating supernatant fluid from a cell pellet.
+In addition, the assembly requires no permanent connections using tape or glue which allows for re-configuration and easy replacement of parts.
+Conveniently, our design can also reach to the bottom of a 15 mL conical tube allowing tasks such as aspirating supernatant fluid from a cell pellet.
 Unlike existing designs our design does not use a membrane that may wear out and require tedious replacement.
@@
 \centering
-\caption{ISO 8655 for 100-1000 uL comparing a commercial pipette with our printed pipette used with existing 3 mL syringe scale and an adjusted scale}
+\caption{ISO 8655 for 100-1000 $\mu$L comparing a commercial pipette with our printed pipette used with existing 3 mL syringe scale and an adjusted scale}
 \label{table3}
@@
         &                       & Mean   & Systematic Error & \% Sys. err. & Random Error & \% Rand. err. \\
-1000 uL & ISO 8655, 100-1000 uL & 1000    & 8.00             & 0.80         & 3.00         & 0.30          \\
+1000 $\mu$L & ISO 8655, 100-1000 $\mu$L & 1000    & 8.00             & 0.80         & 3.00         & 0.30          \\
         & Commercial Pipette    & 1002.98 & 2.98             & 0.30         & 1.72         & 0.17          \\
@@
         &                       &         &                  &              &              &               \\
-500 uL  & ISO 8655, 100-1000 uL & 500     & 8.00             & 1.60         & 3.00         & 0.60          \\
+500 $\mu$L  & ISO 8655, 100-1000 $\mu$L & 500     & 8.00             & 1.60         & 3.00         & 0.60          \\
         & Commercial Pipette    & 503.67  & 3.67             & 0.73         & 0.49         & 0.10          \\
@@
         &                       &         &                  &              &              &               \\
-200 uL  & ISO 8655, 100-1000 uL & 200     & 8.00             & 4.00         & 3.00         & 1.50          \\
+200 $\mu$L  & ISO 8655, 100-1000 $\mu$L & 200     & 8.00             & 4.00         & 3.00         & 1.50          \\
         & Commercial Pipette    & 204.61  & 4.61             & 2.30         & 0.15         & 0.07          \\
@@
         &                       &         &                  &              &              &               \\
-100 uL  & ISO 8655, 100-1000 uL & 100     & 8.00             & 8.00         & 3.00         & 3.00          \\
+100 $\mu$L  & ISO 8655, 100-1000 $\mu$L & 100     & 8.00             & 8.00         & 3.00         & 3.00          \\
         & Commercial Pipette    & 104.29  & 4.29             & 4.29         & 1.65         & 1.58          \\
@@
 \centering
-\caption{ISO 8655 for 30-300 uL comparing a commercial pipette with our printed pipette used with existing 3 mL syringe scale and an adjusted scale}
+\caption{ISO 8655 for 30-300 $\mu$L comparing a commercial pipette with our printed pipette used with existing 3 mL syringe scale and an adjusted scale}
 \label{table4}
@@
        &                       & Mean   & Systematic Error & \% Sys. err. & Random Error & \% Rand. err. \\
-300 uL & ISO 8655, 30-300 uL   & 300    & 4.00             & 1.33         & 1.50         & 0.50          \\
+300 $\mu$L & ISO 8655, 30-300 $\mu$L   & 300    & 4.00             & 1.33         & 1.50         & 0.50          \\
        & Commercial Pipette    & 301.19 & 1.19             & 0.40         & 0.53         & 0.18          \\
@@
        &                       &        &                  &              &              &               \\
-200 uL & ISO 8655, 30-300 uL   & 200    & 4                & 2            & 1.5          & 0.75          \\
+200 $\mu$L & ISO 8655, 30-300 $\mu$L   & 200    & 4                & 2            & 1.5          & 0.75          \\
        & Commercial Pipette    & 200.06 & 0.06             & 0.03         & 0.46         & 0.23          \\
@@
        &                       &        &                  &              &              &               \\
-50 uL  & ISO 8655, 30-300 uL   & 50     & 4                & 8            & 1.5          & 3             \\
+50 $\mu$L  & ISO 8655, 30-300 $\mu$L   & 50     & 4                & 8            & 1.5          & 3             \\
        & Commercial Pipette    & 49.02  & -0.98            & -1.96        & 0.10         & 0.20          \\
@@
        &                       &        &                  &              &              &               \\
-30 uL  & ISO 8655, 30-300 uL   & 30     & 4                & 13.3         & 1.5          & 5             \\
+30 $\mu$L  & ISO 8655, 30-300 $\mu$L   & 30     & 4                & 13.3         & 1.5          & 5             \\
        & Commercial Pipette    & 29.08  & -0.92            & -3.06        & 0.09         & 0.31          \\
@@
        &                       &        &                  &              &              &               \\
-20 uL* & ISO 8655, 30-300 uL   & 20     & 4                & 20           & 1.5          & 7.5           \\
+20 $\mu$L* & ISO 8655, 30-300 $\mu$L   & 20     & 4                & 20           & 1.5          & 7.5           \\
        & Commercial Pipette    & NA     & NA               & NA           & NA           & NA            \\
@@
        &                       &        &                  &              &              &               \\
-10 uL* & ISO 8655, 30-300 uL   & 10     & 4                & 40           & 1.5          & 15            \\
+10 $\mu$L* & ISO 8655, 30-300 $\mu$L   & 10     & 4                & 40           & 1.5          & 15            \\
        & Commercial Pipette    & NA     & NA               & NA           & NA           & NA            \\
@@
 \end{tabular}
-\begin{flushleft} * The 20 uL and 10 uL volumes are out of the range in this case but we wanted to demonstrate that the pipette is capable of even smaller volumes.
+\begin{flushleft} * The 20 $\mu$L and 10 $\mu$L volumes are out of the range in this case but we wanted to demonstrate that the pipette is capable of even smaller volumes.
 \end{flushleft}
@@
 We have presented an open design micropipette that uses 3D-printable parts in addition to a disposable syringe and a few easily sourced pieces of hardware.
-Our open design pipette is novel in that it allows the user to set the pipette to the desired volume with out the need to calibrate or verify with a weighing scale. 
-We validated the accuracy and precision of our pipette and developed a new graduation scale to correct for the use of the syringe for air-displacement measurements.
-o meet the ISO standard for adjustable pipettes.
+Our open design pipette is novel in that it allows the user to set the pipette to the desired volume without the need to calibrate or verify with a weighing scale. 
+We validated the accuracy and precision of our pipette and developed a new graduation scale to correct for the use of the syringe for air-displacement measurements that meets the ISO standard for adjustable pipettes.
 Our design is free to use and modify to encourage further collaborative development.
@@
 \label{S1_Fig}
-{\bf Adjusted Scale Graduations for 30-300 uL Pipette.} New scale graduations that can be printed on a transparency sheet and taped onto a 1 mL syringe.
+{\bf Adjusted Scale Graduations for 30-300 $\mu$L Pipette.} New scale graduations that can be printed on a transparency sheet and taped onto a 1 mL syringe.
 Using these graduations will correct for expansion of air and allow ISO standards to be met.
@@
 \label{S2_Fig}
-{\bf Adjusted Scale Graduations for 100-1000 uL Pipette.} New scale graduations that can be printed on a transparency sheet and taped onto a 3 mL syringe.
+{\bf Adjusted Scale Graduations for 100-1000 $\mu$L Pipette.} New scale graduations that can be printed on a transparency sheet and taped onto a 3 mL syringe.
 Using these graduations will correct for expansion of air and allow ISO standards to be met.

### 2017-01-05 Plos-one-manuscript/latex/manuscript.tex
editing

@@
 {\Large
-\textbf\newline{3D-Printable Micropipette}
+\textbf\newline{Open Design 3D-Printable Adjustable Micropipette that meets ISO Standard for Accuracy}
 }
@@
 \section*{Abstract}
-Open source development of lab equipment is being facilitated, in part, by growing availability of 3D printing which allows the production of simple lab tools.
-We developed 3D-printable parts that, along with a disposable syringe, form a micropipette that requires no calibration or validation with a scale.
+Open source projects make use of 3D printing as an increasingly practical tool to share designs, fabricate parts, and decrease cost of production.
+Scientists
+We developed a micropipette that uses 3D-printable parts and some hardware to actuate a disposable syringe to a user adjustable limit.
+Graduations on the syringe are used to accurately adjust the set point to the desired volume.  
 Our open design printed micropipette is assessed in comparison to a commercial pipette and meets ISO 8655 standards.
@@
 Open source development also enables the development of custom solutions to meet unique applications not met by commercial products that are shared freely and are user modifiable\cite{Fullerton2014,Pearce2012,Rankin2014,Sulkin2013}.
-Some advanced, noteworthy, open-source scientific equipment include a PCR device\cite{ChaiBiotechnologiesInc2015}, and a two-photon microscope\cite{Rosenegger2014} although simple tools are often more impactful as they can serve a wider community.
+Some advanced, noteworthy, open-source scientific equipment include a PCR device\cite{ChaiBiotechnologiesInc2015}, and a two-photon microscope\cite{Rosenegger2014} although simple tools have potential to be impactful as they can serve a wider community.
 
-Some simple and clever printable parts that have emerged are ones that give a new function to a ubiquitous existing device, such as drill bit attachment designed to hold centrifuge tubes, allowing a drill to be used as a centrifuge\cite{Garvey2009}.
-Although this may make a rather crude centrifuge it may be an adequate solution which only costs pennies compared to commercially available centrifuges.
+Some simple and clever printable parts that have emerged are ones that give a new function to a ubiquitous existing device, such as drill bit attachment designed to hold centrifuge tubes, allowing a dremel to be used as a centrifuge\cite{Garvey2009}.
+Although this may make a rather crude centrifuge it may be an adequate solution for a fraction of the cost of a commercial centrifuge.
 Other examples of open-design research tools that utilize 3D printed parts include optics equipment\cite{Zhang2013}, microscopes\cite{Baden2014a,Walus2014}, syringe pumps\cite{Wijnen2014}, and reactionware\cite{Symes2012} to name a few.
@@
 One example of a everyday scientific tool that provides opportunity for an open design solution is the micropipette.
-A open design micropipette that can be made for cheap can cut costs and allow for more options for labs and educational settings.
+An open design micropipette that can be made cheaply can cut costs and allow for more options for labs and educational settings.
 Micropipettes are an indispensable tool used routinely in lab tasks and can easily cost \$1000 USD for a set.
@@
 Because there is no built in feature such as a readout for the user to set the displacement to a desired volume, this design requires the user to validate the volumes dispensed with a high precision scale.
-Without verification with a scale the volumes dispensed can only be estimated based on calculations of the deflection of the membrane.
+Without verification with a scale the volumes dispensed can only be estimated based on calculations of the deflection of the membrane which is not a practical protocol.
 
-We submit a new design whose major strength is the ability to adjust to any volume according to a built in scale.
-Our open design 3D-printable micropipette works by actuating a disposable syringe to a user adjustable set-point.
+We submit a new design whose major strength is the ability to adjust to any volume aided by the the built in scale.
+Our open design 3D-printable micropipette works by actuating a disposable syringe to a user adjustable set point.
 This allows the user to set the pipette to a volume by reading the graduations on the syringe barrel.
-The scale marks on the syringe can be used to adjust the dispensed volume accurately without calibrating with a scale.
-Our pipette also offers a simplified assembly requiring no glue, tape, or permanent connections.
+We have also designed an adjusted graduation scale, to be used in place of the printed on scale, that corrects for the compressibility of air which allows the pipette to be set accurately.
+Additionally our pipette offers a simplified assembly requiring no glue, tape, or permanent connections.
 

### 2017-01-05 Plos-one-manuscript/latex/manuscript.tex
editing

@@
 Although this may make a rather crude centrifuge it may be an adequate solution for a fraction of the cost of a commercial centrifuge.
-Other examples of open-design research tools that utilize 3D printed parts include optics equipment\cite{Zhang2013}, microscopes\cite{Baden2014a,Walus2014}, syringe pumps\cite{Wijnen2014}, and reactionware\cite{Symes2012} to name a few.
+Other examples of open-design research tools that utilize 3D printed parts include optics equipment\cite{Zhang2013}, microscopes\cite{Baden2014a,Walus2014}, syringe pumps\cite{Wijnen2014}, reactionware\cite{Symes2012} and the list continues to grow.
 
@@
 Our printed pipette is designed to actuate a 1 mL or 3 mL syringe to a user set displacement.
-The core of the design is two printed parts, the body and the plunger which are able to be printed on a consumer grade FDM printer (fig.~\ref{fig1}).
+The core of the design is two printed parts, the body and the plunger which are able to be printed on a consumer grade FDM printer (fig.~\ref{fig1}), in this case a Makerbot Replicator.
 A 1 mL or 3 mL syringe twists to lock in the body part and is held into place by the syringe flanges.

### 2017-01-06 Plos-one-manuscript/latex/manuscript.tex
working

@@
 One example of a everyday scientific tool that provides opportunity for an open design solution is the micropipette.
-An open design micropipette that can be made cheaply can cut costs and allow for more options for labs and educational settings.
+An open design micropipette that can be made cheaply affords more options for labs and educational settings.
 Micropipettes are an indispensable tool used routinely in lab tasks and can easily cost \$1000 USD for a set.
@@
 
-Our pipette uses the air-displacement design, where a pocket of air is used to draw liquid into the pipette.
+Our pipette uses the air-displacement method, where a vacuum is applied to a pocket of air to draw liquid into the pipette.
 As air is an compressible fluid, this pocket of air grows due to the weight of the liquid pulling on it.
@@
 Data was taken with commercial pipettes of 30-300 $\mu$L and 100-1000 $\mu$L to compare to the printed pipette.
-The systematic error and random error was calculated according to ISO 8655~\cite{ISO8655} (Table~\ref{table3} and \ref{table4}).
+Accuracy and precision are expressed as systematic error and random error, respectively, and are calculated according to ISO 8655~\cite{ISO8655} (Table~\ref{table3} and \ref{table4}).
+The systematic error, or accuracy, is calculated according to the following equations where accuracy ($A$) is the difference of the mean volume ($\bar{V}$) and the nominal volume ($V_{o}$):
+
+\begin{equation}\label{eq:accuracy} 
+A = \bar{V}-V_{o},
+A\% = 100\%  \times  A / V_{o}
+\end{equation}
+The precision or random error is the standard deviation ($s$) of the measurements and ($cv$) is the coefficient of variation:
+
+\begin{equation}\label{eq:precision} 
+s = \sqrt{\frac{\sum_{i=1}^{n}(V_{i}-\bar{V})^2}{n-1}},
+cv = 100\% \times s / \bar{V}
+\end{equation}
 
@@
 
+The performance of this pipette relies heavily on the syringe and its
+Luckliy as a regulated medical device the syringe is made to tight standards and 
+This design relies heavily on this specialized part for the core function as well as accuracy.
+As disposable syringes are a regulated medical device they must meet high standards.
+As good as the performance of our printed pipette is, a commercial pipette should be expected to be more reliable and preferred for critical procedures. 
+Adjusting the printed pipette to the desired volume requires more time and attention which would be tedious for procedures requiring many adjustments.
+On the other hand due to the \$6 cost to make the printed pipette would be ideal to assemble several and pre-set each for a planned transfer rather then re-adjusting one commercial pipette for each step.
+The printable pipette can also be used as a disposable, sparing the commercial micropipette, in situations were cross-contamination and re-sterilization is required, or damage from volatile reagents is a concern.
+The syringe of the printed pipette can be easily replaced with a fresh sterile one sparing the expensive commercial pipette.
+This pipette would also be ideal for high school and teaching labs or any resource limited program especially as part of a module about 3D printing.
+
 The open design nature of this project encourages anyone to use and submit changes to improve and add features to this design.
 All of the working files and documentation are kept in a public repository~\cite{BMLmicropipette}.
+Future directions for this project include developing a tip ejection system and additional configurations for transferring volumes below 30 uL as well as  increasing over all user friendliness, such as making the adjusting bolt easier to grip and improving ergonomics.
+
 % Please add the following required packages to your document preamble:

### 2017-01-10 Plos-one-manuscript/latex/manuscript.tex
second draft to dte

@@
 \section*{Abstract}
-Open source projects make use of 3D printing as an increasingly practical tool to share designs, fabricate parts, and decrease cost of production.
-Scientists
-We developed a micropipette that uses 3D-printable parts and some hardware to actuate a disposable syringe to a user adjustable limit.
+Scientific communities are drawn to the open source model as an increasingly utilitarian method to produce and share work.
+Initially used as a means to develop freely available software, open source projects have been applied to hardware including scientific tools.
+Increasing convenience of 3D printing has fueled the proliferation of open labware projects aiming to develop and share designs for scientific tools that can be produced in-house as cheap alternatives to commercial products.
+We present our design of a micropipette that is assembled from 3D-printable parts and some hardware that works by actuating a disposable syringe to a user adjustable limit.
 Graduations on the syringe are used to accurately adjust the set point to the desired volume.  
@@
 Open design 3D-printable lab equipment is an attractive idea because, like open source software, it allows free access to technology that is otherwise inaccessible due to proprietary and/or financial barriers.
-Open design tools create opportunity for scientists and educational programs in remote or resource limited areas to participate with inexpensive and easy to make tools\cite{Baden2015,Marzullo2012,Lang2011,Baker2014,Cybulski2014}.
-Open source development also enables the development of custom solutions to meet unique applications not met by commercial products that are shared freely and are user modifiable\cite{Fullerton2014,Pearce2012,Rankin2014,Sulkin2013}.
-Some advanced, noteworthy, open-source scientific equipment include a PCR device\cite{ChaiBiotechnologiesInc2015}, and a two-photon microscope\cite{Rosenegger2014} although simple tools have potential to be impactful as they can serve a wider community.
+Open design tools create opportunity for scientists and educational programs in remote or resource limited areas to participate with inexpensive and easy to make tools\cite{Marzullo2012,Lang2011,Fobel2013,Baker2014,Cybulski2014}.
+Open source development also enables the development of custom solutions to meet unique applications not met by commercial products that are shared freely and are user modifiable\cite{Fullerton2014,Pearce2012,Rankin2014,Sulkin2013,Dryden2015,DaCosta2014,Tek2008}.
+Some advanced, noteworthy, open source scientific equipment include a PCR device\cite{ChaiBiotechnologiesInc2015}, and a two-photon microscope\cite{Rosenegger2014} although simple tools have potential to be impactful as they can serve a wider community.
 
@@
 Although this may make a rather crude centrifuge it may be an adequate solution for a fraction of the cost of a commercial centrifuge.
-Other examples of open-design research tools that utilize 3D printed parts include optics equipment\cite{Zhang2013}, microscopes\cite{Baden2014a,Walus2014}, syringe pumps\cite{Wijnen2014}, reactionware\cite{Symes2012} and the list continues to grow.
+Other examples of open source research tools that utilize 3D printed parts include optics equipment\cite{Zhang2013}, microscopes\cite{Baden2014a,Walus2014}, syringe pumps\cite{Wijnen2014}, reactionware\cite{Symes2012,Kitson2012,Mathieson2013,Kitson2014}, microfluidics\cite{Brennan2015,Dragone2013} and the list continues to grow\cite{PlosCollections}.
 
@@
 	\caption{
-		{\bf CAD renderings of assembled pipette and function.} The pipetted actuates the syringe to three positions.
-{\bf(i) The set position.} The position of the screw determines the total displacement.
+		{\bf CAD renderings of assembled pipette and function.} The pipette actuates the syringe to three positions.
+{\bf (A) The latched position.} When the plunger is pressed the pipette locks at this position.
+The tip is then placed in a liquid and the unlatching button is pressed to release the pipette back to the set position (B), drawing in liquid.
+{\bf(B) The set position.} The position of the screw determines the total displacement that the plunger moves.
 The pipette is spring loaded to return to this position.
-{\bf (ii) The latched position.} When the plunger is pressed the pipette locks at this position.
-The tip is then placed in a liquid and the unlatching button is pressed to release the pipette back to the set position, drawing in liquid.
-{\bf (iii) The blow-out position.} The fluid is transferred by pressing the plunger past the latched position to blow-out all the liquid.
+{\bf (C) The blow-out position.} The fluid is transferred by pressing the plunger past the latched position to blow-out all the liquid.
+{\bf (D) Return to the latched position.} The pipette returns to the latched position ready to preform another transfer.
 	}
@@
 Our solution was to replace the built-in scale with a scale that accounted for the expansion.
-Using the data from our initial testing we calculated a factor for the expansion and used that to make the new scale.
+Using the data from our initial testing we calculated a factor for the expansion and used that to make the new scale (\nameref{S1_Fig} and \nameref{S1_Fig}.)
 With the new scale taped on the syringe our validation testing met the ISO 8655 standard.
@@
 Our printed pipette with the adjusted scale meets ISO standards for accuracy and precision. (Table \ref{table3} and \ref{table4}).
-
-Our printed pipette improves on existing open design pipettes in several ways. 
-Most significantly the user is able to adjust the syringe accurately without verifying the volume with a scale.
-The pipette can be adjusted to any discrete volume within range.
-In addition, the assembly requires no permanent connections using tape or glue which allows for re-configuration and easy replacement of parts.
-Conveniently, our design can also reach to the bottom of a 15 mL conical tube allowing tasks such as aspirating supernatant fluid from a cell pellet.
-Unlike existing designs our design does not use a membrane that may wear out and require tedious replacement.
-The only major limitation of this design compared to the biropipette is the option for a pipette tip ejector.
-The biropipette also uses arguably easier to source parts (a pen VS a syringe) relative to what is required from our design.
-The biropipette also was developed in OpenSCAD which is free and open source CAD software where our design was created in Solidworks a proprietary software.
-
-The performance of this pipette relies heavily on the syringe and its
-Luckliy as a regulated medical device the syringe is made to tight standards and 
-This design relies heavily on this specialized part for the core function as well as accuracy.
-As disposable syringes are a regulated medical device they must meet high standards.
-As good as the performance of our printed pipette is, a commercial pipette should be expected to be more reliable and preferred for critical procedures. 
-Adjusting the printed pipette to the desired volume requires more time and attention which would be tedious for procedures requiring many adjustments.
-On the other hand due to the \$6 cost to make the printed pipette would be ideal to assemble several and pre-set each for a planned transfer rather then re-adjusting one commercial pipette for each step.
-The printable pipette can also be used as a disposable, sparing the commercial micropipette, in situations were cross-contamination and re-sterilization is required, or damage from volatile reagents is a concern.
-The syringe of the printed pipette can be easily replaced with a fresh sterile one sparing the expensive commercial pipette.
-This pipette would also be ideal for high school and teaching labs or any resource limited program especially as part of a module about 3D printing.
-
-The open design nature of this project encourages anyone to use and submit changes to improve and add features to this design.
-All of the working files and documentation are kept in a public repository~\cite{BMLmicropipette}.
-Future directions for this project include developing a tip ejection system and additional configurations for transferring volumes below 30 uL as well as  increasing over all user friendliness, such as making the adjusting bolt easier to grip and improving ergonomics.
 
@@
 
+Our printed pipette improves on existing open design pipettes in several ways. 
+Most significantly the user is able to adjust the syringe accurately without verifying the volume with a scale.
+The pipette can be adjusted to any discrete volume within range.
+In addition, the assembly requires no permanent connections using tape or glue which allows for re-configuration and easy replacement of parts.
+Conveniently, our design can also reach to the bottom of a 15 mL conical tube allowing tasks such as aspirating supernatant fluid from a cell pellet.
+Unlike existing designs our design does not use a membrane that may wear out and require tedious replacement.
+The only major limitation of this design compared to the biropipette is the option for a pipette tip ejector.
+The biropipette also uses arguably easier to source parts (a pen VS a syringe) relative to what is required from our design.
+The biropipette also was developed in OpenSCAD which is free and open source CAD software where our design was created in Solidworks a proprietary software.
+
+This design relies heavily on the syringe, a specialized part, for the core function as well as accuracy.
+Fortunately, as disposable syringes are a regulated medical device they must meet high standards making them a reliable part for this design.
+As good as the performance of our printed pipette is, a commercial pipette should be expected to be more reliable and preferred for critical procedures. 
+Adjusting our printed pipette to the desired volume requires more time and attention which would be tedious for procedures requiring many adjustments.
+On the other hand, due to the \$6 cost to make, many printed pipettes could be assembled and pre-set, each for a planned transfer, rather then re-adjusting one commercial pipette for each step.
+The printable pipette can also be used as a disposable, sparing the commercial micropipette, in situations were cross-contamination and resterilization is required, or damage from volatile reagents is a concern.
+This pipette would also be ideal for high school and teaching labs or any resource limited program especially as part of a module about 3D printing.
+
+The open design nature of this project encourages anyone to use and submit changes to improve and add features to this design.
+All of the working files and documentation are kept in a public repository~\cite{BMLmicropipette}.
+Future directions for this project include developing a tip ejection system and additional configurations for transferring volumes below 30 uL as well as increasing over all user friendliness, such as making the adjusting bolt easier to grip and improving ergonomics.
+
 \section*{Conclusion}
@@
 Our design is free to use and modify to encourage further collaborative development.
-
-%For more information, see \nameref{S1_Text}.
 
@@
 
+\subsection*{S1 Video}
+\label{S1_Video}
+{\bf Video showing assembly and demonstration of operation.} Assembly of the pipette in the 100-1000 $\mu$L and 30-300 $\mu$L configuration is preformed. https://www.youtube.com/watch?v=D8y5WUYpcW0
+
 \nolinenumbers

### 2017-01-13 Plos-one-manuscript/latex/manuscript.tex
started nature comm manuscript

@@
 Conveniently, our design can also reach to the bottom of a 15 mL conical tube allowing tasks such as aspirating supernatant fluid from a cell pellet.
-Unlike existing designs our design does not use a membrane that may wear out and require tedious replacement.
+Unlike existing designs our design does not use a membrane that may wear out and require replacement.
 The only major limitation of this design compared to the biropipette is the option for a pipette tip ejector.
@@
 
-This design relies heavily on the syringe, a specialized part, for the core function as well as accuracy.
+Our design relies heavily on the syringe, a specialized part, for the core function as well as accuracy.
 Fortunately, as disposable syringes are a regulated medical device they must meet high standards making them a reliable part for this design.
@@
 The printable pipette can also be used as a disposable, sparing the commercial micropipette, in situations were cross-contamination and resterilization is required, or damage from volatile reagents is a concern.
-This pipette would also be ideal for high school and teaching labs or any resource limited program especially as part of a module about 3D printing.
+This pipette would also be ideal for high school and teaching labs or any resource limited program.
 

### 2017-01-13 nature-comm-manuscript/manuscript.tex
started nature comm manuscript

--- 2017-01-10 Plos-one-manuscript/latex/manuscript.tex
@@
-	% Template for PLoS
-% Version 3.1 February 2015
-%
-% To compile to pdf, run:
-% latex plos.template
-% bibtex plos.template
-% latex plos.template
-% latex plos.template
-% dvipdf plos.template
-%
-% % % % % % % % % % % % % % % % % % % % % %
-%
-% -- IMPORTANT NOTE
-%
-% This template contains comments intended 
-% to minimize problems and delays during our production 
-% process. Please follow the template instructions
-% whenever possible.
-%
-% % % % % % % % % % % % % % % % % % % % % % % 
-%
-% Once your paper is accepted for publication, 
-% PLEASE REMOVE ALL TRACKED CHANGES in this file and leave only
-% the final text of your manuscript.
-%
-% There are no restrictions on package use within the LaTeX files except that 
-% no packages listed in the template may be deleted.
-%
-% Please do not include colors or graphics in the text.
-%
-% Please do not create a heading level below \subsection. For 3rd level headings, use \paragraph{}.
-%
-% % % % % % % % % % % % % % % % % % % % % % %
-%
-% -- FIGURES AND TABLES
-%
-% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
-%
-% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
-% - Figures should be uploaded separately from your manuscript file. 
-% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
-% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
-% For figure citations, please use "Fig." instead of "Figure".
-% See http://www.plosone.org/static/figureGuidelines for PLOS figure guidelines.
-%
-% Tables should be cell-based and may not contain:
-% - tabs/spacing/line breaks within cells to alter layout or alignment
-% - vertically-merged cells (no tabular environments within tabular environments, do not use \multirow)
-% - colors, shading, or graphic objects
-% See http://www.plosone.org/static/figureGuidelines#tables for table guidelines.
-%
-% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
-%
-% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
-%
-% IMPORTANT
-% Below are a few tips to help format your equations and other special characters according to our specifications.
-For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://www.plosone.org/static/latexGuidelines
-%
-% Please be sure to include all portions of an equation in the math environment.
-%
-% Do not include text that is not math in the math environment. For example, CO2 will be CO\textsubscript{2}.
-%
-% Please add line breaks to long display equations when possible in order to fit size of the column. 
-%
-% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
-%
-% % % % % % % % % % % % % % % % % % % % % % % % 
-%
-% Please contact latex@plos.org with any questions.
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
+%% Template for a preprint Letter or Article for submission
+%% to the journal Nature.
+%% Written by Peter Czoschke, 26 February 2004
+%%
 
-\documentclass[10pt,letterpaper]{article}
-\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
+\documentclass{nature}
 
-% Use adjustwidth environment to exceed column width (see example table in text)
 \usepackage{changepage}
+%% make sure you have the nature.cls and naturemag.bst files where
+%% LaTeX can find them
 
-% Use Unicode characters when possible
-\usepackage[utf8]{inputenc}
+\bibliographystyle{naturemag}
 
-% textcomp package and marvosym package for additional characters
-\usepackage{textcomp,marvosym}
+\title{Open Design 3D-Printable Adjustable Micropipette that meets ISO Standard for Accuracy.}
 
-% fixltx2e package for \textsubscript
-\usepackage{fixltx2e}
+%% Notice placement of commas and superscripts and use of &
+%% in the author list
 
-% amsmath and amssymb packages, useful for mathematical formulas and symbols
-\usepackage{amsmath,amssymb}
-
-% cite package, to clean up citations in the main text. Do not remove.
-\usepackage{cite}
-
-% Use nameref to cite supporting information files (see Supporting Information section for more info)
-\usepackage{nameref,hyperref}
-
-% line numbers
-\usepackage[right]{lineno}
-
-% ligatures disabled
-\usepackage{microtype}
-\DisableLigatures[f]{encoding = *, family = * }
-
-% rotating package for sideways tables
-\usepackage{rotating}
-
-\usepackage{multirow}
-
-% Remove comment for double spacing
-%\usepackage{setspace} 
-%\doublespacing
-
-% Text layout
-\raggedright
-\setlength{\parindent}{0.5cm}
-\textwidth 5.25in 
-\textheight 8.75in
-
-% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
-% Captions will be left justified
-\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
-
-% Use the PLoS provided BiBTeX style
-\bibliographystyle{plos2015}
-
-% Remove brackets from numbering in List of References
-\makeatletter
-\renewcommand{\@biblabel}[1]{\quad#1.}
-\makeatother
-
-% Leave date blank
-\date{}
-
-% Header and Footer with logo
-\usepackage{lastpage,fancyhdr,graphicx}
-\usepackage{epstopdf}
-\pagestyle{myheadings}
-\pagestyle{fancy}
-\fancyhf{}
-\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
-\rfoot{\thepage/\pageref{LastPage}}
-\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
-\fancyheadoffset[L]{2.25in}
-\fancyfootoffset[L]{2.25in}
-\lfoot{\sf PLOS}
-
-%% Include all macros below
-
-\newcommand{\lorem}{{\bf LOREM}}
-\newcommand{\ipsum}{{\bf IPSUM}}
-
-%% END MACROS SECTION
+\author{Martin D. Brennan$^1$, Fahad F. Bokhari$^1$ \& David T. Eddington$^1$}
 
 \begin{document}
-\vspace*{0.35in}
 
-% Title must be 250 characters or less.
-% Please capitalize all terms in the title except conjunctions, prepositions, and articles.
-\begin{flushleft}
-{\Large
-\textbf\newline{Open Design 3D-Printable Adjustable Micropipette that meets ISO Standard for Accuracy}
-}
-\newline
-% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
-\\
-Martin D. Brennan\textsuperscript{1},
-Fahad F. Bokhari\textsuperscript{1},
-David T. Eddington\textsuperscript{1,*},
-%Name4 Surname\textsuperscript{2,\ddag},
-%Name5 Surname\textsuperscript{2,\ddag},
-%Name6 Surname\textsuperscript{2},
-%Name7 Surname\textsuperscript{3,*},
-%with the Lorem Ipsum Consortium\textsuperscript{\textpilcrow}
-\\
-\bigskip
-\bf{1} Department of Bioengineering, University of Illinois at Chicago, Chicago, Illinois, USA
-%\\
-%\bf{2} Affiliation Dept/Program/Center, Institution Name, City, State, Country
-%\\
-%\bf{3} Affiliation Dept/Program/Center, Institution Name, City, State, Country
-%\\
-\bigskip
+\maketitle
 
-% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
-% 
-% Remove or comment out the author notes below if they aren't used.
-%
-% Primary Equal Contribution Note
-%\Yinyang These authors contributed equally to this work.
+\begin{affiliations}
+ \item Department of Bioengineering, University of Illinois at Chicago, Chicago, Illinois, USA
+\end{affiliations}
 
-% Additional Equal Contribution Note
-% Also use this double-dagger symbol for special authorship notes, such as senior authorship.
-%\ddag These authors also contributed equally to this work.
-
-% Current address notes
-%\textcurrency a Insert current address of first author with an address update
-% \textcurrency b Insert current address of second author with an address update
-% \textcurrency c Insert current address of third author with an address update
-
-% Deceased author note
-%\dag Deceased
-
-% Group/Consortium Author Note
-%\textpilcrow Membership list can be found in the Acknowledgments section.
-
-% Use the asterisk to denote corresponding authorship and provide email address in note below.
-* dte@uic.edu
-
-\end{flushleft}
-% Please keep the abstract below 300 words
-\section*{Abstract}
+\begin{abstract}
 Scientific communities are drawn to the open source model as an increasingly utilitarian method to produce and share work.
@@
 Graduations on the syringe are used to accurately adjust the set point to the desired volume.  
-Our open design printed micropipette is assessed in comparison to a commercial pipette and meets ISO 8655 standards.
-
-\linenumbers
+Our open design printed micropipette is assessed in comparison to a commercial pipette and meets ISO 8655 standards. (Add refs)
+\end{abstract}
 
@@
 
-We submit a new design whose major strength is the ability to adjust to any volume aided by the the built in scale.
+We submit a new design whose major strength is the ability to adjust to any volume aided by the the built in scale
 Our open design 3D-printable micropipette works by actuating a disposable syringe to a user adjustable set point.
@@
 Additionally our pipette offers a simplified assembly requiring no glue, tape, or permanent connections.
-
-\section*{Methods}
-Our printed pipette is designed to actuate a 1 mL or 3 mL syringe to a user set displacement.
-The core of the design is two printed parts, the body and the plunger which are able to be printed on a consumer grade FDM printer (fig.~\ref{fig1}), in this case a Makerbot Replicator.
-A 1 mL or 3 mL syringe twists to lock in the body part and is held into place by the syringe flanges.
-The 30-300 $\mu$L configuration uses a 1 mL pipette and the 100-1000 $\mu$L configuration uses a 3 mL pipette.
-The plunger part slides freely in the body part and actuates the syringe by pushing the thumb button (fig.~\ref{fig2}). 
-The pipette is spring loaded towards a set point which is adjustable by a set-screw.
-When the thumb button is pressed the system locks when it reaches the latched position, where it is ready to draw in fluid.
-The plunger is held in place with a latching button design which is released with the unlatching button drawing in fluid.
-The displacement is equal to the distance between the set position and the latched position.
-The pipette can also be pressed past the latched position to `blow-out' the transferred fluid completely from the pipette tip.   
-Additional materials required for assembly include two springs, a nut, a bolt and two washers.
-Attempts to make a printable luer lock adapter for tips was abandoned as the surface of printed parts is too rough to make an air tight seal with the luer or pipette tip.
-Instead, a combination of a barbed luer adapter and elastic tubing is used to attach the pipette tips.
-Our printed pipette mimics commercial pipettes design, function, and user operation, making it intuitive to use.
 
@@
 
-Our pipette uses the air-displacement method, where a vacuum is applied to a pocket of air to draw liquid into the pipette.
-As air is an compressible fluid, this pocket of air grows due to the weight of the liquid pulling on it.
-Due to this effect the graduations on the syringe are not accurate, as they are designed for measuring liquid within the syringe.
-At larger volumes this effect is more pronounced resulting in the volume measured being greater than the amount of liquid pulled into the syringe.
-We remedied this by creating a new scale to account for the expansion.
-The scale is printed on a transparency sheet and is taped onto the syringe for accurate measurements (See~\nameref{S1_Fig} and \nameref{S2_Fig}).
-
-\subsection*{Fabrication \& Assembly}
-Two parts are printed (body.stl and plunger.stl) at normal resolution with rafts on a Makerbot Replicator.
-A small amount of paraffin wax is applied to the screw to prevent slop from causing the set point to drift after each actuation.
-The nut is sunk into the hex inset in the printed body part.
-The bolt is threaded in from the top of the body into the nut.
-Springs and washers are threaded onto the plunger of a 1 mL syringe for the 30-300 $\mu$L configuration.
-Springs are placed inside a 3 mL syringe for the 100-1000 $\mu$L configuration.
-The plunger part is inserted in the body and the syringe assembly is pushed in and locked from the syringe flanges to the body part to complete assembly(fig.~\ref{fig3}).
-Parts and cost are listed in Table~\ref{table1} and \ref{table2}.
-
 \begin{figure}
@@
 \end{figure}
-
-\begin{table}[!ht]
-\centering
-\caption{Parts and cost for the 30-300 $\mu$L pipette.}
-\label{table1}
-\begin{tabular}{|l|l|l|l|}
-	\hline
-	Part         & Unit Price & Source         & Part number \\ \hline
-	Filament     & \$1.63     & Makerbot       & NA          \\ \hline
-	1 mL Syringe & \$0.15     & BD Biosciences & 309628      \\ \hline
-	Bolt         & \$0.12     & McMaster-Carr  & 91287A026   \\ \hline
-	Nut          & \$0.01     & McMaster-Carr  & 90591A121   \\ \hline
-	Spring (2)   & \$4.14     & McMaster-Carr  & 94125K542   \\ \hline
-	Washers (2)  & \$0.16     & McMaster-Carr  & 90107A012   \\ \hline
-	total        & \$6.21     &                &             \\ \hline
-\end{tabular}
-\end{table}
-
-\begin{table}[!ht]
-\centering
-\caption{Parts and cost for the 100-1000 $\mu$L pipette.}
-\label{table2}
-\begin{tabular}{|l|l|l|l|}
-	\hline
-	Part         & Unit Price & Source         & Part number \\ \hline
-	Filament     & \$1.63     & Makerbot       & NA          \\ \hline
-	3 mL Syringe & \$0.73     & BD Biosciences & 309657      \\ \hline
-	Bolt         & \$0.12     & McMaster-Carr  & 91287A026   \\ \hline
-	Nut          & \$0.01     & McMaster-Carr  & 90591A121   \\ \hline
-	Spring (2)   & \$4.14     & McMaster-Carr  & 94125K542   \\ \hline
-	total        & \$6.63     &                &             \\ \hline
-\end{tabular}
-\end{table}
-
-\subsection*{Validation}
-The printed pipette’s accuracy and precision was characterized and compared to a commercial pipette as well as ISO 8655.
-The printed pipette was adjusted to the target volume by eye from the syringe graduations.
-Deionized water was transferred and measured with a scale.
-Five transfers were recorded and averaged to account for random variability.
-Data was taken for printed pipettes with existing syringe graduations as well as with the our adjusted scale.
-Data was taken with commercial pipettes of 30-300 $\mu$L and 100-1000 $\mu$L to compare to the printed pipette.
-Accuracy and precision are expressed as systematic error and random error, respectively, and are calculated according to ISO 8655~\cite{ISO8655} (Table~\ref{table3} and \ref{table4}).
-The systematic error, or accuracy, is calculated according to the following equations where accuracy ($A$) is the difference of the mean volume ($\bar{V}$) and the nominal volume ($V_{o}$):
-
-\begin{equation}\label{eq:accuracy} 
-A = \bar{V}-V_{o},
-A\% = 100\%  \times  A / V_{o}
-\end{equation}
-The precision or random error is the standard deviation ($s$) of the measurements and ($cv$) is the coefficient of variation:
-
-\begin{equation}\label{eq:precision} 
-s = \sqrt{\frac{\sum_{i=1}^{n}(V_{i}-\bar{V})^2}{n-1}},
-cv = 100\% \times s / \bar{V}
-\end{equation}
 
@@
 Our solution was to replace the built-in scale with a scale that accounted for the expansion.
-Using the data from our initial testing we calculated a factor for the expansion and used that to make the new scale (\nameref{S1_Fig} and \nameref{S1_Fig}.)
+Using the data from our initial testing we calculated a factor for the expansion and used that to make the new scale (\ref{S1_Fig} and \ref{S1_Fig}.)
 With the new scale taped on the syringe our validation testing met the ISO 8655 standard.
@@
 Our printed pipette with the adjusted scale meets ISO standards for accuracy and precision. (Table \ref{table3} and \ref{table4}).
-
-% Please add the following required packages to your document preamble:
-% \usepackage{multirow}
-\begin{table}[!ht]
-	\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
-		\centering
-		\caption{ISO 8655 for 100-1000 $\mu$L comparing a commercial pipette with our printed pipette used with existing 3 mL syringe scale and an adjusted scale}
-		\label{table3}
-		\begin{tabular}{lllllll}
-			&                       & Mean   & Systematic Error & \% Sys. err. & Random Error & \% Rand. err. \\
-			1000 $\mu$L & ISO 8655, 100-1000 $\mu$L & 1000    & 8.00             & 0.80         & 3.00         & 0.30          \\
-			& Commercial Pipette    & 1002.98 & 2.98             & 0.30         & 1.72         & 0.17          \\
-			& Printed Pipette       & 949.29  & -50.71           & -5.07        & 0.60         & 0.06          \\
-			& Printed Pipette Scale & 1003.57 & 3.57             & 0.36         & 0.89         & 0.09          \\
-			&                       &         &                  &              &              &               \\
-			500 $\mu$L  & ISO 8655, 100-1000 $\mu$L & 500     & 8.00             & 1.60         & 3.00         & 0.60          \\
-			& Commercial Pipette    & 503.67  & 3.67             & 0.73         & 0.49         & 0.10          \\
-			& Printed Pipette       & 475.99  & -24.01           & -4.80        & 4.75         & 1.00          \\
-			& Printed Pipette Scale & 503.62  & 3.62             & 0.72         & 1.64         & 0.33          \\
-			&                       &         &                  &              &              &               \\
-			200 $\mu$L  & ISO 8655, 100-1000 $\mu$L & 200     & 8.00             & 4.00         & 3.00         & 1.50          \\
-			& Commercial Pipette    & 204.61  & 4.61             & 2.30         & 0.15         & 0.07          \\
-			& Printed Pipette       & 186.55  & -13.45           & -6.72        & 1.31         & 0.70          \\
-			& Printed Pipette Scale & 201.87  & 1.87             & 0.94         & 1.47         & 0.73          \\
-			&                       &         &                  &              &              &               \\
-			100 $\mu$L  & ISO 8655, 100-1000 $\mu$L & 100     & 8.00             & 8.00         & 3.00         & 3.00          \\
-			& Commercial Pipette    & 104.29  & 4.29             & 4.29         & 1.65         & 1.58          \\
-			& Printed Pipette       & 94.02   & -5.98            & -5.98        & 4.81         & 5.12          \\
-			& Printed Pipette Scale & 101.00  & 1.00             & 1.00         & 1.05         & 1.04         
-		\end{tabular}
-		%\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl.
-Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
-		%\end{flushleft}
-	\end{adjustwidth}
-\end{table}
-
-\begin{table}[!ht]
-	\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
-		\centering
-		\caption{ISO 8655 for 30-300 $\mu$L comparing a commercial pipette with our printed pipette used with existing 3 mL syringe scale and an adjusted scale}
-		\label{table4}
-		\begin{tabular}{lllllll}
-			&                       & Mean   & Systematic Error & \% Sys. err. & Random Error & \% Rand. err. \\
-			300 $\mu$L & ISO 8655, 30-300 $\mu$L   & 300    & 4.00             & 1.33         & 1.50         & 0.50          \\
-			& Commercial Pipette    & 301.19 & 1.19             & 0.40         & 0.53         & 0.18          \\
-			& Printed Pipette       & 286.91 & -13.09           & -4.36        & 0.42         & 0.15          \\
-			& Printed Pipette Scale & 299.11 & -0.89            & -0.30        & 0.48         & 0.16          \\
-			&                       &        &                  &              &              &               \\
-			200 $\mu$L & ISO 8655, 30-300 $\mu$L   & 200    & 4                & 2            & 1.5          & 0.75          \\
-			& Commercial Pipette    & 200.06 & 0.06             & 0.03         & 0.46         & 0.23          \\
-			& Printed Pipette       & 193.40 & -6.60            & -3.30        & 2.86         & 1.48          \\
-			& Printed Pipette Scale & 200.57 & 0.57             & 0.28         & 0.86         & 0.43          \\
-			&                       &        &                  &              &              &               \\
-			50 $\mu$L  & ISO 8655, 30-300 $\mu$L   & 50     & 4                & 8            & 1.5          & 3             \\
-			& Commercial Pipette    & 49.02  & -0.98            & -1.96        & 0.10         & 0.20          \\
-			& Printed Pipette       & 49.62  & -0.38            & -0.76        & 1.26         & 2.53          \\
-			& Printed Pipette Scale & 48.73  & -1.27            & -2.54        & 1.11         & 2.27          \\
-			&                       &        &                  &              &              &               \\
-			30 $\mu$L  & ISO 8655, 30-300 $\mu$L   & 30     & 4                & 13.3         & 1.5          & 5             \\
-			& Commercial Pipette    & 29.08  & -0.92            & -3.06        & 0.09         & 0.31          \\
-			& Printed Pipette       & 29.22  & -0.78            & -2.59        & 0.31         & 1.07          \\
-			& Printed Pipette Scale & 27.78  & -2.22            & -7.41        & 1.37         & 4.93          \\
-			&                       &        &                  &              &              &               \\
-			20 $\mu$L* & ISO 8655, 30-300 $\mu$L   & 20     & 4                & 20           & 1.5          & 7.5           \\
-			& Commercial Pipette    & NA     & NA               & NA           & NA           & NA            \\
-			& Printed Pipette       & 18.70  & -1.30            & -6.48        & 0.38         & 2.01          \\
-			& Printed Pipette Scale & 17.94  & -2.06            & -10.29       & 1.87         & 10.42         \\
-			&                       &        &                  &              &              &               \\
-			10 $\mu$L* & ISO 8655, 30-300 $\mu$L   & 10     & 4                & 40           & 1.5          & 15            \\
-			& Commercial Pipette    & NA     & NA               & NA           & NA           & NA            \\
-			& Printed Pipette       & 11.95  & 1.95             & 19.52        & 0.73         & 6.08          \\
-			& Printed Pipette Scale & 7.64   & -2.36            & -23.64       & 0.38         & 4.92         
-		\end{tabular}
-		\begin{flushleft} * The 20 $\mu$L and 10 $\mu$L volumes are out of the range in this case but we wanted to demonstrate that the pipette is capable of even smaller volumes.
-		\end{flushleft}
-	\end{adjustwidth}
-\end{table}
 
@@
 
-\section*{Supporting Information}
+\begin{figure}
+%%%\includegraphics{something} % this command will be ignored
+\caption{Each figure legend should begin with a brief title for
+the whole figure and continue with a short description of each
+panel and the symbols used. For contributions with methods
+sections, legends should not contain any details of methods, or
+exceed 100 words (fewer than 500 words in total for the whole
+paper). In contributions without methods sections, legends should
+be fewer than 300 words (800 words or fewer in total for the whole
+paper).}
+\end{figure}
 
-\subsection*{S1 Fig}
-\label{S1_Fig}
-{\bf Adjusted Scale Graduations for 30-300 $\mu$L Pipette.} New scale graduations that can be printed on a transparency sheet and taped onto a 1 mL syringe.
-Using these graduations will correct for expansion of air and allow ISO standards to be met.
-PDF format for ease of printing to scale.
-1 inch and 1 cm marks to check scale as well as reproduction of standard graduation marks.
+\section*{Another Section}
 
-\subsection*{S2 Fig}
-\label{S2_Fig}
-{\bf Adjusted Scale Graduations for 100-1000 $\mu$L Pipette.} New scale graduations that can be printed on a transparency sheet and taped onto a 3 mL syringe.
-Using these graduations will correct for expansion of air and allow ISO standards to be met.
-PDF format for ease of printing to scale.
-1 inch and 1 cm marks to check scale as well as reproduction of standard graduation marks.
+Sections can only be used in Articles.  Contributions should be
+organized in the sequence: title, text, methods, references,
+Supplementary Information line (if any), acknowledgements,
+interest declaration, corresponding author line, tables, figure
+legends.
 
-\subsection*{S1 Video}
-\label{S1_Video}
-{\bf Video showing assembly and demonstration of operation.} Assembly of the pipette in the 100-1000 $\mu$L and 30-300 $\mu$L configuration is preformed. https://www.youtube.com/watch?v=D8y5WUYpcW0
+Spelling must be British English (Oxford English Dictionary)
 
-\nolinenumbers
+In addition, a cover letter needs to be written with the
+following:
+\begin{enumerate}
+ \item A 100 word or less summary indicating on scientific grounds
+why the paper should be considered for a wide-ranging journal like
+\textsl{Nature} instead of a more narrowly focussed journal.
+ \item A 100 word or less summary aimed at a non-scientific audience,
+written at the level of a national newspaper.  It may be used for
+\textsl{Nature}'s press release or other general publicity.
+ \item The cover letter should state clearly what is included as the
+submission, including number of figures, supporting manuscripts
+and any Supplementary Information (specifying number of items and
+format).
+ \item The cover letter should also state the number of
+words of text in the paper; the number of figures and parts of
+figures (for example, 4 figures, comprising 16 separate panels in
+total); a rough estimate of the desired final size of figures in
+terms of number of pages; and a full current postal address,
+telephone and fax numbers, and current e-mail address.
+\end{enumerate}
 
-\bibliographystyle{plos2015.bst}
-\bibliography{references}
+See \textsl{Nature}'s website
+(\texttt{http://www.nature.com/nature/submit/gta/index.html}) for
+complete submission guidelines.
+
+\begin{methods}
+Our printed pipette is designed to actuate a 1 mL or 3 mL syringe to a user set displacement.
+The core of the design is two printed parts, the body and the plunger which are able to be printed on a consumer grade FDM printer (fig.~\ref{fig1}), in this case a Makerbot Replicator.
+A 1 mL or 3 mL syringe twists to lock in the body part and is held into place by the syringe flanges.
+The 30-300 $\mu$L configuration uses a 1 mL pipette and the 100-1000 $\mu$L configuration uses a 3 mL pipette.
+The plunger part slides freely in the body part and actuates the syringe by pushing the thumb button (fig.~\ref{fig2}). 
+The pipette is spring loaded towards a set point which is adjustable by a set-screw.
+When the thumb button is pressed the system locks when it reaches the latched position, where it is ready to draw in fluid.
+The plunger is held in place with a latching button design which is released with the unlatching button drawing in fluid.
+The displacement is equal to the distance between the set position and the latched position.
+The pipette can also be pressed past the latched position to `blow-out' the transferred fluid completely from the pipette tip.   
+Additional materials required for assembly include two springs, a nut, a bolt and two washers.
+Attempts to make a printable luer lock adapter for tips was abandoned as the surface of printed parts is too rough to make an air tight seal with the luer or pipette tip.
+Instead, a combination of a barbed luer adapter and elastic tubing is used to attach the pipette tips.
+Our printed pipette mimics commercial pipettes design, function, and user operation, making it intuitive to use.
+
+Our pipette uses the air-displacement method, where a vacuum is applied to a pocket of air to draw liquid into the pipette.
+As air is an compressible fluid, this pocket of air grows due to the weight of the liquid pulling on it.
+Due to this effect the graduations on the syringe are not accurate, as they are designed for measuring liquid within the syringe.
+At larger volumes this effect is more pronounced resulting in the volume measured being greater than the amount of liquid pulled into the syringe.
+We remedied this by creating a new scale to account for the expansion.
+The scale is printed on a transparency sheet and is taped onto the syringe for accurate measurements (See~\ref{S1_Fig} and \ref{S2_Fig}).
+
+\subsection{Fabrication \& Assembly}
+Two parts are printed (body.stl and plunger.stl) at normal resolution with rafts on a Makerbot Replicator.
+A small amount of paraffin wax is applied to the screw to prevent slop from causing the set point to drift after each actuation.
+The nut is sunk into the hex inset in the printed body part.
+The bolt is threaded in from the top of the body into the nut.
+Springs and washers are threaded onto the plunger of a 1 mL syringe for the 30-300 $\mu$L configuration.
+Springs are placed inside a 3 mL syringe for the 100-1000 $\mu$L configuration.
+The plunger part is inserted in the body and the syringe assembly is pushed in and locked from the syringe flanges to the body part to complete assembly(fig.~\ref{fig3}).
+Parts and cost are listed in Table~\ref{table1} and \ref{table2}.
+
+\subsection{Validation}
+The printed pipette’s accuracy and precision was characterized and compared to a commercial pipette as well as ISO 8655.
+The printed pipette was adjusted to the target volume by eye from the syringe graduations.
+Deionized water was transferred and measured with a scale.
+Five transfers were recorded and averaged to account for random variability.
+Data was taken for printed pipettes with existing syringe graduations as well as with the our adjusted scale.
+Data was taken with commercial pipettes of 30-300 $\mu$L and 100-1000 $\mu$L to compare to the printed pipette.
+Accuracy and precision are expressed as systematic error and random error, respectively, and are calculated according to ISO 8655~\cite{ISO8655} (Table~\ref{table3} and \ref{table4}).
+The systematic error, or accuracy, is calculated according to the following equations where accuracy ($A$) is the difference of the mean volume ($\bar{V}$) and the nominal volume ($V_{o}$):
+
+\begin{equation}\label{eq:accuracy} 
+A = \bar{V}-V_{o},
+A\% = 100\%  \times  A / V_{o}
+\end{equation}
+The precision or random error is the standard deviation ($s$) of the measurements and ($cv$) is the coefficient of variation:
+
+\begin{equation}\label{eq:precision} 
+s = \sqrt{\frac{\sum_{i=1}^{n}(V_{i}-\bar{V})^2}{n-1}},
+cv = 100\% \times s / \bar{V}
+\end{equation}
+
+\end{methods}
+
+%% Put the bibliography here, most people will use BiBTeX in
+%% which case the environment below should be replaced with
+%% the \bibliography{} command.
+
+% \begin{thebibliography}{1}
+% \bibitem{dummy} Articles are restricted to 50 references, Letters
+% to 30.
+% \bibitem{dummyb} No compound references -- only one source per
+% reference.
+% \end{thebibliography}
+
+\bibliographystyle{naturemag}
+\bibliography{sample}
+
+%% Here is the endmatter stuff: Supplementary Info, etc.
+%% Use \item's to separate, default label is "Acknowledgements"
+
+\begin{addendum}
+ \item Put acknowledgements here.
+ \item[Competing Interests] The authors declare that they have no
+competing financial interests.
+ \item[Correspondence] Correspondence and requests for materials
+should be addressed to A.B.C.~(email: myaddress@nowhere.edu).
+\end{addendum}
+
+%%
+%% TABLES
+%%
+%% If there are any tables, put them here.
+%%
+\begin{table}
+\centering
+\caption{Parts and cost for the 30-300 $\mu$L pipette.}
+\label{table1}
+\medskip
+\begin{tabular}{|l|l|l|l|}
+\hline
+Part         & Unit Price & Source         & Part number \\ \hline
+Filament     & \$1.63     & Makerbot       & NA          \\ \hline
+1 mL Syringe & \$0.15     & BD Biosciences & 309628      \\ \hline
+Bolt         & \$0.12     & McMaster-Carr  & 91287A026   \\ \hline
+Nut          & \$0.01     & McMaster-Carr  & 90591A121   \\ \hline
+Spring (2)   & \$4.14     & McMaster-Carr  & 94125K542   \\ \hline
+Washers (2)  & \$0.16     & McMaster-Carr  & 90107A012   \\ \hline
+total        & \$6.21     &                &             \\ \hline
+\end{tabular}
+\end{table}
+
+\begin{table}
+\centering
+\caption{Parts and cost for the 100-1000 $\mu$L pipette.}
+\label{table2}
+\medskip
+\begin{tabular}{|l|l|l|l|}
+\hline
+Part         & Unit Price & Source         & Part number \\ \hline
+Filament     & \$1.63     & Makerbot       & NA          \\ \hline
+3 mL Syringe & \$0.73     & BD Biosciences & 309657      \\ \hline
+Bolt         & \$0.12     & McMaster-Carr  & 91287A026   \\ \hline
+Nut          & \$0.01     & McMaster-Carr  & 90591A121   \\ \hline
+Spring (2)   & \$4.14     & McMaster-Carr  & 94125K542   \\ \hline
+total        & \$6.63     &                &             \\ \hline
+\end{tabular}
+\end{table}
+
+\begin{table}
+\begin{adjustwidth}{-0.75in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\centering
+\caption{ISO 8655 for 100-1000 $\mu$L comparing a commercial pipette with our printed pipette used with existing 3 mL syringe scale and an adjusted scale}
+\label{table3}
+\begin{tabular}{llccccc}
+&                       & Mean   & Systematic Error & \% Sys. err. & Random Error & \% Rand. err. \\
+1000 $\mu$L & ISO 8655, 100-1000 $\mu$L & 1000    & 8.00             & 0.80         & 3.00         & 0.30          \\
+& Commercial Pipette    & 1002.98 & 2.98             & 0.30         & 1.72         & 0.17          \\
+& Printed Pipette       & 949.29  & -50.71           & -5.07        & 0.60         & 0.06          \\
+& Printed Pipette Scale & 1003.57 & 3.57             & 0.36         & 0.89         & 0.09          \\
+&                       &         &                  &              &              &               \\
+500 $\mu$L  & ISO 8655, 100-1000 $\mu$L & 500     & 8.00             & 1.60         & 3.00         & 0.60          \\
+& Commercial Pipette    & 503.67  & 3.67             & 0.73         & 0.49         & 0.10          \\
+& Printed Pipette       & 475.99  & -24.01           & -4.80        & 4.75         & 1.00          \\
+& Printed Pipette Scale & 503.62  & 3.62             & 0.72         & 1.64         & 0.33          \\
+&                       &         &                  &              &              &               \\
+200 $\mu$L  & ISO 8655, 100-1000 $\mu$L & 200     & 8.00             & 4.00         & 3.00         & 1.50          \\
+& Commercial Pipette    & 204.61  & 4.61             & 2.30         & 0.15         & 0.07          \\
+& Printed Pipette       & 186.55  & -13.45           & -6.72        & 1.31         & 0.70          \\
+& Printed Pipette Scale & 201.87  & 1.87             & 0.94         & 1.47         & 0.73          \\
+&                       &         &                  &              &              &               \\
+100 $\mu$L  & ISO 8655, 100-1000 $\mu$L & 100     & 8.00             & 8.00         & 3.00         & 3.00          \\
+& Commercial Pipette    & 104.29  & 4.29             & 4.29         & 1.65         & 1.58          \\
+& Printed Pipette       & 94.02   & -5.98            & -5.98        & 4.81         & 5.12          \\
+& Printed Pipette Scale & 101.00  & 1.00             & 1.00         & 1.05         & 1.04         
+\end{tabular}
+\end{adjustwidth}
+\end{table}
+
+\begin{table}
+\begin{adjustwidth}{-0.75in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\centering
+\caption{ISO 8655 for 30-300 $\mu$L comparing a commercial pipette with our printed pipette used with existing 3 mL syringe scale and an adjusted scale}
+\label{table4}
+\begin{tabular}{llccccc}
+&                       & Mean   & Systematic Error & \% Sys. err. & Random Error & \% Rand. err. \\
+300 $\mu$L & ISO 8655, 30-300 $\mu$L   & 300    & 4.00             & 1.33         & 1.50         & 0.50          \\
+& Commercial Pipette    & 301.19 & 1.19             & 0.40         & 0.53         & 0.18          \\
+& Printed Pipette       & 286.91 & -13.09           & -4.36        & 0.42         & 0.15          \\
+& Printed Pipette Scale & 299.11 & -0.89            & -0.30        & 0.48         & 0.16          \\
+&                       &        &                  &              &              &               \\
+200 $\mu$L & ISO 8655, 30-300 $\mu$L   & 200    & 4                & 2            & 1.5          & 0.75          \\
+& Commercial Pipette    & 200.06 & 0.06             & 0.03         & 0.46         & 0.23          \\
+& Printed Pipette       & 193.40 & -6.60            & -3.30        & 2.86         & 1.48          \\
+& Printed Pipette Scale & 200.57 & 0.57             & 0.28         & 0.86         & 0.43          \\
+&                       &        &                  &              &              &               \\
+50 $\mu$L  & ISO 8655, 30-300 $\mu$L   & 50     & 4                & 8            & 1.5          & 3             \\
+& Commercial Pipette    & 49.02  & -0.98            & -1.96        & 0.10         & 0.20          \\
+& Printed Pipette       & 49.62  & -0.38            & -0.76        & 1.26         & 2.53          \\
+& Printed Pipette Scale & 48.73  & -1.27            & -2.54        & 1.11         & 2.27          \\
+&                       &        &                  &              &              &               \\
+30 $\mu$L  & ISO 8655, 30-300 $\mu$L   & 30     & 4                & 13.3         & 1.5          & 5             \\
+& Commercial Pipette    & 29.08  & -0.92            & -3.06        & 0.09         & 0.31          \\
+& Printed Pipette       & 29.22  & -0.78            & -2.59        & 0.31         & 1.07          \\
+& Printed Pipette Scale & 27.78  & -2.22            & -7.41        & 1.37         & 4.93          \\        
+\end{tabular}
+\end{adjustwidth}
+\end{table}
+
+\begin{table}
+\centering
+\caption{This is a table with scientific results.}
+\medskip
+\begin{tabular}{ccccc}
+\hline
+1 & 2 & 3 & 4 & 5\\
+\hline
+aaa & bbb & ccc & ddd & eee\\
+aaaa & bbbb & cccc & dddd & eeee\\
+aaaaa & bbbbb & ccccc & ddddd & eeeee\\
+aaaaaa & bbbbbb & cccccc & dddddd & eeeeee\\
+1.000 & 2.000 & 3.000 & 4.000 & 5.000\\
+\hline
+\end{tabular}
+\end{table}
 

### 2017-01-13 nature-comm-manuscript/nature-template.tex
started nature comm manuscript

--- 2017-01-13 nature-comm-manuscript/manuscript.tex
@@
 
-\usepackage{changepage}
 %% make sure you have the nature.cls and naturemag.bst files where
@@
 
-\title{Open Design 3D-Printable Adjustable Micropipette that meets ISO Standard for Accuracy.}
+\title{Put title here (less than 90 characters).}
 
@@
 
-\author{Martin D. Brennan$^1$, Fahad F. Bokhari$^1$ \& David T. Eddington$^1$}
+\author{Aauthor$^{1,2}$, Bauthor$^2$ \& LastAuthor$^2$}
 
@@
 \begin{affiliations}
- \item Department of Bioengineering, University of Illinois at Chicago, Chicago, Illinois, USA
+ \item Put institutions in this environment and
+ \item separate with \verb|\item| commands.
 \end{affiliations}
@@
 \begin{abstract}
-Scientific communities are drawn to the open source model as an increasingly utilitarian method to produce and share work.
-Initially used as a means to develop freely available software, open source projects have been applied to hardware including scientific tools.
-Increasing convenience of 3D printing has fueled the proliferation of open labware projects aiming to develop and share designs for scientific tools that can be produced in-house as cheap alternatives to commercial products.
-We present our design of a micropipette that is assembled from 3D-printable parts and some hardware that works by actuating a disposable syringe to a user adjustable limit.
-Graduations on the syringe are used to accurately adjust the set point to the desired volume.  
-Our open design printed micropipette is assessed in comparison to a commercial pipette and meets ISO 8655 standards. (Add refs)
+For Nature, the abstract is really an introductory paragraph set
+in bold type.  This paragraph must be ``fully referenced'' and
+less than 180 words for Letters.  This is the thing that is
+supposed to be aimed at people from other disciplines and is
+arguably the most important part to getting your paper past the
+editors.  End this paragraph with a sentence like ``Here we
+show...'' or something similar.
 \end{abstract}
 
-\section*{Introduction}
-The open source development model, initially applied to software, is thriving in the development of open source scientific equipment due in part to increasing access of 3D printing\cite{Baden2015,Pearce2013}.
-Additive manufacturing methods have existed for decades although the recent availability of inexpensive desktop printers\cite{MakerbotIndustries,RepRap} have made it feasible for consumers to design and print prototypes and even functional parts, and consumer goods\cite{Fullerton2014,Wittbrodt2013}.
-Proliferation of free CAD software\cite{OpenScad,Blender,SketchUp,123D} and design sharing sites\cite{Thingiverse,NationalInstitutesofHealth,GrabCAD,GitHubInc} have also supported the growth and popularity of open designed parts and projects.
-Open design 3D-printable lab equipment is an attractive idea because, like open source software, it allows free access to technology that is otherwise inaccessible due to proprietary and/or financial barriers.
-Open design tools create opportunity for scientists and educational programs in remote or resource limited areas to participate with inexpensive and easy to make tools\cite{Marzullo2012,Lang2011,Fobel2013,Baker2014,Cybulski2014}.
-Open source development also enables the development of custom solutions to meet unique applications not met by commercial products that are shared freely and are user modifiable\cite{Fullerton2014,Pearce2012,Rankin2014,Sulkin2013,Dryden2015,DaCosta2014,Tek2008}.
-Some advanced, noteworthy, open source scientific equipment include a PCR device\cite{ChaiBiotechnologiesInc2015}, and a two-photon microscope\cite{Rosenegger2014} although simple tools have potential to be impactful as they can serve a wider community.
+Then the body of the main text appears after the intro paragraph.
+Figure environments can be left in place in the document.
+\verb|\includegraphics| commands are ignored since Nature wants
+the figures sent as separate files and the captions are
+automatically moved to the end of the document (they are printed
+out with the \verb|\end{document}| command. However, tables must
+be manually moved to the end of the document, after the addendum.
 
-Some simple and clever printable parts that have emerged are ones that give a new function to a ubiquitous existing device, such as drill bit attachment designed to hold centrifuge tubes, allowing a dremel to be used as a centrifuge\cite{Garvey2009}.
-Although this may make a rather crude centrifuge it may be an adequate solution for a fraction of the cost of a commercial centrifuge.
-Other examples of open source research tools that utilize 3D printed parts include optics equipment\cite{Zhang2013}, microscopes\cite{Baden2014a,Walus2014}, syringe pumps\cite{Wijnen2014}, reactionware\cite{Symes2012,Kitson2012,Mathieson2013,Kitson2014}, microfluidics\cite{Brennan2015,Dragone2013} and the list continues to grow\cite{PlosCollections}.
-
-One example of a everyday scientific tool that provides opportunity for an open design solution is the micropipette.
-An open design micropipette that can be made cheaply affords more options for labs and educational settings.
-Micropipettes are an indispensable tool used routinely in lab tasks and can easily cost \$1000 USD for a set.
-Often a lab will require several sets each for a dedicated task.
-Some pipettes may even re-calibrated for use with liquids of different properties.
-
-Air displacement pipettes use a piston operating principal to draw liquid into the pipette\cite{ISO8655}.
-In a typical commercial pipette the piston is made to be gas-tight with a gasketed plunger inside a smooth barrel.
-Consumer grade fused deposition modeling (FDM) printers are unable to build a smooth surface do to the formation of ridges that occur as each layer is deposited.
-The ridges formed by FDM make it impractical to form a gas-tight seal between moving parts, even with a gasket.
-Existing printable open-design micropipettes get around this limitation by stretching a membrane over one end of a printed tube, which when pressed causes the displacement.
-The displacement membrane can be made from any elastic material such as a latex glove.
-A few open design micropipettes exist including a popular one which, in addition to the printed parts, uses parts scavenged from a retractable pen\cite{Baden2014}.
-Because there is no built in feature such as a readout for the user to set the displacement to a desired volume, this design requires the user to validate the volumes dispensed with a high precision scale.
-Without verification with a scale the volumes dispensed can only be estimated based on calculations of the deflection of the membrane which is not a practical protocol.
-
-We submit a new design whose major strength is the ability to adjust to any volume aided by the the built in scale
-Our open design 3D-printable micropipette works by actuating a disposable syringe to a user adjustable set point.
-This allows the user to set the pipette to a volume by reading the graduations on the syringe barrel.
-We have also designed an adjusted graduation scale, to be used in place of the printed on scale, that corrects for the compressibility of air which allows the pipette to be set accurately.
-Additionally our pipette offers a simplified assembly requiring no glue, tape, or permanent connections.
-
-\begin{figure}
-\caption{
-{\bf CAD renderings of printable parts and cross-sections.} (A) The printed plunger part is a shaft pushes on the syringe plunger and slides in the printed body part.
-The printed plunger has a latching tongue and button which interfaces with the printed body part.
-(B) The printed body part holds the syringe and interfaces with the printed plunger part.
-The body part features the unlatching button and slots to hold the syringe in place by its flanges.
-The body part also has two cutouts in the top for the plunger button and for the hex nut and bolt.
-}
-\label{fig1}
-\end{figure}
-
-\begin{figure}
-\caption{
-{\bf CAD renderings of assembled pipette and function.} The pipette actuates the syringe to three positions.
-{\bf (A) The latched position.} When the plunger is pressed the pipette locks at this position.
-The tip is then placed in a liquid and the unlatching button is pressed to release the pipette back to the set position (B), drawing in liquid.
-{\bf(B) The set position.} The position of the screw determines the total displacement that the plunger moves.
-The pipette is spring loaded to return to this position.
-{\bf (C) The blow-out position.} The fluid is transferred by pressing the plunger past the latched position to blow-out all the liquid.
-{\bf (D) Return to the latched position.} The pipette returns to the latched position ready to preform another transfer.
-}
-\label{fig2}
-\end{figure}
-
-\begin{figure}
-\caption{
-{\bf Photos of assembled pipettes.}  (A) Two assemblies of the pipette: the 100-1000 $\mu$L configuration (above) and the 30-300 $\mu$L configuration (below).
-(B) Close-up photo of the taped on scale for each of the syringes.
-}
-\label{fig3}
-\end{figure}
-
-\section*{Results and Discussion}
-Validation testing preformed with the existing graduations printed on the syringes did not meet the ISO standards.
-According to ISO 8655 for a pipette with the maximum nominal volume of 1000 $\mu$L the systematic error cannot exceed 8 $\mu$L and the random error cannot exceed 3 $\mu$L.
-For the maximum nominal volume of 300 $\mu$L the systemic error cannot exceed 4 $\mu$L and the random error cannot exceed 1.5 $\mu$L.
-The commercial pipettes met these standards handily, but in our initial tests with our printed pipette we noticed large negative systematic error suggesting that we were missing a biasing factor. 
-This error was exaggerated while transferring larger volumes.
-After further investigation we realized that the graduations are intended to measure incompressible fluids within the syringe while we were using them to measure air while under vacuum.
-Because the syringe graduations were used to measure the air under vacuum it could not be expected to serve as a 1:1 volume ratio of water that was pulled into the tip because under vacuum the air had expanded.
-This explains the negative systematic error we were experiencing.
-The water in the tip pulls on the air due to gravity which causes it to expand slightly but enough to make measuring with the graduation in this way inaccurate.
-Our solution was to replace the built-in scale with a scale that accounted for the expansion.
-Using the data from our initial testing we calculated a factor for the expansion and used that to make the new scale (\ref{S1_Fig} and \ref{S1_Fig}.)
-With the new scale taped on the syringe our validation testing met the ISO 8655 standard.
-Replacing the scale with our scale that accounts for the expansion corrected this effect. 
-Our printed pipette with the adjusted scale meets ISO standards for accuracy and precision. (Table \ref{table3} and \ref{table4}).
-
-Our printed pipette improves on existing open design pipettes in several ways. 
-Most significantly the user is able to adjust the syringe accurately without verifying the volume with a scale.
-The pipette can be adjusted to any discrete volume within range.
-In addition, the assembly requires no permanent connections using tape or glue which allows for re-configuration and easy replacement of parts.
-Conveniently, our design can also reach to the bottom of a 15 mL conical tube allowing tasks such as aspirating supernatant fluid from a cell pellet.
-Unlike existing designs our design does not use a membrane that may wear out and require tedious replacement.
-The only major limitation of this design compared to the biropipette is the option for a pipette tip ejector.
-The biropipette also uses arguably easier to source parts (a pen VS a syringe) relative to what is required from our design.
-The biropipette also was developed in OpenSCAD which is free and open source CAD software where our design was created in Solidworks a proprietary software.
-
-This design relies heavily on the syringe, a specialized part, for the core function as well as accuracy.
-Fortunately, as disposable syringes are a regulated medical device they must meet high standards making them a reliable part for this design.
-As good as the performance of our printed pipette is, a commercial pipette should be expected to be more reliable and preferred for critical procedures. 
-Adjusting our printed pipette to the desired volume requires more time and attention which would be tedious for procedures requiring many adjustments.
-On the other hand, due to the \$6 cost to make, many printed pipettes could be assembled and pre-set, each for a planned transfer, rather then re-adjusting one commercial pipette for each step.
-The printable pipette can also be used as a disposable, sparing the commercial micropipette, in situations were cross-contamination and resterilization is required, or damage from volatile reagents is a concern.
-This pipette would also be ideal for high school and teaching labs or any resource limited program especially as part of a module about 3D printing.
-
-The open design nature of this project encourages anyone to use and submit changes to improve and add features to this design.
-All of the working files and documentation are kept in a public repository~\cite{BMLmicropipette}.
-Future directions for this project include developing a tip ejection system and additional configurations for transferring volumes below 30 uL as well as increasing over all user friendliness, such as making the adjusting bolt easier to grip and improving ergonomics.
-
-\section*{Conclusion}
-We have presented an open design micropipette that uses 3D-printable parts in addition to a disposable syringe and a few easily sourced pieces of hardware.
-Our open design pipette is novel in that it allows the user to set the pipette to the desired volume without the need to calibrate or verify with a weighing scale. 
-We validated the accuracy and precision of our pipette and developed a new graduation scale to correct for the use of the syringe for air-displacement measurements that meets the ISO standard for adjustable pipettes.
-Our design is free to use and modify to encourage further collaborative development.
+Citation of Einstein's paper \cite{Einstein}.
 
@@
 \begin{methods}
-Our printed pipette is designed to actuate a 1 mL or 3 mL syringe to a user set displacement.
-The core of the design is two printed parts, the body and the plunger which are able to be printed on a consumer grade FDM printer (fig.~\ref{fig1}), in this case a Makerbot Replicator.
-A 1 mL or 3 mL syringe twists to lock in the body part and is held into place by the syringe flanges.
-The 30-300 $\mu$L configuration uses a 1 mL pipette and the 100-1000 $\mu$L configuration uses a 3 mL pipette.
-The plunger part slides freely in the body part and actuates the syringe by pushing the thumb button (fig.~\ref{fig2}). 
-The pipette is spring loaded towards a set point which is adjustable by a set-screw.
-When the thumb button is pressed the system locks when it reaches the latched position, where it is ready to draw in fluid.
-The plunger is held in place with a latching button design which is released with the unlatching button drawing in fluid.
-The displacement is equal to the distance between the set position and the latched position.
-The pipette can also be pressed past the latched position to `blow-out' the transferred fluid completely from the pipette tip.   
-Additional materials required for assembly include two springs, a nut, a bolt and two washers.
-Attempts to make a printable luer lock adapter for tips was abandoned as the surface of printed parts is too rough to make an air tight seal with the luer or pipette tip.
-Instead, a combination of a barbed luer adapter and elastic tubing is used to attach the pipette tips.
-Our printed pipette mimics commercial pipettes design, function, and user operation, making it intuitive to use.
+Put methods in here.  If you are going to subsection it, use
+\verb|\subsection| commands.  Methods section should be less than
+800 words and if it is less than 200 words, it can be incorporated
+into the main text.
 
-Our pipette uses the air-displacement method, where a vacuum is applied to a pocket of air to draw liquid into the pipette.
-As air is an compressible fluid, this pocket of air grows due to the weight of the liquid pulling on it.
-Due to this effect the graduations on the syringe are not accurate, as they are designed for measuring liquid within the syringe.
-At larger volumes this effect is more pronounced resulting in the volume measured being greater than the amount of liquid pulled into the syringe.
-We remedied this by creating a new scale to account for the expansion.
-The scale is printed on a transparency sheet and is taped onto the syringe for accurate measurements (See~\ref{S1_Fig} and \ref{S2_Fig}).
+\subsection{Method subsection.}
 
-\subsection{Fabrication \& Assembly}
-Two parts are printed (body.stl and plunger.stl) at normal resolution with rafts on a Makerbot Replicator.
-A small amount of paraffin wax is applied to the screw to prevent slop from causing the set point to drift after each actuation.
-The nut is sunk into the hex inset in the printed body part.
-The bolt is threaded in from the top of the body into the nut.
-Springs and washers are threaded onto the plunger of a 1 mL syringe for the 30-300 $\mu$L configuration.
-Springs are placed inside a 3 mL syringe for the 100-1000 $\mu$L configuration.
-The plunger part is inserted in the body and the syringe assembly is pushed in and locked from the syringe flanges to the body part to complete assembly(fig.~\ref{fig3}).
-Parts and cost are listed in Table~\ref{table1} and \ref{table2}.
-
-\subsection{Validation}
-The printed pipette’s accuracy and precision was characterized and compared to a commercial pipette as well as ISO 8655.
-The printed pipette was adjusted to the target volume by eye from the syringe graduations.
-Deionized water was transferred and measured with a scale.
-Five transfers were recorded and averaged to account for random variability.
-Data was taken for printed pipettes with existing syringe graduations as well as with the our adjusted scale.
-Data was taken with commercial pipettes of 30-300 $\mu$L and 100-1000 $\mu$L to compare to the printed pipette.
-Accuracy and precision are expressed as systematic error and random error, respectively, and are calculated according to ISO 8655~\cite{ISO8655} (Table~\ref{table3} and \ref{table4}).
-The systematic error, or accuracy, is calculated according to the following equations where accuracy ($A$) is the difference of the mean volume ($\bar{V}$) and the nominal volume ($V_{o}$):
-
-\begin{equation}\label{eq:accuracy} 
-A = \bar{V}-V_{o},
-A\% = 100\%  \times  A / V_{o}
-\end{equation}
-The precision or random error is the standard deviation ($s$) of the measurements and ($cv$) is the coefficient of variation:
-
-\begin{equation}\label{eq:precision} 
-s = \sqrt{\frac{\sum_{i=1}^{n}(V_{i}-\bar{V})^2}{n-1}},
-cv = 100\% \times s / \bar{V}
-\end{equation}
+Here is a description of a specific method used.  Note that the
+subsection heading ends with a full stop (period) and that the
+command is \verb|\subsection{}| not \verb|\subsection*{}|.
 
@@
 %%
-\begin{table}
-\centering
-\caption{Parts and cost for the 30-300 $\mu$L pipette.}
-\label{table1}
-\medskip
-\begin{tabular}{|l|l|l|l|}
-\hline
-Part         & Unit Price & Source         & Part number \\ \hline
-Filament     & \$1.63     & Makerbot       & NA          \\ \hline
-1 mL Syringe & \$0.15     & BD Biosciences & 309628      \\ \hline
-Bolt         & \$0.12     & McMaster-Carr  & 91287A026   \\ \hline
-Nut          & \$0.01     & McMaster-Carr  & 90591A121   \\ \hline
-Spring (2)   & \$4.14     & McMaster-Carr  & 94125K542   \\ \hline
-Washers (2)  & \$0.16     & McMaster-Carr  & 90107A012   \\ \hline
-total        & \$6.21     &                &             \\ \hline
-\end{tabular}
-\end{table}
-
-\begin{table}
-\centering
-\caption{Parts and cost for the 100-1000 $\mu$L pipette.}
-\label{table2}
-\medskip
-\begin{tabular}{|l|l|l|l|}
-\hline
-Part         & Unit Price & Source         & Part number \\ \hline
-Filament     & \$1.63     & Makerbot       & NA          \\ \hline
-3 mL Syringe & \$0.73     & BD Biosciences & 309657      \\ \hline
-Bolt         & \$0.12     & McMaster-Carr  & 91287A026   \\ \hline
-Nut          & \$0.01     & McMaster-Carr  & 90591A121   \\ \hline
-Spring (2)   & \$4.14     & McMaster-Carr  & 94125K542   \\ \hline
-total        & \$6.63     &                &             \\ \hline
-\end{tabular}
-\end{table}
-
-\begin{table}
-\begin{adjustwidth}{-0.75in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
-\centering
-\caption{ISO 8655 for 100-1000 $\mu$L comparing a commercial pipette with our printed pipette used with existing 3 mL syringe scale and an adjusted scale}
-\label{table3}
-\begin{tabular}{llccccc}
-&                       & Mean   & Systematic Error & \% Sys. err. & Random Error & \% Rand. err. \\
-1000 $\mu$L & ISO 8655, 100-1000 $\mu$L & 1000    & 8.00             & 0.80         & 3.00         & 0.30          \\
-& Commercial Pipette    & 1002.98 & 2.98             & 0.30         & 1.72         & 0.17          \\
-& Printed Pipette       & 949.29  & -50.71           & -5.07        & 0.60         & 0.06          \\
-& Printed Pipette Scale & 1003.57 & 3.57             & 0.36         & 0.89         & 0.09          \\
-&                       &         &                  &              &              &               \\
-500 $\mu$L  & ISO 8655, 100-1000 $\mu$L & 500     & 8.00             & 1.60         & 3.00         & 0.60          \\
-& Commercial Pipette    & 503.67  & 3.67             & 0.73         & 0.49         & 0.10          \\
-& Printed Pipette       & 475.99  & -24.01           & -4.80        & 4.75         & 1.00          \\
-& Printed Pipette Scale & 503.62  & 3.62             & 0.72         & 1.64         & 0.33          \\
-&                       &         &                  &              &              &               \\
-200 $\mu$L  & ISO 8655, 100-1000 $\mu$L & 200     & 8.00             & 4.00         & 3.00         & 1.50          \\
-& Commercial Pipette    & 204.61  & 4.61             & 2.30         & 0.15         & 0.07          \\
-& Printed Pipette       & 186.55  & -13.45           & -6.72        & 1.31         & 0.70          \\
-& Printed Pipette Scale & 201.87  & 1.87             & 0.94         & 1.47         & 0.73          \\
-&                       &         &                  &              &              &               \\
-100 $\mu$L  & ISO 8655, 100-1000 $\mu$L & 100     & 8.00             & 8.00         & 3.00         & 3.00          \\
-& Commercial Pipette    & 104.29  & 4.29             & 4.29         & 1.65         & 1.58          \\
-& Printed Pipette       & 94.02   & -5.98            & -5.98        & 4.81         & 5.12          \\
-& Printed Pipette Scale & 101.00  & 1.00             & 1.00         & 1.05         & 1.04         
-\end{tabular}
-\end{adjustwidth}
-\end{table}
-
-\begin{table}
-\begin{adjustwidth}{-0.75in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
-\centering
-\caption{ISO 8655 for 30-300 $\mu$L comparing a commercial pipette with our printed pipette used with existing 3 mL syringe scale and an adjusted scale}
-\label{table4}
-\begin{tabular}{llccccc}
-&                       & Mean   & Systematic Error & \% Sys. err. & Random Error & \% Rand. err. \\
-300 $\mu$L & ISO 8655, 30-300 $\mu$L   & 300    & 4.00             & 1.33         & 1.50         & 0.50          \\
-& Commercial Pipette    & 301.19 & 1.19             & 0.40         & 0.53         & 0.18          \\
-& Printed Pipette       & 286.91 & -13.09           & -4.36        & 0.42         & 0.15          \\
-& Printed Pipette Scale & 299.11 & -0.89            & -0.30        & 0.48         & 0.16          \\
-&                       &        &                  &              &              &               \\
-200 $\mu$L & ISO 8655, 30-300 $\mu$L   & 200    & 4                & 2            & 1.5          & 0.75          \\
-& Commercial Pipette    & 200.06 & 0.06             & 0.03         & 0.46         & 0.23          \\
-& Printed Pipette       & 193.40 & -6.60            & -3.30        & 2.86         & 1.48          \\
-& Printed Pipette Scale & 200.57 & 0.57             & 0.28         & 0.86         & 0.43          \\
-&                       &        &                  &              &              &               \\
-50 $\mu$L  & ISO 8655, 30-300 $\mu$L   & 50     & 4                & 8            & 1.5          & 3             \\
-& Commercial Pipette    & 49.02  & -0.98            & -1.96        & 0.10         & 0.20          \\
-& Printed Pipette       & 49.62  & -0.38            & -0.76        & 1.26         & 2.53          \\
-& Printed Pipette Scale & 48.73  & -1.27            & -2.54        & 1.11         & 2.27          \\
-&                       &        &                  &              &              &               \\
-30 $\mu$L  & ISO 8655, 30-300 $\mu$L   & 30     & 4                & 13.3         & 1.5          & 5             \\
-& Commercial Pipette    & 29.08  & -0.92            & -3.06        & 0.09         & 0.31          \\
-& Printed Pipette       & 29.22  & -0.78            & -2.59        & 0.31         & 1.07          \\
-& Printed Pipette Scale & 27.78  & -2.22            & -7.41        & 1.37         & 4.93          \\        
-\end{tabular}
-\end{adjustwidth}
-\end{table}
 

### 2017-01-18 nature-comm-manuscript/manuscript.tex
submitted to nat comm

@@
 
-\documentclass{nature}
+\documentclass{naturegraphicx}
 
 \usepackage{changepage}
+\usepackage{graphicx}
+
 %% make sure you have the nature.cls and naturemag.bst files where
@@
 Graduations on the syringe are used to accurately adjust the set point to the desired volume.  
-Our open design printed micropipette is assessed in comparison to a commercial pipette and meets ISO 8655 standards. (Add refs)
+Our open design printed micropipette is assessed in comparison to a commercial pipette and meets ISO 8655 standards.
 \end{abstract}
@@
 Open design 3D-printable lab equipment is an attractive idea because, like open source software, it allows free access to technology that is otherwise inaccessible due to proprietary and/or financial barriers.
-Open design tools create opportunity for scientists and educational programs in remote or resource limited areas to participate with inexpensive and easy to make tools\cite{Marzullo2012,Lang2011,Fobel2013,Baker2014,Cybulski2014}.
+Open design tools create opportunity for scientists and educational programs in remote or resource limited areas to participate with inexpensive and easy to make tools\cite{Marzullo2012,Lang2011,Fobel2013,Baker2014,Cybulski2014,Bhamla2017}.
 Open source development also enables the development of custom solutions to meet unique applications not met by commercial products that are shared freely and are user modifiable\cite{Fullerton2014,Pearce2012,Rankin2014,Sulkin2013,Dryden2015,DaCosta2014,Tek2008}.
-Some advanced, noteworthy, open source scientific equipment include a PCR device\cite{ChaiBiotechnologiesInc2015}, and a two-photon microscope\cite{Rosenegger2014} although simple tools have potential to be impactful as they can serve a wider community.
+Some advanced, noteworthy, open source scientific equipment include a PCR device\cite{ChaiBiotechnologiesInc2015}, a tissue scaffold printer\cite{Trachtenberg2014}, and a two-photon microscope\cite{Rosenegger2014} although simple tools have potential to be impactful as they can serve a wider community.
 
@@
 Although this may make a rather crude centrifuge it may be an adequate solution for a fraction of the cost of a commercial centrifuge.
-Other examples of open source research tools that utilize 3D printed parts include optics equipment\cite{Zhang2013}, microscopes\cite{Baden2014a,Walus2014}, syringe pumps\cite{Wijnen2014}, reactionware\cite{Symes2012,Kitson2012,Mathieson2013,Kitson2014}, microfluidics\cite{Brennan2015,Dragone2013} and the list continues to grow\cite{PlosCollections}.
+Other examples of open source research tools that utilize 3D printed parts include optics equipment\cite{Zhang2013}, microscopes\cite{Baden2014a,Walus2014}, syringe pumps\cite{Wijnen2014,Patrick2015}, reactionware\cite{Symes2012,Kitson2012,Mathieson2013,Kitson2014}, microfluidics\cite{Brennan2015,Dragone2013} and the list continues to grow\cite{PlosCollections}.
 
@@
 In a typical commercial pipette the piston is made to be gas-tight with a gasketed plunger inside a smooth barrel.
-Consumer grade fused deposition modeling (FDM) printers are unable to build a smooth surface do to the formation of ridges that occur as each layer is deposited.
+Consumer grade fused deposition modeling (FDM) printers are unable to build a smooth surface do to the formation of ridges that occur as each layer is deposited\cite{Takagishi2017}.
 The ridges formed by FDM make it impractical to form a gas-tight seal between moving parts, even with a gasket.
@@
 
-We submit a new design whose major strength is the ability to adjust to any volume aided by the the built in scale
+We submit a new design whose major strength is the ability to adjust to any volume aided by the the built in scale.
 Our open design 3D-printable micropipette works by actuating a disposable syringe to a user adjustable set point.
@@
 \begin{figure}
+\includegraphics[scale=0.4]{figure1.png} % this command will be ignored
 \caption{
@@
 \begin{figure}
+\includegraphics[scale=0.4]{figure2.png} % this command will be ignored
 \caption{
@@
 \begin{figure}
+\includegraphics[scale=1]{figure3.png} % this command will be ignored
 \caption{
@@
 Our solution was to replace the built-in scale with a scale that accounted for the expansion.
-Using the data from our initial testing we calculated a factor for the expansion and used that to make the new scale (\ref{S1_Fig} and \ref{S1_Fig}.)
+Using the data from our initial testing we calculated a factor for the expansion and used that to make the new scale (See SI Fig. 1 and SI Fig. 2). %\ref{S1_Fig} and \ref{S1_Fig}.
 With the new scale taped on the syringe our validation testing met the ISO 8655 standard.
@@
 
-\begin{figure}
-%%%\includegraphics{something} % this command will be ignored
-\caption{Each figure legend should begin with a brief title for
-the whole figure and continue with a short description of each
-panel and the symbols used. For contributions with methods
-sections, legends should not contain any details of methods, or
-exceed 100 words (fewer than 500 words in total for the whole
-paper). In contributions without methods sections, legends should
-be fewer than 300 words (800 words or fewer in total for the whole
-paper).}
-\end{figure}
-
-\section*{Another Section}
-
-Sections can only be used in Articles.  Contributions should be
-organized in the sequence: title, text, methods, references,
-Supplementary Information line (if any), acknowledgements,
-interest declaration, corresponding author line, tables, figure
-legends.
-
-Spelling must be British English (Oxford English Dictionary)
-
-In addition, a cover letter needs to be written with the
-following:
-\begin{enumerate}
- \item A 100 word or less summary indicating on scientific grounds
-why the paper should be considered for a wide-ranging journal like
-\textsl{Nature} instead of a more narrowly focussed journal.
- \item A 100 word or less summary aimed at a non-scientific audience,
-written at the level of a national newspaper.  It may be used for
-\textsl{Nature}'s press release or other general publicity.
- \item The cover letter should state clearly what is included as the
-submission, including number of figures, supporting manuscripts
-and any Supplementary Information (specifying number of items and
-format).
- \item The cover letter should also state the number of
-words of text in the paper; the number of figures and parts of
-figures (for example, 4 figures, comprising 16 separate panels in
-total); a rough estimate of the desired final size of figures in
-terms of number of pages; and a full current postal address,
-telephone and fax numbers, and current e-mail address.
-\end{enumerate}
-
-See \textsl{Nature}'s website
-(\texttt{http://www.nature.com/nature/submit/gta/index.html}) for
-complete submission guidelines.
-
 \begin{methods}
 Our printed pipette is designed to actuate a 1 mL or 3 mL syringe to a user set displacement.
-The core of the design is two printed parts, the body and the plunger which are able to be printed on a consumer grade FDM printer (fig.~\ref{fig1}), in this case a Makerbot Replicator.
+The core of the design is two printed parts, the body and the plunger which are able to be printed on a consumer grade FDM printer (fig. 1~\ref{fig1}), in this case a Makerbot Replicator.
 A 1 mL or 3 mL syringe twists to lock in the body part and is held into place by the syringe flanges.
 The 30-300 $\mu$L configuration uses a 1 mL pipette and the 100-1000 $\mu$L configuration uses a 3 mL pipette.
-The plunger part slides freely in the body part and actuates the syringe by pushing the thumb button (fig.~\ref{fig2}). 
+The plunger part slides freely in the body part and actuates the syringe by pushing the thumb button (fig. 2~\ref{fig2}). 
 The pipette is spring loaded towards a set point which is adjustable by a set-screw.
@@
 We remedied this by creating a new scale to account for the expansion.
-The scale is printed on a transparency sheet and is taped onto the syringe for accurate measurements (See~\ref{S1_Fig} and \ref{S2_Fig}).
+The scale is printed on a transparency sheet and is taped onto the syringe for accurate measurements (See SI Fig. 1 and SI Fig. 2).% ~\ref{S1_Fig} and ~\ref{S2_Fig}).
 
@@
 Springs are placed inside a 3 mL syringe for the 100-1000 $\mu$L configuration.
-The plunger part is inserted in the body and the syringe assembly is pushed in and locked from the syringe flanges to the body part to complete assembly(fig.~\ref{fig3}).
+The plunger part is inserted in the body and the syringe assembly is pushed in and locked from the syringe flanges to the body part to complete assembly (fig. 3~\ref{fig3}).
 Parts and cost are listed in Table~\ref{table1} and \ref{table2}.
@@
 
-%% Put the bibliography here, most people will use BiBTeX in
-%% which case the environment below should be replaced with
-%% the \bibliography{} command.
+%\bibliographystyle{naturemag}
+%\bibliography{sample}
 
-% \begin{thebibliography}{1}
-% \bibitem{dummy} Articles are restricted to 50 references, Letters
-% to 30.
-% \bibitem{dummyb} No compound references -- only one source per
-% reference.
-% \end{thebibliography}
+\begin{thebibliography}{10}
+	\expandafter\ifx\csname url\endcsname\relax
+	\def\url#1{\texttt{#1}}\fi
+	\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
+	\providecommand{\bibinfo}[2]{#2}
+	\providecommand{\eprint}[2][]{\url{#2}}
 
-\bibliographystyle{naturemag}
-\bibliography{sample}
+	\bibitem{Baden2015}
+	\bibinfo{author}{Baden, T.} \emph{et~al.}
+	\newblock \bibinfo{title}{{Open Labware: 3-D Printing Your Own Lab Equipment}}.
+	\newblock \emph{\bibinfo{journal}{PLOS Biology}} \textbf{\bibinfo{volume}{13}},
+	\bibinfo{pages}{e1002086} (\bibinfo{year}{2015}).
+	\newblock \urlprefix\url{http://dx.plos.org/10.1371/journal.pbio.1002086}.
+
+	\bibitem{Pearce2013}
+	\bibinfo{author}{Pearce, J.~M.}
+	\newblock \emph{\bibinfo{title}{{Open-source Lab}}} (\bibinfo{year}{2013}).
+
+	\bibitem{MakerbotIndustries}
+	\bibinfo{author}{{Makerbot Industries}}.
+	\newblock \bibinfo{title}{{Makerbot}} (\bibinfo{year}{2017}).
+	\newblock \urlprefix\url{https://www.makerbot.com/}.
+
+	\bibitem{RepRap}
+	\bibinfo{author}{{RepRap Project}}.
+	\newblock \bibinfo{title}{{RepRap}} (\bibinfo{year}{2017}).
+	\newblock \urlprefix\url{reprap.org}.
+
+	\bibitem{Fullerton2014}
+	\bibinfo{author}{Fullerton, J.~N.}, \bibinfo{author}{Frodsham, G. C.~M.} \&
+	\bibinfo{author}{Day, R.~M.}
+	\newblock \bibinfo{title}{{3D printing for the many, not the few}}.
+	\newblock \emph{\bibinfo{journal}{Nature Biotechnology}}
+	\textbf{\bibinfo{volume}{32}}, \bibinfo{pages}{1086--1087}
+	(\bibinfo{year}{2014}).
+	\newblock \urlprefix\url{http://www.nature.com/doifinder/10.1038/nbt.3056}.
+
+	\bibitem{Wittbrodt2013}
+	\bibinfo{author}{Wittbrodt, B.} \emph{et~al.}
+	\newblock \bibinfo{title}{{Life-cycle economic analysis of distributed
+			manufacturing with open-source 3-D printers}}.
+	\newblock \emph{\bibinfo{journal}{Mechatronics}} \textbf{\bibinfo{volume}{23}},
+	\bibinfo{pages}{713--726} (\bibinfo{year}{2013}).
+	\newblock
+	\urlprefix\url{http://linkinghub.elsevier.com/retrieve/pii/S0957415813001153}.
+
+	\bibitem{OpenScad}
+	\bibinfo{author}{Kintel, M.}
+	\newblock \bibinfo{title}{{OpenSCAD}} (\bibinfo{year}{2017}).
+	\newblock \urlprefix\url{http://www.openscad.org/}.
+
+	\bibitem{Blender}
+	\bibinfo{author}{{Blender Foudation}}.
+	\newblock \bibinfo{title}{{Blender}}  (\bibinfo{year}{2017}).
+	\newblock \urlprefix\url{www.blender.org}.
+
+	\bibitem{SketchUp}
+	\bibinfo{author}{{Trimble Inc.}}
+	\newblock \bibinfo{title}{{SketchUp}} (\bibinfo{year}{2016}).
+	\newblock \urlprefix\url{www.sketchup.com}.
+
+	\bibitem{123D}
+	\bibinfo{author}{{Autodesk Inc.}}
+	\newblock \bibinfo{title}{{Autodesk 123D}} (\bibinfo{year}{2017}).
+	\newblock \urlprefix\url{www.123dapp.com}.
+
+	\bibitem{Thingiverse}
+	\bibinfo{author}{{Makerbot Industries}}.
+	\newblock \bibinfo{title}{{Thingiverse}} (\bibinfo{year}{2017}).
+	\newblock \urlprefix\url{https://www.thingiverse.com/}.
+
+	\bibitem{NationalInstitutesofHealth}
+	\bibinfo{author}{{National Institutes of Health}}.
+	\newblock \bibinfo{title}{{NIH 3D Print Exchange}}  (\bibinfo{year}{2017}).
+	\newblock \urlprefix\url{http://3dprint.nih.gov/}.
+
+	\bibitem{GrabCAD}
+	\bibinfo{author}{Stratasys}.
+	\newblock \bibinfo{title}{{GrabCAD}}.
+	\newblock \urlprefix\url{https://grabcad.com/}.
+
+	\bibitem{GitHubInc}
+	\bibinfo{author}{{GitHub Inc.}}
+	\newblock \bibinfo{title}{{GitHub}}  (\bibinfo{year}{2017}).
+	\newblock \urlprefix\url{https://github.com/}.
+
+	\bibitem{Marzullo2012}
+	\bibinfo{author}{Marzullo, T.~C.} \& \bibinfo{author}{Gage, G.~J.}
+	\newblock \bibinfo{title}{{The SpikerBox: A Low Cost, Open-Source BioAmplifier
+			for Increasing Public Participation in Neuroscience Inquiry}}.
+	\newblock \emph{\bibinfo{journal}{PLoS ONE}} \textbf{\bibinfo{volume}{7}},
+	\bibinfo{pages}{e30837} (\bibinfo{year}{2012}).
+	\newblock \urlprefix\url{http://dx.plos.org/10.1371/journal.pone.0030837}.
+
+	\bibitem{Lang2011}
+	\bibinfo{author}{Lang, T.}
+	\newblock \bibinfo{title}{{Advancing global health research through digital
+			technology and sharing data.}}
+	\newblock \emph{\bibinfo{journal}{Science (New York, N.Y.)}}
+	\textbf{\bibinfo{volume}{331}}, \bibinfo{pages}{714--717}
+	(\bibinfo{year}{2011}).
+
+	\bibitem{Fobel2013}
+	\bibinfo{author}{Fobel, R.}, \bibinfo{author}{Fobel, C.} \&
+	\bibinfo{author}{Wheeler, A.~R.}
+	\newblock \bibinfo{title}{{DropBot: An open-source digital microfluidic control
+			system with precise control of electrostatic driving force and instantaneous
+			drop velocity measurement}}.
+	\newblock \emph{\bibinfo{journal}{Applied Physics Letters}}
+	\textbf{\bibinfo{volume}{102}}, \bibinfo{pages}{1--5} (\bibinfo{year}{2013}).
+
+	\bibitem{Baker2014}
+	\bibinfo{author}{Baker, E.}
+	\newblock \bibinfo{title}{{Open source data logger for low-cost environmental
+			monitoring.}}
+	\newblock \emph{\bibinfo{journal}{Biodiversity data journal}}
+	\bibinfo{pages}{e1059} (\bibinfo{year}{2014}).
+	\newblock
+	\urlprefix\url{http://www.pubmedcentral.nih.gov/articlerender.fcgi?artid=4030251{\&}tool=pmcentrez{\&}rendertype=abstract}.
+
+	\bibitem{Cybulski2014}
+	\bibinfo{author}{Cybulski, J.~S.}, \bibinfo{author}{Clements, J.} \&
+	\bibinfo{author}{Prakash, M.}
+	\newblock \bibinfo{title}{{Foldscope: origami-based paper microscope.}}
+	\newblock \emph{\bibinfo{journal}{PloS one}} \textbf{\bibinfo{volume}{9}},
+	\bibinfo{pages}{e98781} (\bibinfo{year}{2014}).
+	\newblock
+	\urlprefix\url{http://journals.plos.org/plosone/article?id=10.1371/journal.pone.0098781}.
+	\newblock \eprint{1403.1211}.
+
+	\bibitem{Bhamla2017}
+	\bibinfo{author}{Bhamla, M.~S.} \emph{et~al.}
+	\newblock \bibinfo{title}{{Hand-powered ultralow-cost paper centrifuge}}.
+	\newblock \emph{\bibinfo{journal}{Nature Biomedical Engineering}}
+	\textbf{\bibinfo{volume}{1}}, \bibinfo{pages}{0009} (\bibinfo{year}{2017}).
+	\newblock \urlprefix\url{http://www.nature.com/articles/s41551-016-0009}.
+
+	\bibitem{Pearce2012}
+	\bibinfo{author}{Pearce, J.~M.}
+	\newblock \bibinfo{title}{{Building Research Equipment with Free, Open-Source
+			Hardware}}.
+	\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{337}},
+	\bibinfo{pages}{1303--1304} (\bibinfo{year}{2012}).
+	\newblock
+	\urlprefix\url{citeulike-article-id:11241059{\%}5Cnhttp://dx.doi.org/10.1126/science.1226328
+		http://www.ncbi.nlm.nih.gov/pubmed/22984060
+		http://www.sciencemag.org/cgi/doi/10.1126/science.1228183}.
+
+	\bibitem{Rankin2014}
+	\bibinfo{author}{Rankin, T.~M.} \emph{et~al.}
+	\newblock \bibinfo{title}{{Three-dimensional printing surgical instruments: are
+			we there yet?}}
+	\newblock \emph{\bibinfo{journal}{Journal of Surgical Research}}
+	\textbf{\bibinfo{volume}{189}}, \bibinfo{pages}{193--197}
+	(\bibinfo{year}{2014}).
+	\newblock
+	\urlprefix\url{http://linkinghub.elsevier.com/retrieve/pii/S0022480414001644}.
+
+	\bibitem{Sulkin2013}
+	\bibinfo{author}{Sulkin, M.~S.} \emph{et~al.}
+	\newblock \bibinfo{title}{{Three-dimensional printing physiology laboratory
+			technology}}.
+	\newblock \emph{\bibinfo{journal}{AJP: Heart and Circulatory Physiology}}
+	\textbf{\bibinfo{volume}{305}}, \bibinfo{pages}{H1569--H1573}
+	(\bibinfo{year}{2013}).
+	\newblock
+	\urlprefix\url{http://ajpheart.physiology.org/cgi/doi/10.1152/ajpheart.00599.2013}.
+
+	\bibitem{Dryden2015}
+	\bibinfo{author}{Dryden, M. D.~M.} \& \bibinfo{author}{Wheeler, A.~R.}
+	\newblock \bibinfo{title}{{DStat: A versatile, open-source potentiostat for
+			electroanalysis and integration}}.
+	\newblock \emph{\bibinfo{journal}{PLoS ONE}} \textbf{\bibinfo{volume}{10}},
+	\bibinfo{pages}{1--17} (\bibinfo{year}{2015}).
+	\newblock \urlprefix\url{http://dx.doi.org/10.1371/journal.pone.0140349}.
+
+	\bibitem{DaCosta2014}
+	\bibinfo{author}{da~Costa, E.~T.} \emph{et~al.}
+	\newblock \bibinfo{title}{{Getting started with open-hardware: Development and
+			control of microfluidic devices}}.
+	\newblock \emph{\bibinfo{journal}{Electrophoresis}}
+	\textbf{\bibinfo{volume}{35}}, \bibinfo{pages}{2370--2377}
+	(\bibinfo{year}{2014}).
+
+	\bibitem{Tek2008}
+	\bibinfo{author}{Tek, P.} \emph{et~al.}
+	\newblock \bibinfo{title}{{Rapid prototyping for neuroscience and neural
+			engineering}}.
+	\newblock \emph{\bibinfo{journal}{Journal of Neuroscience Methods}}
+	\textbf{\bibinfo{volume}{172}}, \bibinfo{pages}{263--269}
+	(\bibinfo{year}{2008}).
+
+	\bibitem{ChaiBiotechnologiesInc2015}
+	\bibinfo{author}{{Chai Biotechnologies Inc}}.
+	\newblock \bibinfo{title}{{Open PCR}} (\bibinfo{year}{2017}).
+	\newblock \urlprefix\url{http://openpcr.org/}.
+
+	\bibitem{Trachtenberg2014}
+	\bibinfo{author}{Trachtenberg, J.~E.} \emph{et~al.}
+	\newblock \bibinfo{title}{{Open-source three-dimensional printing of
+			biodegradable polymer scaffolds for tissue engineering}}.
+	\newblock \emph{\bibinfo{journal}{Journal of Biomedical Materials Research -
+			Part A}} \textbf{\bibinfo{volume}{102}}, \bibinfo{pages}{4326--4335}
+	(\bibinfo{year}{2014}).
+
+	\bibitem{Rosenegger2014}
+	\bibinfo{author}{Rosenegger, D.~G.}, \bibinfo{author}{Tran, C. H.~T.},
+	\bibinfo{author}{LeDue, J.}, \bibinfo{author}{Zhou, N.} \&
+	\bibinfo{author}{Gordon, G.~R.}
+	\newblock \bibinfo{title}{{A High Performance, Cost-Effective, Open-Source
+			Microscope for Scanning Two-Photon Microscopy that Is Modular and Readily
+			Adaptable}}.
+	\newblock \emph{\bibinfo{journal}{PLoS ONE}} \textbf{\bibinfo{volume}{9}},
+	\bibinfo{pages}{e110475} (\bibinfo{year}{2014}).
+	\newblock \urlprefix\url{http://dx.plos.org/10.1371/journal.pone.0110475}.
+
+	\bibitem{Garvey2009}
+	\bibinfo{author}{Garvey, C.}
+	\newblock \bibinfo{title}{{DremelFuge}} (\bibinfo{year}{2009}).
+	\newblock \urlprefix\url{https://www.thingiverse.com/thing:1483}.
+
+	\bibitem{Zhang2013}
+	\bibinfo{author}{Zhang, C.}, \bibinfo{author}{Anzalone, N.~C.},
+	\bibinfo{author}{Faria, R.~P.} \& \bibinfo{author}{Pearce, J.~M.}
+	\newblock \bibinfo{title}{{Open-Source 3D-Printable Optics Equipment}}.
+	\newblock \emph{\bibinfo{journal}{PLoS ONE}} \textbf{\bibinfo{volume}{8}}
+	(\bibinfo{year}{2013}).
+
+	\bibitem{Baden2014a}
+	\bibinfo{author}{Baden, T.}
+	\newblock \bibinfo{title}{{Raspberry Pi Scope}}  (\bibinfo{year}{2014}).
+	\newblock \urlprefix\url{http://3dprint.nih.gov/discover/3dpx-000609}.
+
+	\bibitem{Walus2014}
+	\bibinfo{author}{Walus, K.}
+	\newblock \bibinfo{title}{{A Fully Printable Microscope}}
+	(\bibinfo{year}{2014}).
+	\newblock \urlprefix\url{http://3dprint.nih.gov/discover/3dpx-000304}.
+
+	\bibitem{Wijnen2014}
+	\bibinfo{author}{Wijnen, B.}, \bibinfo{author}{Hunt, E.~J.},
+	\bibinfo{author}{Anzalone, G.~C.} \& \bibinfo{author}{Pearce, J.~M.}
+	\newblock \bibinfo{title}{{Open-Source Syringe Pump Library}}.
+	\newblock \emph{\bibinfo{journal}{PLoS ONE}} \textbf{\bibinfo{volume}{9}},
+	\bibinfo{pages}{e107216} (\bibinfo{year}{2014}).
+	\newblock \urlprefix\url{http://dx.plos.org/10.1371/journal.pone.0107216}.
+
+	\bibitem{Patrick2015}
+	\bibinfo{author}{Patrick, W.~G.} \emph{et~al.}
+	\newblock \bibinfo{title}{{DNA assembly in 3D printed fluidics}}.
+	\newblock \emph{\bibinfo{journal}{PLoS ONE}} \textbf{\bibinfo{volume}{10}},
+	\bibinfo{pages}{1--18} (\bibinfo{year}{2015}).
+
+	\bibitem{Symes2012}
+	\bibinfo{author}{Symes, M.} \emph{et~al.}
+	\newblock \bibinfo{title}{{Integrated 3D-printed reactionware for chemical
+			synthesis and analysis}}.
+	\newblock \emph{\bibinfo{journal}{Nature Chemistry}}
+	\textbf{\bibinfo{volume}{4}}, \bibinfo{pages}{349--354}
+	(\bibinfo{year}{2012}).
+	\newblock \urlprefix\url{http://eprints.gla.ac.uk/68744/}.
+
+	\bibitem{Kitson2012}
+	\bibinfo{author}{Kitson, P.~J.}, \bibinfo{author}{Rosnes, M.~H.},
+	\bibinfo{author}{Sans, V.}, \bibinfo{author}{Dragone, V.} \&
+	\bibinfo{author}{Cronin, L.}
+	\newblock \bibinfo{title}{{Configurable 3D-Printed millifluidic and
+			microfluidic ‘lab on a chip' reactionware devices}}.
+	\newblock \emph{\bibinfo{journal}{Lab on a Chip}}
+	\textbf{\bibinfo{volume}{12}}, \bibinfo{pages}{3267} (\bibinfo{year}{2012}).
+
+	\bibitem{Mathieson2013}
+	\bibinfo{author}{Mathieson, J.~S.}, \bibinfo{author}{Rosnes, M.~H.},
+	\bibinfo{author}{Sans, V.}, \bibinfo{author}{Kitson, P.~J.} \&
+	\bibinfo{author}{Cronin, L.}
+	\newblock \bibinfo{title}{{Continuous parallel ESI-MS analysis of reactions
+			carried out in a bespoke 3D printed device}}.
+	\newblock \emph{\bibinfo{journal}{Beilstein Journal of Nanotechnology}}
+	\textbf{\bibinfo{volume}{4}}, \bibinfo{pages}{285--291}
+	(\bibinfo{year}{2013}).
+
+	\bibitem{Kitson2014}
+	\bibinfo{author}{Kitson, P.~J.}, \bibinfo{author}{Marshall, R.~J.},
+	\bibinfo{author}{Long, D.}, \bibinfo{author}{Forgan, R.~S.} \&
+	\bibinfo{author}{Cronin, L.}
+	\newblock \bibinfo{title}{{3D Printed high-throughput hydrothermal reactionware
+			for discovery, optimization, and scale-up}}.
+	\newblock \emph{\bibinfo{journal}{Angewandte Chemie - International Edition}}
+	\bibinfo{pages}{1--7} (\bibinfo{year}{2014}).
+
+	\bibitem{Brennan2015}
+	\bibinfo{author}{Brennan, M.~D.}, \bibinfo{author}{Rexius-Hall, M.~L.} \&
+	\bibinfo{author}{Eddington, D.~T.}
+	\newblock \bibinfo{title}{{A 3D-Printed Oxygen Control Insert for a 24-Well
+			Plate}}.
+	\newblock \emph{\bibinfo{journal}{Plos One}} \textbf{\bibinfo{volume}{10}},
+	\bibinfo{pages}{e0137631} (\bibinfo{year}{2015}).
+	\newblock \urlprefix\url{http://dx.plos.org/10.1371/journal.pone.0137631}.
+
+	\bibitem{Dragone2013}
+	\bibinfo{author}{Dragone, V.}, \bibinfo{author}{Sans, V.},
+	\bibinfo{author}{Rosnes, M.~H.}, \bibinfo{author}{Kitson, P.~J.} \&
+	\bibinfo{author}{Cronin, L.}
+	\newblock \bibinfo{title}{{3D-printed devices for continuous-flow organic
+			chemistry}}.
+	\newblock \emph{\bibinfo{journal}{Beilstein Journal of Organic Chemistry}}
+	\textbf{\bibinfo{volume}{9}}, \bibinfo{pages}{951--959}
+	(\bibinfo{year}{2013}).
+
+	\bibitem{PlosCollections}
+	\bibinfo{author}{{Plos Collections}}.
+	\newblock \bibinfo{title}{{Open Source Toolkit Hardware}}
+	(\bibinfo{year}{2017}).
+	\newblock
+	\urlprefix\url{http://collections.plos.org/open-source-toolkit-hardware}.
+
+	\bibitem{ISO8655}
+	\bibinfo{author}{{International Organization for Standardization}}.
+	\newblock \emph{\bibinfo{title}{{ISO 8655-1:2002(en)}}} (\bibinfo{year}{2002}).
+
+	\bibitem{Takagishi2017}
+	\bibinfo{author}{Takagishi, K.} \& \bibinfo{author}{Umezu, S.}
+	\newblock \bibinfo{title}{{Development of the Improving Process for the 3D
+			Printed Structure}}.
+	\newblock \emph{\bibinfo{journal}{Nature Publishing Group}}
+	\bibinfo{pages}{1--10} (\bibinfo{year}{2017}).
+	\newblock \urlprefix\url{http://dx.doi.org/10.1038/srep39852}.
+
+	\bibitem{Baden2014}
+	\bibinfo{author}{Baden, T.}
+	\newblock \bibinfo{title}{{Biropette: customisable, high precision pipette.}}
+	(\bibinfo{year}{2014}).
+	\newblock \urlprefix\url{http://www.thingiverse.com/thing:255519}.
+
+	\bibitem{BMLmicropipette}
+	\bibinfo{author}{{Eddington Lab}}.
+	\newblock \bibinfo{title}{{3D Printable Micropipette}} (\bibinfo{year}{2017}).
+	\newblock
+	\urlprefix\url{https://github.com/Biological-Microsystems-Laboratory/micropipette}.
+
+\end{thebibliography}
 
@@
 \begin{addendum}
- \item Put acknowledgements here.
+ \item We would like to acknowledge the UIC Bioengineering Senior Design team of 2014 for initial work on this project: Oluwafemi Aboloye, Pedro Hurtado, Rafael Romero, and Vivian Sandoval.
  \item[Competing Interests] The authors declare that they have no
@@
  \item[Correspondence] Correspondence and requests for materials
-should be addressed to A.B.C.~(email: myaddress@nowhere.edu).
+should be addressed to David T. Eddington~(email: dte@uic.edu).
 \end{addendum}
@@
 \begin{table}
-\begin{adjustwidth}{-0.75in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\begin{adjustwidth}{-0.75in}{-1.0in}
 \centering
@@
 
-\begin{table}
-\centering
-\caption{This is a table with scientific results.}
-\medskip
-\begin{tabular}{ccccc}
-\hline
-1 & 2 & 3 & 4 & 5\\
-\hline
-aaa & bbb & ccc & ddd & eee\\
-aaaa & bbbb & cccc & dddd & eeee\\
-aaaaa & bbbbb & ccccc & ddddd & eeeee\\
-aaaaaa & bbbbbb & cccccc & dddddd & eeeeee\\
-1.000 & 2.000 & 3.000 & 4.000 & 5.000\\
-\hline
-\end{tabular}
-\end{table}
-
 \end{document}

### 2017-06-27 Plos-one-manuscript/latex/manuscript.tex
working on review

@@
 Although this may make a rather crude centrifuge it may be an adequate solution for a fraction of the cost of a commercial centrifuge.
-Other examples of open source research tools that utilize 3D printed parts include optics equipment\cite{Zhang2013}, microscopes\cite{Baden2014a,Walus2014}, syringe pumps\cite{Wijnen2014}, reactionware\cite{Symes2012,Kitson2012,Mathieson2013,Kitson2014}, microfluidics\cite{Brennan2015,Dragone2013} and the list continues to grow\cite{PlosCollections}.
+Other examples of open source research tools that utilize 3D printed parts include optics equipment\cite{Zhang2013}, microscopes\cite{Baden2014a,Walus2014}, syringe pumps\cite{Wijnen2014,Patrick2015}, reactionware\cite{Symes2012,Kitson2012,Mathieson2013,Kitson2014}, microfluidics\cite{Brennan2015,Dragone2013} and the list continues to grow\cite{PlosCollections}.
 
-One example of a everyday scientific tool that provides opportunity for an open design solution is the micropipette.
+One example of an everyday scientific tool that provides opportunity for an open design solution is the micropipette.
 An open design micropipette that can be made cheaply affords more options for labs and educational settings.
@@
 Often a lab will require several sets each for a dedicated task.
-Some pipettes may even re-calibrated for use with liquids of different properties.
+Some pipettes may even be re-calibrated for use with liquids of different properties.
 
-Air displacement pipettes use a piston operating principal to draw liquid into the pipette\cite{ISO8655}.
+Air displacement pipettes use a piston operating principle to draw liquid into the pipette\cite{ISO8655}.
 In a typical commercial pipette the piston is made to be gas-tight with a gasketed plunger inside a smooth barrel.
-Consumer grade fused deposition modeling (FDM) printers are unable to build a smooth surface do to the formation of ridges that occur as each layer is deposited.
+Consumer grade fused deposition modeling (FDM) printers are unable to build a smooth surface due to the formation of ridges that occur as each layer is deposited\cite{Takagishi2017}.
 The ridges formed by FDM make it impractical to form a gas-tight seal between moving parts, even with a gasket.
@@
 {\bf (C) The blow-out position.} The fluid is transferred by pressing the plunger past the latched position to blow-out all the liquid.
-{\bf (D) Return to the latched position.} The pipette returns to the latched position ready to preform another transfer.
+{\bf (D) Return to the latched position.} The pipette returns to the latched position ready to perform another transfer.
 	}
@@
 \section*{Results and Discussion}
-Validation testing preformed with the existing graduations printed on the syringes did not meet the ISO standards.
+Validation testing performed with the existing graduations printed on the syringes did not meet the ISO standards.
 According to ISO 8655 for a pipette with the maximum nominal volume of 1000 $\mu$L the systematic error cannot exceed 8 $\mu$L and the random error cannot exceed 3 $\mu$L.
@@
 The water in the tip pulls on the air due to gravity which causes it to expand slightly but enough to make measuring with the graduation in this way inaccurate.
+
 Our solution was to replace the built-in scale with a scale that accounted for the expansion.
-Using the data from our initial testing we calculated a factor for the expansion and used that to make the new scale (\nameref{S1_Fig} and \nameref{S1_Fig}.)
+We compared expected volumes with actual measurements and noticed a linear relationship.
+We scaled up the graduations by a factor of 1.027x for both the 100-1000 $\mu$L, and 30-300 $\mu$L configurations.
+These scales were exported to portable document format (PDF) so that they are most easily printed to scale.
+These adjusted scales are printed on a transparency sheet and taped onto the syringe with the zero at plunger in the latched position (\nameref{S1_Fig} and \nameref{S1_Fig}).
+
 With the new scale taped on the syringe our validation testing met the ISO 8655 standard.
@@
 		\label{table3}
-		\begin{tabular}{lllllll}
+		\begin{tabular}{llccccc}
 			&                       & Mean   & Systematic Error & \% Sys. err. & Random Error & \% Rand. err. \\
@@
 		\label{table4}
-		\begin{tabular}{lllllll}
+		\begin{tabular}{llccccc}
 			&                       & Mean   & Systematic Error & \% Sys. err. & Random Error & \% Rand. err. \\
@@
 			&                       &        &                  &              &              &               \\         
-			20 $\mu$L* & ISO 8655, 30-300 $\mu$L   & 20     & 4                & 20           & 1.5          & 7.5           \\
-			& Commercial Pipette    & NA     & NA               & NA           & NA           & NA            \\
-			& Printed Pipette       & 18.70  & -1.30            & -6.48        & 0.38         & 2.01          \\
-			& Printed Pipette Scale & 17.94  & -2.06            & -10.29       & 1.87         & 10.42         \\
-			&                       &        &                  &              &              &               \\
-			10 $\mu$L* & ISO 8655, 30-300 $\mu$L   & 10     & 4                & 40           & 1.5          & 15            \\
-			& Commercial Pipette    & NA     & NA               & NA           & NA           & NA            \\
-			& Printed Pipette       & 11.95  & 1.95             & 19.52        & 0.73         & 6.08          \\
-			& Printed Pipette Scale & 7.64   & -2.36            & -23.64       & 0.38         & 4.92         
 		\end{tabular}
-		\begin{flushleft} * The 20 $\mu$L and 10 $\mu$L volumes are out of the range in this case but we wanted to demonstrate that the pipette is capable of even smaller volumes.
-		\end{flushleft}
 	\end{adjustwidth}
@@
 Future directions for this project include developing a tip ejection system and additional configurations for transferring volumes below 30 uL as well as increasing over all user friendliness, such as making the adjusting bolt easier to grip and improving ergonomics.
+It's our hope that this project is under continuous development and compatibility with different syringes and printers can be crowd-sourced from community contributors.
 
@@
 \label{S1_Video}
-{\bf Video showing assembly and demonstration of operation.} Assembly of the pipette in the 100-1000 $\mu$L and 30-300 $\mu$L configuration is preformed. https://www.youtube.com/watch?v=D8y5WUYpcW0
+{\bf Video showing assembly and demonstration of operation.} Assembly of the pipette in the 100-1000 $\mu$L and 30-300 $\mu$L configuration is performed. https://www.youtube.com/watch?v=D8y5WUYpcW0
 

### 2017-06-29 Plos-one-manuscript/latex/manuscript.tex
working on revision

@@
 These scales were exported to portable document format (PDF) so that they are most easily printed to scale.
-These adjusted scales are printed on a transparency sheet and taped onto the syringe with the zero at plunger in the latched position (\nameref{S1_Fig} and \nameref{S1_Fig}).
+These adjusted scales are printed on paper or a transparency sheet and taped onto the syringe with the zero at plunger in the latched position (\nameref{S1_Fig} and \nameref{S1_Fig}).
 
@@
 The biropipette also was developed in OpenSCAD which is free and open source CAD software where our design was created in Solidworks a proprietary software.
+This creates a limitation for users who may not have access to the proprietary software used to make the design.
+Fortunately the produced STL files are universal and can be imported an modified by any CAD software.
+
+The luer to pipette tip connection is a good candidate for a 3D printed solution.
+Unfortunately the current state of FDM can not make this adapter with high enough resolution or critically, surface smoothness.
+Other printing techniques, such as stereolithography (SLA) and MultiJet Printing (MJP), provide higher resolution and smoother finishing, yet FDM is the the most widely available and affordable of printing technologies.
+SLA printers are coming down in price but are still significantly more expensive especially considering the higher cost of the consumable resin vs. FDM filament.
+Ultimately the goal of this project is to make this pipette cheap and easy to make.
 

### 2017-07-07 Plos-one-manuscript/latex/manuscript.tex
save

@@
 The pipette can also be pressed past the latched position to `blow-out' the transferred fluid completely from the pipette tip.   
-Additional materials required for assembly include two springs, a nut, a bolt and two washers.
+Additional materials required for assembly include two springs, a nut, and a bolt.
 Attempts to make a printable luer lock adapter for tips was abandoned as the surface of printed parts is too rough to make an air tight seal with the luer or pipette tip.
@@
 The bolt is threaded in from the top of the body into the nut.
-Springs and washers are threaded onto the plunger of a 1 mL syringe for the 30-300 $\mu$L configuration.
+Two springs are threaded onto the plunger of a 1 mL syringe for the 30-300 $\mu$L configuration.
 Springs are placed inside a 3 mL syringe for the 100-1000 $\mu$L configuration.
@@
 \label{table1}
-\begin{tabular}{|l|l|l|l|}
+	\begin{tabular}{|l|l|r|l|}
 		\hline
-	Part         & Unit Price & Source         & Part number \\ \hline
-	Filament     & \$1.63     & Makerbot       & NA          \\ \hline
-	1 mL Syringe & \$0.15     & BD Biosciences & 309628      \\ \hline
-	Bolt         & \$0.12     & McMaster-Carr  & 91287A026   \\ \hline
-	Nut          & \$0.01     & McMaster-Carr  & 90591A121   \\ \hline
-	Spring (2)   & \$4.14     & McMaster-Carr  & 94125K542   \\ \hline
-	Washers (2)  & \$0.16     & McMaster-Carr  & 90107A012   \\ \hline
-	total        & \$6.21     &                &             \\ \hline
+	30-300 mL Configuration:              & Source            & Unit Price & Part Number \\ \hline
+	Filament                              & Makerbot          & \$1.63     & NA          \\ \hline
+	1 mL Syringe                          & BD Biosciences    & \$0.15     & 309628      \\ \hline
+	M3 Bolt, 35 mm                        & McMaster-Carr     & \$0.12     & 91287A026   \\ \hline
+	M3 Nut                                & McMaster-Carr     & \$0.01     & 90591A121   \\ \hline
+	Music Wire Compression Springs* (2)   & Jones Spring Co   & \$1.23     & C10-022-048 \\ \hline
+	Female Luer to 1/8" Hose Barb Adapter & Cole-Parmer       & \$0.40     & EW-30800-08 \\ \hline
+	Tygon Tubing, 1/16"ID x 3/16"OD       & Cole-Parmer       & \$0.03     & EW-06407-72 \\ \hline
+	300 uL Tips (10)                      & Fisher Scientific & \$0.34     & 02-707-447  \\ \hline
+	& Total             & \$3.91     &     \\ \hline        
 	\end{tabular}
@@
 \label{table2}
-\begin{tabular}{|l|l|l|l|}
+\begin{tabular}{|l|l|r|l|}
 	\hline
-	Part         & Unit Price & Source         & Part number \\ \hline
-	Filament     & \$1.63     & Makerbot       & NA          \\ \hline
-	3 mL Syringe & \$0.73     & BD Biosciences & 309657      \\ \hline
-	Bolt         & \$0.12     & McMaster-Carr  & 91287A026   \\ \hline
-	Nut          & \$0.01     & McMaster-Carr  & 90591A121   \\ \hline
-	Spring (2)   & \$4.14     & McMaster-Carr  & 94125K542   \\ \hline
-	total        & \$6.63     &                &             \\ \hline
+	100-1000 mL configuration:             & Source            & Unit Price & Part Number \\ \hline
+	Filament                               & Makerbot          & \$1.63     & NA          \\ \hline
+	3 mL Syringe                           & BD Biosciences    & \$0.73     & 309657      \\ \hline
+	M3 Bolt, 35 mm                         & McMaster-Carr     & \$0.12     & 91287A026   \\ \hline
+	M3 Nut                                 & McMaster-Carr     & \$0.01     & 90591A121   \\ \hline
+	Music Wire Compression Springs* (2)    & Jones Spring Co   & \$1.23     & C10-022-048 \\ \hline
+	Female luer to 5/32" Hose Barb Adapter & Cole-Parmer       & \$0.66     & EW-45508-06 \\ \hline
+	Tygon Tubing, 1/8"ID x 1/4"OD          & Cole-Parmer       & \$0.05     & EW-06407-76 \\ \hline
+	1000 uL Tips (10)                      & Fisher Scientific & \$0.41     & 02-707-400  \\ \hline
+	& Total             & \$4.84     &            \\ \hline
 \end{tabular}
+\begin{flushleft} *Spring Specifications: Overall length 38 mm, OD 7.62 mm, wire diameter 0.56 mm, Max load 0.86 kg, with closed and flat ends. Also available from McMaster-Carr P/N: 9657K347.
+\end{flushleft}
 \end{table}
@@
 These scales were exported to portable document format (PDF) so that they are most easily printed to scale.
-These adjusted scales are printed on paper or a transparency sheet and taped onto the syringe with the zero at plunger in the latched position (\nameref{S1_Fig} and \nameref{S1_Fig}).
+These adjusted scales are printed on paper or a transparency sheet and taped onto the syringe with the zero at the plunger in the latched position (\nameref{S1_Fig} and \nameref{S1_Fig}).
 

### 2017-07-13 data/commerical-Vs-printed-comparison/analysis/box-plots.R
working on box plots

@@ -1,0 +1,13 @@
+ISO_1000uL <- read.csv(file='1000uL_ISO.csv', sep=',')
+
+library(ggplot2)
+ggplot(ISO_plot_1000[3,], aes(x=nominal, ymin = `minus`, 
+                                ymax = `plus`, lower = `minus`, 
+                                upper = `plus`, middle = `minus`+8)) + 
+  geom_boxplot(stat = 'identity') +
+  #xlab('Nominal Volume') + 
+  ylab('Volume')
+  #geom_crossbar(aes(y = `commercial`), linetype = 1)+
+  #geom_crossbar(aes(y = `Printed`), linetype = 2)
+geom_point(ISO_plot_1000[3,], aes(x=nominal, y=`commercial`)
+           

### 2017-07-14 data/commerical-Vs-printed-comparison/analysis/box-plots300.R
box plots done

@@ -1,0 +1,39 @@
+data_300uL <- read.csv(file='data_300uL.csv', sep=',')
+data_300uL = as.data.frame(data_300uL)
+
+library(ggplot2)
+
+require(gridExtra)
+plot1 <- ggplot(data_300uL[1,], aes(x=nominal, ymin = `low`, ymax = `high`, lower = `low`, upper = `high`, middle = `nominal`)) + 
+  geom_boxplot(stat = 'identity') +
+  geom_point(aes(nominal, y=`commercial`), size=5, shape=21)+
+  geom_point(aes(nominal, y=`printed`), size=5, shape=22, fill="black" ) +
+  geom_point(aes(nominal, y=`adjusted`), size=5, shape=22)+
+  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank(), axis.title.y=element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
+  labs(x="300 μL")
+plot2 <- ggplot(data_300uL[2,], aes(x=nominal, ymin = `low`, ymax = `high`, lower = `low`, upper = `high`, middle = `nominal`)) + 
+  geom_boxplot(stat = 'identity') +
+  geom_point(aes(nominal, y=`commercial`), size=5, shape=21)+
+  geom_point(aes(nominal, y=`printed`), size=5, shape=22, fill="black" ) +
+  geom_point(aes(nominal, y=`adjusted`), size=5, shape=22)+
+  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank(), axis.title.y=element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
+  labs(x="200 μL")
+plot3 <- ggplot(data_300uL[3,], aes(x=nominal, ymin = `low`, ymax = `high`, lower = `low`, upper = `high`, middle = `nominal`)) + 
+  geom_boxplot(stat = 'identity') +
+  geom_point(aes(nominal, y=`commercial`), size=5, shape=21)+
+  geom_point(aes(nominal, y=`printed`), size=5, shape=22, fill="black" ) +
+  geom_point(aes(nominal, y=`adjusted`), size=5, shape=22)+
+  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank(), axis.title.y=element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank())+  
+  labs(x="50 μL")
[…]

### 2017-07-14 Plos-one-manuscript/latex/manuscript-old.tex
ready to submit

--- 2017-06-27 Plos-one-manuscript/latex/manuscript.tex
@@
 
-One example of an everyday scientific tool that provides opportunity for an open design solution is the micropipette.
+One example of a everyday scientific tool that provides opportunity for an open design solution is the micropipette.
 An open design micropipette that can be made cheaply affords more options for labs and educational settings.
@@
 Often a lab will require several sets each for a dedicated task.
-Some pipettes may even be re-calibrated for use with liquids of different properties.
+Some pipettes may even re-calibrated for use with liquids of different properties.
 
-Air displacement pipettes use a piston operating principle to draw liquid into the pipette\cite{ISO8655}.
+Air displacement pipettes use a piston operating principal to draw liquid into the pipette\cite{ISO8655}.
 In a typical commercial pipette the piston is made to be gas-tight with a gasketed plunger inside a smooth barrel.
-Consumer grade fused deposition modeling (FDM) printers are unable to build a smooth surface due to the formation of ridges that occur as each layer is deposited\cite{Takagishi2017}.
+Consumer grade fused deposition modeling (FDM) printers are unable to build a smooth surface do to the formation of ridges that occur as each layer is deposited\cite{Takagishi2017}.
 The ridges formed by FDM make it impractical to form a gas-tight seal between moving parts, even with a gasket.
@@
 {\bf (C) The blow-out position.} The fluid is transferred by pressing the plunger past the latched position to blow-out all the liquid.
-{\bf (D) Return to the latched position.} The pipette returns to the latched position ready to perform another transfer.
+{\bf (D) Return to the latched position.} The pipette returns to the latched position ready to preform another transfer.
 	}
@@
 \section*{Results and Discussion}
-Validation testing performed with the existing graduations printed on the syringes did not meet the ISO standards.
+Validation testing preformed with the existing graduations printed on the syringes did not meet the ISO standards.
 According to ISO 8655 for a pipette with the maximum nominal volume of 1000 $\mu$L the systematic error cannot exceed 8 $\mu$L and the random error cannot exceed 3 $\mu$L.
@@
 The water in the tip pulls on the air due to gravity which causes it to expand slightly but enough to make measuring with the graduation in this way inaccurate.
-
 Our solution was to replace the built-in scale with a scale that accounted for the expansion.
-We compared expected volumes with actual measurements and noticed a linear relationship.
-We scaled up the graduations by a factor of 1.027x for both the 100-1000 $\mu$L, and 30-300 $\mu$L configurations.
-These scales were exported to portable document format (PDF) so that they are most easily printed to scale.
-These adjusted scales are printed on a transparency sheet and taped onto the syringe with the zero at plunger in the latched position (\nameref{S1_Fig} and \nameref{S1_Fig}).
-
+Using the data from our initial testing we calculated a factor for the expansion and used that to make the new scale (\nameref{S1_Fig} and \nameref{S1_Fig}.)
 With the new scale taped on the syringe our validation testing met the ISO 8655 standard.
@@
 Future directions for this project include developing a tip ejection system and additional configurations for transferring volumes below 30 uL as well as increasing over all user friendliness, such as making the adjusting bolt easier to grip and improving ergonomics.
-It's our hope that this project is under continuous development and compatibility with different syringes and printers can be crowd-sourced from community contributors.
 
@@
 \label{S1_Video}
-{\bf Video showing assembly and demonstration of operation.} Assembly of the pipette in the 100-1000 $\mu$L and 30-300 $\mu$L configuration is performed. https://www.youtube.com/watch?v=D8y5WUYpcW0
+{\bf Video showing assembly and demonstration of operation.} Assembly of the pipette in the 100-1000 $\mu$L and 30-300 $\mu$L configuration is preformed. https://www.youtube.com/watch?v=D8y5WUYpcW0
 
